### 2024-11-08 paper/A2-starter-code.Rmd
starter code and data added

---
title: "A2 Sample"
author: "Author A & Author B"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include=TRUE, eval=TRUE)
required_packages <- c("lubridate", "sf", "tidyverse")
for (p in required_packages) {
  if (!require(p, character.only = TRUE)) {
    install.packages(p, character.only = TRUE)
  }
}
library(tidyverse)
library(sf)
# you are welcome to use either the CSV file or the GeoJSON file
# GeoJSON format maybe useful if you would like to combine
# an external geospatial dataset
bike_thefts_csv <- read_csv("data/Bicycle_Thefts_Open_Data.csv") |>
  mutate(
    occurence_date = as_date(
      OCC_DATE, format = "%a, %d %b %Y %H:%M:%S GMT"
    ),
    report_date = as_date(
      REPORT_DATE, format = "%a, %d %b %Y %H:%M:%S GMT"
    )
  )
bike_thefts_sf <- read_sf("data/Bicycle_Thefts_Open_Data.geojson") |>
  mutate(
    occurence_date = as_date(
      OCC_DATE, format = "%a, %d %b %Y %H:%M:%S GMT"
    ),
    report_date = as_date(
      REPORT_DATE, format = "%a, %d %b %Y %H:%M:%S GMT"
    )
  )
```

### 2024-11-08 paper/A2-starter-code.Rmd
paper setups

@@
 ---
-title: "A2 Sample"
-author: "Author A & Author B"
-output: html_document
+title: "Spatial and Temporal Analysis of Bicycle Thefts in Toronto"
+subtitle: "Trends, Patterns, and Insights"
+author: "Yingke He, Ziheng Zhong"
+output:
+  pdf_document: default
+  html_document: default
 ---
@@
 knitr::opts_chunk$set(echo = FALSE, include=TRUE, eval=TRUE)
-required_packages <- c("lubridate", "sf", "tidyverse")
+required_packages <- c("lubridate", "sf", "tidyverse", "readr", "here")
 for (p in required_packages) {
@@
 }
+
 library(tidyverse)
 library(sf)
+library(readr)
+library(here)
+
 # you are welcome to use either the CSV file or the GeoJSON file
@@
 # an external geospatial dataset
-bike_thefts_csv <- read_csv("data/Bicycle_Thefts_Open_Data.csv") |>
+bike_thefts_csv <- read_csv(here("data/Bicycle_Thefts_Open_Data.csv")) |>
   mutate(
@@
   )
-bike_thefts_sf <- read_sf("data/Bicycle_Thefts_Open_Data.geojson") |>
+bike_thefts_sf <- read_sf(here("data/Bicycle_Thefts_Open_Data.geojson")) |>
   mutate(

### 2024-11-08 paper/A2-starter-code.Rmd
possible charts added

@@
 knitr::opts_chunk$set(echo = FALSE, include=TRUE, eval=TRUE)
-required_packages <- c("lubridate", "sf", "tidyverse", "readr", "here")
+
+required_packages <- c("lubridate", "sf", "tidyverse", "readr", "here", "osmdata", "ggplot2")
 for (p in required_packages) {
@@
 
+library(lubridate)
 library(tidyverse)
-library(sf)
+library(ggplot2)
+library(osmdata)
 library(readr)
 library(here)
+library(sf)
 
@@
 ```
+
+```{r}
+# Load the dataset
+bike_thefts <- read_csv(here("data/Bicycle_Thefts_Open_Data.csv"))
+
+# Create a bar chart for the number of bicycle thefts by month
+bike_thefts %>%
+  count(OCC_MONTH) %>%
+  ggplot(aes(x = reorder(OCC_MONTH, -n), y = n, fill = OCC_MONTH)) +
+  geom_bar(stat = "identity") +
+  labs(title = "Number of Bicycle Thefts by Month", x = "Month", y = "Number of Thefts") +
+  theme_minimal()
+
+# Save the plot
+# ggsave(here("other/charts/thefts_by_month.png"))
+```
+
+```{r}
+# Create a pie chart for the status of bicycle thefts
+bike_thefts %>%
+  count(STATUS) %>%
+  ggplot(aes(x = "", y = n, fill = STATUS)) +
+  geom_bar(stat = "identity", width = 1) +
+  coord_polar("y") +
+  labs(title = "Bicycle Theft Status (Stolen vs Recovered)") +
+  theme_minimal()
+
+# Save the plot
+# ggsave(here("other/charts/theft_status_pie.png"))
+```
+
+```{r}
+# Create a bar chart for bicycle thefts by day of the week
+bike_thefts %>%
+  count(OCC_DOW) %>%
+  ggplot(aes(x = reorder(OCC_DOW, -n), y = n, fill = OCC_DOW)) +
+  geom_bar(stat = "identity") +
+  labs(title = "Number of Bicycle Thefts by Day of the Week", x = "Day of the Week", y = "Number of Thefts") +
+  theme_minimal()
+
+# Save the plot
+# ggsave(here("other/charts/thefts_by_day.png"))
+```
+
+```{r}
+# Load cleaned coordinates data
+coordinates_data <- read.csv(here("data/cleaned_coordinates_data.csv"))
+
+# Get bounding box for Toronto (approximate limits for Toronto)
+toronto_bbox <- c(-79.6303856025883, 43.5822069220627, -79.1180336515019, 43.8554571861712)
+
+# Fetch map data from OpenStreetMap (OSM)
+toronto_map <- opq(bbox = toronto_bbox) %>%
+  add_osm_feature(key = "highway", value = "primary") %>%
+  add_osm_feature(key = 'highway', value = 'secondary') %>%
+  add_osm_feature(key = 'highway', value = 'tertiary') %>%
+  add_osm_feature(key = 'highway', value = 'residential') %>%
+  osmdata_sf()
+
+# Convert map data to Simple Features (sf) objects
+streets <- toronto_map$osm_lines
+
+# Plot the map with bike theft locations data
+ggplot() +
+  geom_sf(data = streets, color = "gray", size = 0.3, alpha = 0.6) + # OSM street map layer
+  geom_point(
+    data = coordinates_data, aes(x = longitude, y = latitude),
+    size = 0.5, color = "red"
+  ) + # Bike theft points
+  labs(
+    title = "Map of Bicycle Theft Locations in Toronto",
+    x = "Longitude", y = "Latitude"
+  ) +
+  coord_sf(
+    xlim = c(-79.6303856025883, -79.1180336515019),
+    ylim = c(43.5822069220627, 43.8554571861712), expand = FALSE
+  ) +
+  theme_minimal() +
+  theme(
+    panel.background = element_blank(), # Remove panel background
+    panel.grid.major = element_blank(), # Remove major grid lines
+    panel.grid.minor = element_blank(), # Remove minor grid lines
+    axis.text.x = element_text(angle = 45, hjust = 1)
+  )
+
+# Save the plot
+# ggsave(here("other/charts/bicycle_theft_heatmap.png"))
+```

### 2024-11-08 paper/A2-starter-code.Rmd
charts updated

@@
   theme_minimal()
-
-# Save the plot
-# ggsave(here("other/charts/theft_status_pie.png"))
 ```
@@
   theme_minimal()
-
-# Save the plot
-# ggsave(here("other/charts/thefts_by_day.png"))
 ```
@@
   )
-
-# Save the plot
-# ggsave(here("other/charts/bicycle_theft_heatmap.png"))
 ```

### 2024-11-08 scripts/charts.R

@@ -1,0 +1,106 @@
+#### Setup #####
+# Libraries
+required_packages <- c("lubridate", "sf", "tidyverse", "readr", "here", "osmdata", "ggplot2")
+for (p in required_packages) {
+  if (!require(p, character.only = TRUE)) {
+    install.packages(p, character.only = TRUE)
+  }
+}
+
+library(lubridate)
+library(tidyverse)
+library(ggplot2)
+library(osmdata)
+library(readr)
+library(here)
+library(sf)
+
+# Data
+bike_thefts <- read_csv(here("data/Bicycle_Thefts_Open_Data.csv"))
+coordinates_data <- read.csv(here("data/cleaned_coordinates_data.csv"))
+
+#### Chart 1 #####
+# Create a bar chart for the number of bicycle thefts by month
+bike_thefts %>%
+  count(OCC_MONTH) %>%
+  ggplot(aes(x = reorder(OCC_MONTH, -n), y = n, fill = OCC_MONTH)) +
+  geom_bar(stat = "identity") +
+  labs(title = "Number of Bicycle Thefts by Month", x = "Month", y = "Number of Thefts") +
+  theme_minimal()
+
+# Save the plot
+ggsave(here("other/charts/thefts_by_month.png"))
+
+
+
+#### Chart 2 #####
+# Create a pie chart for the status of bicycle thefts
+bike_thefts %>%
+  count(STATUS) %>%
+  ggplot(aes(x = "", y = n, fill = STATUS)) +
+  geom_bar(stat = "identity", width = 1) +
+  coord_polar("y") +
+  labs(title = "Bicycle Theft Status (Stolen vs Recovered)") +
+  theme_minimal()
+
+# Save the plot
+ggsave(here("other/charts/theft_status_pie.png"))
+
+
+
+#### Chart 3 #####
+# Create a bar chart for bicycle thefts by day of the week
+bike_thefts %>%
+  count(OCC_DOW) %>%
+  ggplot(aes(x = reorder(OCC_DOW, -n), y = n, fill = OCC_DOW)) +
+  geom_bar(stat = "identity") +
+  labs(title = "Number of Bicycle Thefts by Day of the Week", x = "Day of the Week", y = "Number of Thefts") +
+  theme_minimal()
+
+# Save the plot
+ggsave(here("other/charts/thefts_by_day.png"))
+
+
+
+#### Chart 4 #####
+# Get bounding box for Toronto (approximate limits for Toronto)
[…]

### 2024-11-08 paper/paper.Rmd
paper name changed, warnings and messages hided

--- 2024-11-08 paper/A2-starter-code.Rmd
@@
 
-```{r setup, include=FALSE}
+```{r, include = FALSE, warning = FALSE, message = FALSE}
 knitr::opts_chunk$set(echo = FALSE, include=TRUE, eval=TRUE)
@@
 
-```{r}
+```{r, include = TRUE, warning = FALSE, message = FALSE}
 # Load the dataset
@@
 
-```{r}
+```{r, include = TRUE, warning = FALSE, message = FALSE}
 # Create a pie chart for the status of bicycle thefts
@@
 
-```{r}
+```{r, include = TRUE, warning = FALSE, message = FALSE}
 # Create a bar chart for bicycle thefts by day of the week
@@
 
-```{r}
+```{r, include = TRUE, warning = FALSE, message = FALSE}
 # Load cleaned coordinates data

### 2024-11-10 scripts/data_clean.R
Add cleaned data

@@ -1,49 +1,28 @@
-# Load required libraries
-library(jsonlite)
+
+# Purpose: This code sequence cleans and processes bicycle theft data by renaming columns, converting data types, handling missing values, and adding calculated fields. The cleaned dataset is then saved for further analysis, enabling insights into theft patterns, risk factors, and reporting delays to better inform the cyclist community and relevant stakeholders.
+# Author: Yingke He, Ziheng Zhong
+# Date: Nov 11 2024
+# Contact: ziheng.zhong@mail.utoronto.ca
+# License: MIT
+
+#### Load necessary libraries ####
 library(dplyr)
-library(sf)
+library(lubridate)
+library(readr)
+library(here)  # Added this to ensure 'here' is loaded
 
-# Load the GeoJSON data
-bike_thefts_geo <- read_sf(here("data/Bicycle_Thefts_Open_Data.geojson"))
+#### Load data ####
+bicycle_thefts <- read_csv(here("data", "Bicycle_Thefts_Open_Data.csv"))
 
-# Function to extract and clean coordinates from geometry
-extract_coordinates <- function(geo) {
-  if (!is.null(geo) && nrow(st_coordinates(geo)) > 0) {
-    # Convert geometry to WKT format and extract coordinates
-    coords <- st_coordinates(geo)
-    
-    if (!is.null(coords)) {
-      # Separate longitude and latitude
-      longitude <- coords[, 1]
-      latitude <- coords[, 2]
-      
-      # Create a data frame with longitude and latitude
-      coords_df <- data.frame(longitude = longitude, latitude = latitude)
-      return(coords_df)
-    }
-  }
-  
-  return(NULL) # Return NULL for invalid or empty data
-}
 
-# Apply the function to extract all coordinates from the 'geometry' column
-all_coordinates <- lapply(bike_thefts_geo$geometry, extract_coordinates)
+#### Handle missing values ####
+# Example: Remove rows with missing dates
+bicycle_thefts <- bicycle_thefts %>%
+  filter(!is.na(Occurrence_Date) & !is.na(Reported_Date))
 
-# Filter out any NULL values from the list of extracted coordinates
-valid_coordinates <- all_coordinates[!sapply(all_coordinates, is.null)]
+#### Remove columns with any missing values ####
+bicycle_thefts <- bicycle_thefts %>%
+  select(where(~ !any(is.na(.))))
 
[…]

### 2024-11-10 scripts/data_coordinates_clean.R

@@ -1,0 +1,49 @@
+# Load required libraries
+library(jsonlite)
+library(dplyr)
+library(sf)
+
+# Load the GeoJSON data
+bike_thefts_geo <- read_sf(here("data/Bicycle_Thefts_Open_Data.geojson"))
+
+# Function to extract and clean coordinates from geometry
+extract_coordinates <- function(geo) {
+  if (!is.null(geo) && nrow(st_coordinates(geo)) > 0) {
+    # Convert geometry to WKT format and extract coordinates
+    coords <- st_coordinates(geo)
+    
+    if (!is.null(coords)) {
+      # Separate longitude and latitude
+      longitude <- coords[, 1]
+      latitude <- coords[, 2]
+      
+      # Create a data frame with longitude and latitude
+      coords_df <- data.frame(longitude = longitude, latitude = latitude)
+      return(coords_df)
+    }
+  }
+  
+  return(NULL) # Return NULL for invalid or empty data
+}
+
+# Apply the function to extract all coordinates from the 'geometry' column
+all_coordinates <- lapply(bike_thefts_geo$geometry, extract_coordinates)
+
+# Filter out any NULL values from the list of extracted coordinates
+valid_coordinates <- all_coordinates[!sapply(all_coordinates, is.null)]
+
+# Create a unique ID for each geometry feature (so we know which points belong together)
+bike_thefts_geo$id <- seq_len(nrow(bike_thefts_geo))
+
+# Combine all valid coordinates into a single dataframe with IDs
+coordinates_data <- do.call(rbind, Map(function(coords, id) {
+  coords$id <- id # Add ID to each set of coordinates
+  return(coords)
+}, valid_coordinates, bike_thefts_geo$id[!sapply(all_coordinates, is.null)]))
+
+# Ensure no NA values exist in longitude and latitude
+coordinates_data <- coordinates_data %>%
+  filter(!is.na(longitude), !is.na(latitude))
+
+# Save the cleaned coordinates data to the same directory
+write.csv(coordinates_data, here("data/cleaned_coordinates_data.csv"), row.names = FALSE)

### 2024-11-10 paper/paper.Rmd

@@
 ---
-title: "Spatial and Temporal Analysis of Bicycle Thefts in Toronto"
-subtitle: "Trends, Patterns, and Insights"
+title: "Ride at Your Own Risk: Insights into Toronto’s Bicycle Theft Hotspots"
+subtitle: "[To Be Updated....]"
 author: "Yingke He, Ziheng Zhong"
+thanks: "Code and data are available at: [https://github.com/iJustinn/Toronto_Bicycle_Thefts/tree/main](https://github.com/iJustinn/Toronto_Bicycle_Thefts/tree/main)."
+date: today
 output:
-  pdf_document: default
+  pdf_document:
+    latex_engine: xelatex
   html_document: default
+bibliography: references.bib
 ---
@@
 ```
-
+Bar chart
 ```{r, include = TRUE, warning = FALSE, message = FALSE}
@@
 ```
-
+Pie chart
 ```{r, include = TRUE, warning = FALSE, message = FALSE}
@@
 ```
-
+Map
 ```{r, include = TRUE, warning = FALSE, message = FALSE}
@@
 ```
+# introduction
+write an intro to convey the issue
+the goal of the article :be careful of bikes
+
+# When Are Bikes at the Greatest Risk? A Look at Seasonal and weekly Patterns
+Explore temporal insights, such as trends by month, day of the week with visualizations that reveal when thefts are most likely to occur.
+
+# What Makes a Bike a Target? Analyzing Theft by Bicycle Type and Value
+Discuss any available data on bike types, brands, or values, showing if certain bikes are more vulnerable to theft than others.
+
+# A Decade of Disappearing Bikes: Tracing Theft Trends Over Ten Years
+- timeline
+
+# Mapping the Danger Zones: High-Risk Locations Across Toronto
+Use a map visualization to highlight theft hotspots across Toronto, pointing out neighborhoods or transit hubs with the highest incidence rates.
+
+- map
+
+# Discussion 
+- Consolidation of all the info that we present, we first talk about...this is how all visualizations are connected together, in the future what can be done...
+
+# Conclusion
+- short reminder for the audience, tips to protect their bikes
+
+General tips: 
+ - This paper wants to tell the story about tips to protect bikes
+
+ - after every visualizations talk a bit about the visualization itself, key points, make sure the story that we are talking about is proved by this visualization so each plot make sense (for example in 2016 there is a peak in May illustrated by the visualization, why?
+find relevant news and articels to explain it and cite), 用更descriptive的形式去explain 你的visualization plot with proves.

### 2024-11-10 paper/paper.Rmd
Add relevant plots and animations

@@
 date: today
-output:
-  pdf_document:
-    latex_engine: xelatex
-  html_document: default
+output: html_document
 bibliography: references.bib
 ---
+
+<style>
+body {
+  background-color: #f0f8ff; /* AliceBlue color */
+}
+</style>
 
@@
 # an external geospatial dataset
-bike_thefts_csv <- read_csv(here("data/Bicycle_Thefts_Open_Data.csv")) |>
+bike_thefts_csv <- read_csv(here("data/clean_data.csv")) |>
   mutate(
@@
   )
-```
-Bar chart
-```{r, include = TRUE, warning = FALSE, message = FALSE}
-# Load the dataset
-bike_thefts <- read_csv(here("data/Bicycle_Thefts_Open_Data.csv"))
-
-# Create a bar chart for the number of bicycle thefts by month
-bike_thefts %>%
-  count(OCC_MONTH) %>%
-  ggplot(aes(x = reorder(OCC_MONTH, -n), y = n, fill = OCC_MONTH)) +
-  geom_bar(stat = "identity") +
-  labs(title = "Number of Bicycle Thefts by Month", x = "Month", y = "Number of Thefts") +
-  theme_minimal()
-
-# Save the plot
-# ggsave(here("other/charts/thefts_by_month.png"))
-```
-Pie chart
-```{r, include = TRUE, warning = FALSE, message = FALSE}
-# Create a pie chart for the status of bicycle thefts
-bike_thefts %>%
-  count(STATUS) %>%
-  ggplot(aes(x = "", y = n, fill = STATUS)) +
-  geom_bar(stat = "identity", width = 1) +
-  coord_polar("y") +
-  labs(title = "Bicycle Theft Status (Stolen vs Recovered)") +
-  theme_minimal()
-```
-Bar chart
-```{r, include = TRUE, warning = FALSE, message = FALSE}
-# Create a bar chart for bicycle thefts by day of the week
-bike_thefts %>%
-  count(OCC_DOW) %>%
-  ggplot(aes(x = reorder(OCC_DOW, -n), y = n, fill = OCC_DOW)) +
-  geom_bar(stat = "identity") +
-  labs(title = "Number of Bicycle Thefts by Day of the Week", x = "Day of the Week", y = "Number of Thefts") +
-  theme_minimal()
 ```
@@
 # When Are Bikes at the Greatest Risk? A Look at Seasonal and weekly Patterns
-Explore temporal insights, such as trends by month, day of the week with visualizations that reveal when thefts are most likely to occur.
+
+```{r mothly_plot, include = TRUE, warning = FALSE, message = FALSE, fig.width=11, fig.height=5}
+# Load necessary libraries
+library(tidyverse)
+library(ggridges)
+library(cowplot)
+library(here)
+
+# Load your data
+data <- read_csv(here("data", "Theft_and_Found_Counts_By_Month_2014_2024.csv"), show_col_types = FALSE)
+
+# Convert month names to month numbers for ordering
+data <- data %>%
+  mutate(OCC_MONTH_NUM = factor(OCC_MONTH, levels = month.name))
+
+# Specify levels for OCC_YEAR to order from 2014 to 2024
+data$OCC_YEAR <- factor(data$OCC_YEAR, levels = 2014:2024)
+
+# Calculate a scaled height for "Found" data by dividing by the maximum "Found" value
+max_found <- max(data$Found, na.rm = TRUE)
+max_stolen <- max(data$Stolen, na.rm = TRUE)
+
+# Plot for Bikes Found with scaled heights
+plot_found <- ggplot(data, aes(x = OCC_MONTH_NUM, y = OCC_YEAR, 
+                               height = (Found / max_found) * 4, group = OCC_YEAR)) +
+  geom_ridgeline(
+    fill = "#05595B", color = "white", alpha = 0.5, scale = 1, linewidth = 0
+  ) +
+  labs(y = "", x = NULL) +  # Remove x-axis title
+  theme_minimal() +
+  theme(
+    axis.ticks.y = element_blank(),
+    axis.text.y = element_text(size = 12),
+    axis.text.x = element_text(size = 12, angle = 45, hjust = 1),
+    panel.grid.major.x = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    panel.grid.major.y = element_line(size = 0.5),
+    panel.border = element_blank(),
+    plot.title = element_text(size = 10, color = "#05595B", hjust = -0.1, vjust = 1.5),  # Smaller title
+    panel.background = element_rect(fill = "#f0f8ff", color = NA),  # Light blue background for plot area
+    plot.background = element_rect(fill = "#f0f8ff", color = NA)    # Light blue background for overall plot
+  ) +
+  scale_x_discrete(labels = month.abb) +
+  ggtitle("Bikes Found")  # Add title for Bikes Found
+
+# Plot for Bikes Stolen with scaled heights and no borders
+plot_stolen <- ggplot(data, aes(x = OCC_MONTH_NUM, y = OCC_YEAR, 
+                                height = (Stolen / max_stolen) * 4, group = OCC_YEAR)) +
+  geom_ridgeline(
+    fill = "#603601", color = "white", alpha = 0.5, scale = 1, linewidth = 0
+  ) +
+  labs(y = "", x = NULL) +  # Remove x-axis title
+  theme_minimal() +
+  theme(
+    axis.ticks.y = element_blank(),
+    axis.text.y = element_text(size = 12),
+    axis.text.x = element_text(size = 12, angle = 45, hjust = 1),
+    panel.grid.major.x = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    panel.grid.major.y = element_line(size = 0.5),
+    panel.border = element_blank(),
+    panel.background = element_rect(fill = "#f0f8ff", color = NA),  # Light blue background for plot area
+    plot.background = element_rect(fill = "#f0f8ff", color = NA),   # Light blue background for overall plot
+    plot.title = element_text(size = 10, color = "#603601", hjust = -0.1, vjust = 1.5)  # Smaller title
+  ) +
+  scale_x_discrete(labels = month.abb) +
+  ggtitle("Bikes Stolen")  # Add title for Bikes Stolen
+
+# Combine the plots side by side
+combined_plot <- plot_grid(plot_found, plot_stolen, nrow = 1)
+
+# Display the combined plot
+combined_plot
+
+```
+
+```{r interactive_weekly_plot, echo=FALSE, message=FALSE, warning=FALSE, results='asis', fig.width=7, fig.height=4}
+library(plotly)
+library(readr)
+library(dplyr)
+library(here)
+
+# Load the data
+data <- read_csv(here("data", "Theft_Counts_By_Day.csv"), show_col_types = FALSE)
+
+# Arrange data by day of the week (Monday to Sunday)
+data <- data %>%
+  arrange(factor(OCC_DOW, levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")))
+
+# Initialize plot with a line trace for the entire data
+fig <- plot_ly(data, x = ~OCC_DOW, y = ~Number_of_Thefts, type = 'scatter', mode = 'lines+markers',
+               line = list(color = 'brown'), marker = list(color = 'blue', size = 8))
+
+# Add points for each day with initial visibility settings
+for (i in 1:nrow(data)) {
+  fig <- fig %>%
+    add_trace(
+      x = data$OCC_DOW[i],
+      y = data$Number_of_Thefts[i],
+      type = 'scatter',
+      mode = 'markers+text',
+      text = paste("Thefts:", data$Number_of_Thefts[i]),
+      textposition = "top center",
+      marker = list(color = "yellow", size = 10),
+      showlegend = FALSE,
+      visible = ifelse(i == 1, TRUE, FALSE)
+    )
+}
+
+# Define steps for each day in the slider
+steps <- lapply(1:nrow(data), function(i) {
+  step <- list(
+    method = "restyle",
+    args = list("visible", as.list(rep(FALSE, nrow(data) + 1))),  # +1 to include the main line trace
+    label = data$OCC_DOW[i]
+  )
+  step$args[[2]][i + 1] <- TRUE  # Make only the current day’s point visible (offset by 1 due to main line trace)
+  step$args[[2]][1] <- TRUE       # Keep the main line trace visible
+  return(step)
+})
+
+# Add layout with the slider and set background colors
+fig <- fig %>%
+  layout(
+    xaxis = list(title = ""),
+    yaxis = list(title = "Number of Thefts"),
+    sliders = list(
+      list(
+        active = 0,
+        currentvalue = list(prefix = "Day: "),
+        steps = steps
+      )
+    ),
+    plot_bgcolor = "#f0f8ff",     # Set background color for the plotting area
+    paper_bgcolor = "#f0f8ff"     # Set background color for the entire plot
+  )
+
+# Display the plot
+fig
+
+```
 
@@
 # A Decade of Disappearing Bikes: Tracing Theft Trends Over Ten Years
-- timeline
+
+```{r animated_bar_plot, echo=FALSE, message=FALSE, warning=FALSE, results='asis', fig.width=7, fig.height=4}
+# Libraries
+library(ggplot2)
+library(gganimate)
+library(readr)
+library(here)
+library(dplyr)
+
+# Load the data
+data <- read_csv(here("data", "Stolen_Found_Counts.csv"), show_col_types = FALSE)
+
+# Rename "THEFT" to "Stolen" in the Offence_Category column
+data <- data %>%
+  mutate(Offence_Category = ifelse(Offence_Category == "THEFT", "Stolen", Offence_Category))
+
+# Set the number of frames for the animation
+max_frames <- 100  # Total number of frames for smooth animation
+
+# Generate interpolated data for simultaneous increase
+animated_data <- data %>%
+  # Repeat each category for each frame
+  group_by(Offence_Category) %>%
+  do(data.frame(
+    Offence_Category = .$Offence_Category,
+    Number_of_Offences = seq(0, .$Number_of_Offences, length.out = max_frames),
+    frame = 1:max_frames
+  ))
+
+# Ensure Offence_Category is a factor for proper ordering
+animated_data$Offence_Category <- as.factor(animated_data$Offence_Category)
+
+# Define custom colors for each category
+custom_colors <- c("Stolen" = "#603601", "FOUND" = "#4682B4", "Other" = "#eedaaf")
+
+# Create the animated bar plot
+ggplot(animated_data, aes(x=Offence_Category, y=Number_of_Offences, fill=Offence_Category)) + 
+  geom_bar(stat='identity') +
+  theme_minimal() +
+  labs(x = 'Offense Category', y = 'Number of Offences') +
+
+  # Apply custom colors
+  scale_fill_manual(values = custom_colors) +
+
+  # Remove the legend title
+  guides(fill = guide_legend(title = NULL)) +
+
+  # Set background colors for panel and plot
+  theme(
+    panel.background = element_rect(fill = "#f0f8ff", color = NA),
+    plot.background = element_rect(fill = "#f0f8ff", color = NA)
+  ) +
+
+  # gganimate specific settings for smooth transition
+  transition_states(
+    frame,
+    transition_length = 2,
+    state_length = 1
+  ) +
+  ease_aes('linear')  # Ensures a smooth, even increase
+
+```
+<div style="color: grey; font-size: 12 px; margin-top: 3px;"> Displays the count of various bicycle-related offences reported to the Toronto Police Service, highlighting categories such as stolen, found, and other incidents.
+The smooth increase in bar heights emphasizes the scale of each offence type, offering insights into the distribution and relative frequency of these incidents from 2014 to 2024 </div> \
+
+```{r animated_line_plot, echo=FALSE, message=FALSE, warning=FALSE, results='asis', fig.width=6, fig.height=3}
+# Load necessary libraries
+library(ggplot2)
+library(gganimate)
+library(dplyr)
+library(hrbrthemes)
+library(readr)
+library(here)
+
+# Load your data
+data <- read_csv(here("data", "Bicycle_Theft_Monthly_Counts.csv"), show_col_types = FALSE)
+
+# Create a numeric month order variable
+data <- data %>%
+  mutate(
+    OCC_MONTH_NUM = match(OCC_MONTH, c("January", "February", "March", "April", "May", 
+                                       "June", "July", "August", "September", "October", 
+                                       "November", "December"))
+  )
+
+# Create the animated plot
+plot <- data %>%
+  ggplot(aes(x = OCC_MONTH_NUM, y = Number_of_Thefts, group = as.factor(OCC_YEAR), color = as.factor(OCC_YEAR))) +
+  geom_line() +
+  geom_point() +
+  scale_color_viridis_d() +
+  ylab("Number of Bikes Stolen") +
+  xlab("Month") +
+  scale_x_continuous(breaks = 1:12, labels = c("January", "February", "March", "April", "May", "June", 
+                                               "July", "August", "September", "October", "November", "December")) +
+  theme_ipsum() +
+  theme(
+    axis.text.x = element_text(angle = 45, hjust = 1),
+    panel.background = element_rect(fill = "#f0f8ff", color = NA),
+    plot.background = element_rect(fill = "#f0f8ff", color = NA)
+  ) +
+  transition_reveal(OCC_MONTH_NUM) +
+  labs(color = "Year")
+
+# Render the animation
+animate(plot, nframes = 100, fps = 10)
+
+```
+<div style="color: grey; font-size: 12 px; margin-top: 3px;"> Visualizes the monthly count of bicycle thefts reported to the Toronto Police Service from 2014 to June 2024.
+The animation reveals seasonal patterns and variations across different years, providing insights into peak months and potential trends over time.
+</div> \
 

### 2024-11-11 scripts/data_map_clean.R
map data added, map data cleanning added, maps added

@@ -1,0 +1,60 @@
+#### Load necessary libraries ####
+library(readr)
+library(dplyr)
+library(here)
+
+
+
+#### Load data ####
+raw_data <- read_csv(here("data", "Bicycle_Thefts_Open_Data.csv"))
+
+
+
+#### Clean Data ####
+# Read in the data
+raw_data <- read_csv(here("data", "Bicycle_Thefts_Open_Data.csv"))
+
+# Select only the specified columns and rename them
+cleaned_data <- raw_data %>%
+  select(hood_num = HOOD_158, longitude = LONG_WGS84, latitude = LAT_WGS84)
+
+# Save the cleaned dataset
+write_csv(cleaned_data, here("data", "map_by_neighbourhoods_data.csv"))
+
+# Define neighborhood classification lists
+north_york <- c("151", "153", "152", "149", "130", "131", "132", "155", "154", "173", "150", "118", "119", "120")
+scarborough <- c("143", "145", "146", "144", "142", "135", "156", "157", "136", "134", "133", "148", "147")
+toronto_downtown_central <- c("166", "169", "170", "168", "167", "165", "163", "164", "82", "83", "95")
+etobicoke <- c("158", "159", "161", "160", "136")
+york <- c("107", "109", "171")
+east_york <- c("100", "102")
+others <- c("172")
+
+# Classify data based on hood_num and save each as a separate CSV file
+cleaned_data %>%
+  filter(hood_num %in% north_york) %>%
+  write_csv(here("data", "north_york_data.csv"))
+
+cleaned_data %>%
+  filter(hood_num %in% scarborough) %>%
+  write_csv(here("data", "scarborough_data.csv"))
+
+cleaned_data %>%
+  filter(hood_num %in% toronto_downtown_central) %>%
+  write_csv(here("data", "toronto_downtown_central_data.csv"))
+
+cleaned_data %>%
+  filter(hood_num %in% etobicoke) %>%
+  write_csv(here("data", "etobicoke_data.csv"))
+
+cleaned_data %>%
+  filter(hood_num %in% york) %>%
+  write_csv(here("data", "york_data.csv"))
+
+cleaned_data %>%
+  filter(hood_num %in% east_york) %>%
+  write_csv(here("data", "east_york_data.csv"))
+
+cleaned_data %>%
+  filter(hood_num %in% others) %>%
+  write_csv(here("data", "others_data.csv"))

### 2024-11-11 scripts/maps.R

@@ -1,0 +1,300 @@
+#### Setup #####
+# Libraries
+required_packages <- c("sf", "tidyverse", "here", "osmdata", "ggplot2")
+for (p in required_packages) {
+  if (!require(p, character.only = TRUE)) {
+    install.packages(p, character.only = TRUE)
+  }
+}
+
+library(tidyverse)
+library(ggplot2)
+library(osmdata)
+library(here)
+library(sf)
+
+
+
+#### Chart 5 #####
+# Load North York data
+north_york_data <- read_csv(here("data", "north_york_data.csv"))
+
+# Get bounding box for Toronto (approximate limits for Toronto)
+toronto_bbox <- c(-79.6303856025883, 43.5822069220627, -79.1180336515019, 43.8554571861712)
+
+# Fetch map data from OpenStreetMap (OSM)
+toronto_map <- opq(bbox = toronto_bbox) %>%
+  add_osm_feature(key = "highway", value = "primary") %>%
+  add_osm_feature(key = 'highway', value = 'secondary') %>%
+  add_osm_feature(key = 'highway', value = 'tertiary') %>%
+  add_osm_feature(key = 'highway', value = 'residential') %>%
+  osmdata_sf()
+
+# Convert map data to Simple Features (sf) objects
+streets <- toronto_map$osm_lines
+
+# Plot the map with North York bike theft locations data
+ggplot() +
+  geom_sf(data = streets, color = "gray", size = 0.3, alpha = 0.6) + # OSM street map layer
+  geom_point(
+    data = north_york_data, aes(x = longitude, y = latitude),
+    size = 0.5, color = "red"
+  ) + # Bike theft points
+  labs(
+    title = "Map of Bicycle Theft Locations in North York",
+    x = "Longitude", y = "Latitude"
+  ) +
+  coord_sf(
+    xlim = c(-79.6303856025883, -79.1180336515019),
+    ylim = c(43.5822069220627, 43.8554571861712), expand = FALSE
+  ) +
+  theme_minimal() +
+  theme(
+    panel.background = element_blank(), # Remove panel background
+    panel.grid.major = element_blank(), # Remove major grid lines
+    panel.grid.minor = element_blank(), # Remove minor grid lines
+    axis.text.x = element_text(angle = 45, hjust = 1)
+  )
+
+# Save the plot
+ggsave(here("other/charts/north_york_bicycle_theft_map.png"))
+
+
+
+#### Chart 6 #####
+# Load North York data
[…]

### 2024-11-11 scripts/data_map_clean.R
Etobicoke data and chart revised

@@ -25,7 +25,7 @@ write_csv(cleaned_data, here("data", "map_by_neighbourhoods_data.csv"))
 north_york <- c("151", "153", "152", "149", "130", "131", "132", "155", "154", "173", "150", "118", "119", "120")
 scarborough <- c("143", "145", "146", "144", "142", "135", "156", "157", "136", "134", "133", "148", "147")
 toronto_downtown_central <- c("166", "169", "170", "168", "167", "165", "163", "164", "82", "83", "95")
-etobicoke <- c("158", "159", "161", "160", "136")
+etobicoke <- c("158", "159", "161", "160")
 york <- c("107", "109", "171")
 east_york <- c("100", "102")
 others <- c("172")

### 2024-11-11 paper/paper.Rmd
add background image

@@
 ---
-title: "Ride at Your Own Risk: Insights into Toronto’s Bicycle Theft Hotspots"
-subtitle: "[To Be Updated....]"
-author: "Yingke He, Ziheng Zhong"
 thanks: "Code and data are available at: [https://github.com/iJustinn/Toronto_Bicycle_Thefts/tree/main](https://github.com/iJustinn/Toronto_Bicycle_Thefts/tree/main)."
-date: today
 output: html_document
@@
 ---
+---
+output: html_document
+---
 
+<!-- Background image -->
 <style>
 body {
-  background-color: #f0f8ff; /* AliceBlue color */
+  background-image: url('bikes1.jpg');
+  background-size: cover;
+  background-position: center;
+  background-attachment: fixed;
+  color: white;
+  font-family: Arial, sans-serif;
+}
+
+.title {
+  font-size: 60px;
+  font-weight: bold;
+  color: #FFC107; /* Yellow color */
+  margin-top: 100px;
+  text-align: left;
+  font-family: 'Georgia'
+}
+
+.subtitle {
+  font-size: 35px;
+  font-weight: normal;
+  color: white;
+  text-align: left;
+  margin-top: 10px;
+  font-family: 'Open Sans', sans-serif;
+}
+
+.description {
+  font-size: 18px;
+  font-weight: normal;
+  color: white;
+  line-height: 1.6;
+  text-align: left;
+  max-width: 600px;
+  margin-top: 20px;
+  font-family: 'Lora'
+}
+
+.author-date {
+  font-size: 18px;
+  font-weight: normal;
+  color: white;
+  text-align: left;
+  margin-top: 30px;
+  font-style: italic;
 }
 </style>
+
+<div class="title">Ride at Your Own Risk: Insights into Toronto’s Bicycle Theft Hotspots</div>
+
+<div class="subtitle">Navigating Toronto’s streets with eyes wide open, this data-driven guide helps cyclists stay ahead of bicycle thieves.</div>
+
+<div class="description">
+Each year, countless bikes disappear from Toronto’s streets, leaving cyclists frustrated and vulnerable.
+Our analysis digs into patterns and insights across the city, highlighting where and when bicycles are most at risk.
+With data spanning over a decade, we reveal theft hotspots and provide tips to help keep your bike safe.
+</div>
+
+<div class="author-date">Yingke He, Ziheng Zhong<br>November 12, 2024</div>
 
@@
 ```
-Map
-```{r, include = TRUE, warning = FALSE, message = FALSE}
-# Load cleaned coordinates data
-coordinates_data <- read.csv(here("data/cleaned_coordinates_data.csv"))
 
-# Get bounding box for Toronto (approximate limits for Toronto)
-toronto_bbox <- c(-79.6303856025883, 43.5822069220627, -79.1180336515019, 43.8554571861712)
+Imagine locking up your bike on a bustling Toronto street, feeling reassured that a strong lock and some common sense will keep it safe.
+But what if certain seasons, specific bike types, or even certain neighborhoods increase your risk of theft far more than you realize?
+For many cyclists, bike theft has moved from a distant possibility to an everyday concern, with data revealing just how pervasive the risk can be in Toronto.
 
-# Fetch map data from OpenStreetMap (OSM)
-toronto_map <- opq(bbox = toronto_bbox) %>%
-  add_osm_feature(key = "highway", value = "primary") %>%
-  add_osm_feature(key = 'highway', value = 'secondary') %>%
-  add_osm_feature(key = 'highway', value = 'tertiary') %>%
-  add_osm_feature(key = 'highway', value = 'residential') %>%
-  osmdata_sf()
+In this analysis, we dig into over a decade’s worth of data from the Toronto Police Service to answer key questions: When are bikes at the greatest risk?
+What makes a bike more likely to be targeted?
+And where are the theft hotspots cyclists should avoid?
+Each section of our article addresses a different angle of bike theft in Toronto, from seasonal and weekly theft patterns to variations by bicycle type and value, to pinpointing the city’s most high-risk locations.
 
-# Convert map data to Simple Features (sf) objects
-streets <- toronto_map$osm_lines
-
-# Plot the map with bike theft locations data
-ggplot() +
-  geom_sf(data = streets, color = "gray", size = 0.3, alpha = 0.6) + # OSM street map layer
-  geom_point(
-    data = coordinates_data, aes(x = longitude, y = latitude),
-    size = 0.5, color = "red"
-  ) + # Bike theft points
-  labs(
-    title = "Map of Bicycle Theft Locations in Toronto",
-    x = "Longitude", y = "Latitude"
-  ) +
-  coord_sf(
-    xlim = c(-79.6303856025883, -79.1180336515019),
-    ylim = c(43.5822069220627, 43.8554571861712), expand = FALSE
-  ) +
-  theme_minimal() +
-  theme(
-    panel.background = element_blank(), # Remove panel background
-    panel.grid.major = element_blank(), # Remove major grid lines
-    panel.grid.minor = element_blank(), # Remove minor grid lines
-    axis.text.x = element_text(angle = 45, hjust = 1)
-  )
-```
-# introduction
-write an intro to convey the issue
-the goal of the article :be careful of bikes
+With these insights, we aim to empower cyclists with knowledge that can help them safeguard their bikes and inform Cycle Toronto and local authorities about the areas most in need of intervention.
+Read on as we trace theft trends over the years, reveal the high-risk locations, and provide practical advice to help protect your bike.
 
@@
 
-```{r mothly_plot, include = TRUE, warning = FALSE, message = FALSE, fig.width=11, fig.height=5}
-# Load necessary libraries
-library(tidyverse)
-library(ggridges)
-library(cowplot)
-library(here)
-
-# Load your data
-data <- read_csv(here("data", "Theft_and_Found_Counts_By_Month_2014_2024.csv"), show_col_types = FALSE)
-
-# Convert month names to month numbers for ordering
-data <- data %>%
-  mutate(OCC_MONTH_NUM = factor(OCC_MONTH, levels = month.name))
-
-# Specify levels for OCC_YEAR to order from 2014 to 2024
-data$OCC_YEAR <- factor(data$OCC_YEAR, levels = 2014:2024)
-
-# Calculate a scaled height for "Found" data by dividing by the maximum "Found" value
-max_found <- max(data$Found, na.rm = TRUE)
-max_stolen <- max(data$Stolen, na.rm = TRUE)
-
-# Plot for Bikes Found with scaled heights
-plot_found <- ggplot(data, aes(x = OCC_MONTH_NUM, y = OCC_YEAR, 
-                               height = (Found / max_found) * 4, group = OCC_YEAR)) +
-  geom_ridgeline(
-    fill = "#05595B", color = "white", alpha = 0.5, scale = 1, linewidth = 0
-  ) +
-  labs(y = "", x = NULL) +  # Remove x-axis title
-  theme_minimal() +
-  theme(
-    axis.ticks.y = element_blank(),
-    axis.text.y = element_text(size = 12),
-    axis.text.x = element_text(size = 12, angle = 45, hjust = 1),
-    panel.grid.major.x = element_blank(),
-    panel.grid.minor.x = element_blank(),
-    panel.grid.major.y = element_line(size = 0.5),
-    panel.border = element_blank(),
-    plot.title = element_text(size = 10, color = "#05595B", hjust = -0.1, vjust = 1.5),  # Smaller title
-    panel.background = element_rect(fill = "#f0f8ff", color = NA),  # Light blue background for plot area
-    plot.background = element_rect(fill = "#f0f8ff", color = NA)    # Light blue background for overall plot
-  ) +
-  scale_x_discrete(labels = month.abb) +
-  ggtitle("Bikes Found")  # Add title for Bikes Found
-
-# Plot for Bikes Stolen with scaled heights and no borders
-plot_stolen <- ggplot(data, aes(x = OCC_MONTH_NUM, y = OCC_YEAR, 
-                                height = (Stolen / max_stolen) * 4, group = OCC_YEAR)) +
-  geom_ridgeline(
-    fill = "#603601", color = "white", alpha = 0.5, scale = 1, linewidth = 0
-  ) +
-  labs(y = "", x = NULL) +  # Remove x-axis title
-  theme_minimal() +
-  theme(
-    axis.ticks.y = element_blank(),
-    axis.text.y = element_text(size = 12),
-    axis.text.x = element_text(size = 12, angle = 45, hjust = 1),
-    panel.grid.major.x = element_blank(),
-    panel.grid.minor.x = element_blank(),
-    panel.grid.major.y = element_line(size = 0.5),
-    panel.border = element_blank(),
-    panel.background = element_rect(fill = "#f0f8ff", color = NA),  # Light blue background for plot area
-    plot.background = element_rect(fill = "#f0f8ff", color = NA),   # Light blue background for overall plot
-    plot.title = element_text(size = 10, color = "#603601", hjust = -0.1, vjust = 1.5)  # Smaller title
-  ) +
-  scale_x_discrete(labels = month.abb) +
-  ggtitle("Bikes Stolen")  # Add title for Bikes Stolen
-
-# Combine the plots side by side
-combined_plot <- plot_grid(plot_found, plot_stolen, nrow = 1)
-
-# Display the combined plot
-combined_plot
-
-```
-
-```{r interactive_weekly_plot, echo=FALSE, message=FALSE, warning=FALSE, results='asis', fig.width=7, fig.height=4}
+```{r interactive_weekly_plot, echo=FALSE, message=FALSE, warning=FALSE, results='asis', fig.width=9.5, fig.height=4}
 library(plotly)
@@
     ),
-    plot_bgcolor = "#f0f8ff",     # Set background color for the plotting area
-    paper_bgcolor = "#f0f8ff"     # Set background color for the entire plot
+    plot_bgcolor = "#faecd5",     # Set background color for the plotting area
+    paper_bgcolor = "#faecd5"     # Set background color for the entire plot
   )
@@
 fig
+
+```
+
+```{r mothly_plot, include = TRUE, warning = FALSE, message = FALSE, fig.width=11, fig.height=5}
+# Load necessary libraries
+library(tidyverse)
+library(ggridges)
+library(cowplot)
+library(here)
+
+# Load your data
+data <- read_csv(here("data", "Theft_and_Found_Counts_By_Month_2014_2024.csv"), show_col_types = FALSE)
+
+# Convert month names to month numbers for ordering
+data <- data %>%
+  mutate(OCC_MONTH_NUM = factor(OCC_MONTH, levels = month.name))
+
+# Specify levels for OCC_YEAR to order from 2014 to 2024
+data$OCC_YEAR <- factor(data$OCC_YEAR, levels = 2014:2024)
+
+# Calculate a scaled height for "Found" data by dividing by the maximum "Found" value
+max_found <- max(data$Found, na.rm = TRUE)
+max_stolen <- max(data$Stolen, na.rm = TRUE)
+
+# Calculate yearly totals for annotation
+yearly_totals <- data %>%
+  group_by(OCC_YEAR) %>%
+  summarise(Found_Total = sum(Found, na.rm = TRUE), Stolen_Total = sum(Stolen, na.rm = TRUE))
+
+# Plot for Bikes Found with scaled heights and yearly total annotations
+plot_found <- ggplot(data, aes(x = OCC_MONTH_NUM, y = OCC_YEAR, 
+                               height = (Found / max_found) * 4, group = OCC_YEAR)) +
+  geom_ridgeline(
+    fill = "#05595B", color = "white", alpha = 0.5, scale = 1, linewidth = 0
+  ) +
+  labs(y = "", x = NULL) +  # Remove x-axis title
+  theme_minimal() +
+  theme(
+    axis.ticks.y = element_blank(),
+    axis.text.y = element_text(size = 12),
+    axis.text.x = element_text(size = 12, angle = 45, hjust = 1),
+    panel.grid.major.x = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    panel.grid.major.y = element_line(size = 0.5),
+    panel.border = element_blank(),
+    plot.title = element_text(size = 14, color = "#05595B", hjust = -0.1, vjust = 1.5),  # Smaller title
+    panel.background = element_rect(fill = "#faecd5", color = NA),  # Light blue background for plot area
+    plot.background = element_rect(fill = "#faecd5", color = NA)    # Light blue background for overall plot
+  ) +
+  scale_x_discrete(labels = month.abb) +
+  ggtitle("Bikes Found") +  # Add title for Bikes Found
+  geom_text(data = yearly_totals, aes(x = 12.5, y = OCC_YEAR, label = Found_Total), 
+            color = "#05595B", hjust = 1, size = 3, inherit.aes = FALSE)
+
+# Plot for Bikes Stolen with scaled heights, no borders, and yearly total annotations
+plot_stolen <- ggplot(data, aes(x = OCC_MONTH_NUM, y = OCC_YEAR, 
+                                height = (Stolen / max_stolen) * 4, group = OCC_YEAR)) +
+  geom_ridgeline(
+    fill = "#603601", color = "white", alpha = 0.5, scale = 1, linewidth = 0
+  ) +
+  labs(y = "", x = NULL) +  # Remove x-axis title
+  theme_minimal() +
+  theme(
+    axis.ticks.y = element_blank(),
+    axis.text.y = element_text(size = 12),
+    axis.text.x = element_text(size = 12, angle = 45, hjust = 1),
+    panel.grid.major.x = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    panel.grid.major.y = element_line(size = 0.5),
+    panel.border = element_blank(),
+    panel.background = element_rect(fill = "#faecd5", color = NA),  # Light blue background for plot area
+    plot.background = element_rect(fill = "#faecd5", color = NA),   # Light blue background for overall plot
+    plot.title = element_text(size = 14, color = "#603601", hjust = -0.1, vjust = 1.5)  # Smaller title
+  ) +
+  scale_x_discrete(labels = month.abb) +
+  ggtitle("Bikes Stolen") +  # Add title for Bikes Stolen
+  geom_text(data = yearly_totals, aes(x = 12.5, y = OCC_YEAR, label = Stolen_Total), 
+            color = "#603601", hjust = 1, size = 3, inherit.aes = FALSE)
+
+# Combine the plots side by side
+combined_plot <- plot_grid(plot_found, plot_stolen, nrow = 1)
+
+# Display the combined plot
+combined_plot
 
@@
 
-```{r animated_bar_plot, echo=FALSE, message=FALSE, warning=FALSE, results='asis', fig.width=7, fig.height=4}
+```{r animated_bar_plot, echo=FALSE, message=FALSE, warning=FALSE, results='asis', fig.width=7, fig.height=4.5}
 # Libraries
@@
   theme(
-    panel.background = element_rect(fill = "#f0f8ff", color = NA),
-    plot.background = element_rect(fill = "#f0f8ff", color = NA)
+    panel.background = element_rect(fill = "#faecd5", color = NA),
+    plot.background = element_rect(fill = "#faecd5", color = NA)
   ) +
@@
     axis.text.x = element_text(angle = 45, hjust = 1),
-    panel.background = element_rect(fill = "#f0f8ff", color = NA),
-    plot.background = element_rect(fill = "#f0f8ff", color = NA)
+    panel.background = element_rect(fill = "#faecd5", color = NA),
+    plot.background = element_rect(fill = "#faecd5", color = NA)
   ) +
@@
 find relevant news and articels to explain it and cite), 用更descriptive的形式去explain 你的visualization plot with proves.
+
+Map
+```{r, include = TRUE, warning = FALSE, message = FALSE}
+# Load cleaned coordinates data
+coordinates_data <- read.csv(here("data/cleaned_coordinates_data.csv"))
+
+# Get bounding box for Toronto (approximate limits for Toronto)
+toronto_bbox <- c(-79.6303856025883, 43.5822069220627, -79.1180336515019, 43.8554571861712)
+
+# Fetch map data from OpenStreetMap (OSM)
+toronto_map <- opq(bbox = toronto_bbox) %>%
+  add_osm_feature(key = "highway", value = "primary") %>%
+  add_osm_feature(key = 'highway', value = 'secondary') %>%
+  add_osm_feature(key = 'highway', value = 'tertiary') %>%
+  add_osm_feature(key = 'highway', value = 'residential') %>%
+  osmdata_sf()
+
+# Convert map data to Simple Features (sf) objects
+streets <- toronto_map$osm_lines
+
+# Plot the map with bike theft locations data
+ggplot() +
+  geom_sf(data = streets, color = "gray", size = 0.3, alpha = 0.6) + # OSM street map layer
+  geom_point(
+    data = coordinates_data, aes(x = longitude, y = latitude),
+    size = 0.5, color = "red"
+  ) + # Bike theft points
+  labs(
+    title = "Map of Bicycle Theft Locations in Toronto",
+    x = "Longitude", y = "Latitude"
+  ) +
+  coord_sf(
+    xlim = c(-79.6303856025883, -79.1180336515019),
+    ylim = c(43.5822069220627, 43.8554571861712), expand = FALSE
+  ) +
+  theme_minimal() +
+  theme(
+    panel.background = element_blank(), # Remove panel background
+    panel.grid.major = element_blank(), # Remove major grid lines
+    panel.grid.minor = element_blank(), # Remove minor grid lines
+    axis.text.x = element_text(angle = 45, hjust = 1)
+  )
+```

### 2024-11-11 paper/test.Rmd
interactive maps draft

```{r, echo=FALSE, warning=FALSE, message=FALSE}
#### Map with Markers ####

# Load necessary libraries
library(dplyr)         # Provides functions for data manipulation.
library(leaflet)       # Enables interactive maps.
library(purrr)         # Contains functional programming tools, used here to walk through data.
library(readr)         # Provides functions to read rectangular data like CSV files.
library(here)          # Helps manage file paths in a more robust way.

# Load your dataset (adjust the file path accordingly)
map_data <- read_csv(here("data", "map_by_neighbourhoods_data.csv"), show_col_types = FALSE)
# Loads the CSV file from the specified path using the 'here()' function for consistent path management.
# 'show_col_types = FALSE' suppresses messages about the data types of each column.

# Create a new column 'magnitude' that counts the total number of occurrences for each value in 'hood_num'
map_data <- map_data %>% 
  group_by(hood_num) %>%       # Groups the data by 'hood_num'.
  mutate(magnitude = n()) %>%  # Adds a 'magnitude' column, which counts the number of rows in each group.
  ungroup()                    # Ungroups the data, making it ready for further manipulations.

# Modify the data frame, categorizing magnitude column
map_data <- map_data %>% 
  mutate(
    mag.level = cut(magnitude, c(100, 500, 1000, 1500),
                    labels = c('> 100 & <=500', '>500 & <=1000', '>1000 & <=1500'))
    # Creates a 'mag.level' column that categorizes 'magnitude' into three levels based on specified ranges.
  ) %>%
  split(.$mag.level)  # Splits the dataset into a list of data frames by 'mag.level'.

# Initialize the leaflet map
l <- leaflet() %>%
  addProviderTiles(providers$Esri.OceanBasemap)
# Initializes a Leaflet map object and adds a base tile layer from the Esri Ocean Basemap provider.

# Add the markers to the map for each magnitude level
names(map_data) %>%
  walk(function(df) {
    l <<- l %>% 
      addMarkers(
        data = map_data[[df]], lng = ~longitude, lat = ~latitude,
        label = ~as.character(magnitude), popup = ~as.character(magnitude),
        group = df,
        clusterOptions = markerClusterOptions()
      )
  })
# Iterates over the names of the 'map_data' list (which are the different 'mag.level' categories).
# For each category, it adds markers to the map:
# - `data = map_data[[df]]`: Uses the split data for the current magnitude level.
# - `lng = ~longitude, lat = ~latitude`: Sets longitude and latitude for marker placement.
# - `label` and `popup`: Display the 'magnitude' value when markers are clicked or hovered over.
# - `group = df`: Groups the markers by 'mag.level'.
# - `clusterOptions = markerClusterOptions()`: Enables clustering of markers for better visualization.

# Add layer controls and a minimap
l <- l %>%
  addLayersControl(
    overlayGroups = names(map_data),
    options = layersControlOptions(collapsed = FALSE)
  ) %>%
  addMiniMap(tiles = providers$Esri.OceanBasemap, width = 120, height = 80)
# Adds layer controls to allow switching between different 'mag.level' categories on the map.
# Adds a minimap showing a small overview of the area using the Esri Ocean Basemap.

# Display the Map
l
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
#### Map with Areas ####

# Load necessary libraries
library(dplyr)
library(readr)
library(ggplot2)
library(plotly)
library(sf)
library(crosstalk)
library(here)
library(osmdata)

# Load your dataset (adjust the file path accordingly)
map_data <- read_csv(here("data", "map_by_neighbourhoods_data.csv"), show_col_types = FALSE)

# Create a new column 'magnitude' that counts the total number of occurrences for each value in 'hood_num'
map_data <- map_data %>% 
  group_by(hood_num) %>% 
  summarise(
    magnitude = n(),
    longitude = mean(longitude),
    latitude = mean(latitude)
  ) %>% 
  ungroup()

# Get bounding box for Toronto (approximate limits for Toronto)
toronto_bbox <- c(-79.6303856025883, 43.5822069220627, -79.1180336515019, 43.8554571861712)

# Fetch map data from OpenStreetMap (OSM)
toronto_map <- opq(bbox = toronto_bbox) %>%
  add_osm_feature(key = "highway", value = "primary") %>%
  add_osm_feature(key = "highway", value = "secondary") %>%
  add_osm_feature(key = "highway", value = "tertiary") %>%
  add_osm_feature(key = "highway", value = "residential") %>%
  osmdata_sf()

# Convert map data to Simple Features (sf) objects
streets <- toronto_map$osm_lines

# Generate a similar plot using ggplot2 and plotly
shared_data <- crosstalk::SharedData$new(map_data)

# Create ggplot object with the dataset and Toronto map as a background
ggplot_map <- ggplot() +
  geom_sf(data = streets, color = "gray", size = 0.3, alpha = 0.6) +  # Add OSM street map layer
  geom_point(data = shared_data, aes(x = longitude, y = latitude, color = magnitude, size = magnitude)) +
  coord_sf(
    xlim = c(-79.6303856025883, -79.1180336515019),
    ylim = c(43.5822069220627, 43.8554571861712), expand = FALSE
  ) +
  theme_minimal() +
  labs(title = "Toronto Neighbourhood Data", x = "Longitude", y = "Latitude") +
  theme(
    panel.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

# Convert ggplot object to interactive plotly object
plotly_map <- ggplotly(ggplot_map) %>%
  highlight(
    on = "plotly_hover",
    off = "plotly_doubleclick",
    selected = attrs_selected(line = list(color = "black"))
  )

# Display the interactive plotly map
plotly_map
```

### 2024-11-11 scripts/data_map_clean.R

@@ -16,7 +16,8 @@ raw_data <- read_csv(here("data", "Bicycle_Thefts_Open_Data.csv"))
 
 # Select only the specified columns and rename them
 cleaned_data <- raw_data %>%
-  select(hood_num = HOOD_158, longitude = LONG_WGS84, latitude = LAT_WGS84)
+  select(hood_num = HOOD_158, longitude = LONG_WGS84, latitude = LAT_WGS84) %>%
+  filter(hood_num != "NSA")
 
 # Save the cleaned dataset
 write_csv(cleaned_data, here("data", "map_by_neighbourhoods_data.csv"))

### 2024-11-12 paper/test.Rmd
interactive maps revised

@@
 
-# Create a new column 'magnitude' that counts the total number of occurrences for each value in 'hood_num'
-map_data <- map_data %>% 
-  group_by(hood_num) %>%       # Groups the data by 'hood_num'.
-  mutate(magnitude = n()) %>%  # Adds a 'magnitude' column, which counts the number of rows in each group.
-  ungroup()                    # Ungroups the data, making it ready for further manipulations.
-
-# Modify the data frame, categorizing magnitude column
+# Modify the data frame, categorizing case_num column
 map_data <- map_data %>% 
   mutate(
-    mag.level = cut(magnitude, c(100, 500, 1000, 1500),
+    mag.level = cut(case_num, c(100, 500, 1000, 1500),
                     labels = c('> 100 & <=500', '>500 & <=1000', '>1000 & <=1500'))
-    # Creates a 'mag.level' column that categorizes 'magnitude' into three levels based on specified ranges.
+    # Creates a 'mag.level' column that categorizes 'case_num' into three levels based on specified ranges.
   ) %>%
@@
 
-# Add the markers to the map for each magnitude level
+# Add the markers to the map for each case_num level
 names(map_data) %>%
@@
         data = map_data[[df]], lng = ~longitude, lat = ~latitude,
-        label = ~as.character(magnitude), popup = ~as.character(magnitude),
+        label = ~paste0("Hood: ", hood_name, " | Stolen Place: ", stolen_place, " | Cost: ", cost, " | Status: ", status),
+        popup = ~paste0(
+          "Hood: ", hood_name, "<br>",
+          "Stolen Place: ", stolen_place, "<br>",
+          "Cost: ", cost, "<br>",
+          "Status: ", status, "<br>",
+          "Case in area: ", case_num
+        ),
         group = df,
@@
 # For each category, it adds markers to the map:
-# - `data = map_data[[df]]`: Uses the split data for the current magnitude level.
+# - `data = map_data[[df]]`: Uses the split data for the current case_num level.
 # - `lng = ~longitude, lat = ~latitude`: Sets longitude and latitude for marker placement.
-# - `label` and `popup`: Display the 'magnitude' value when markers are clicked or hovered over.
+# - `label`: Displays the 'case_num' value when markers are hovered over.
+# - `popup`: Displays additional information (hood_num, stolen_place, cost, status, and case_num) when a marker is clicked.
 # - `group = df`: Groups the markers by 'mag.level'.
@@
 # Load your dataset (adjust the file path accordingly)
-map_data <- read_csv(here("data", "map_by_neighbourhoods_data.csv"), show_col_types = FALSE)
-
-# Create a new column 'magnitude' that counts the total number of occurrences for each value in 'hood_num'
-map_data <- map_data %>% 
-  group_by(hood_num) %>% 
-  summarise(
-    magnitude = n(),
-    longitude = mean(longitude),
-    latitude = mean(latitude)
-  ) %>% 
-  ungroup()
+map_data <- read_csv(here("data", "map_by_area_data.csv"), show_col_types = FALSE)
 
@@
 toronto_map <- opq(bbox = toronto_bbox) %>%
-  add_osm_feature(key = "highway", value = "primary") %>%
-  add_osm_feature(key = "highway", value = "secondary") %>%
-  add_osm_feature(key = "highway", value = "tertiary") %>%
-  add_osm_feature(key = "highway", value = "residential") %>%
+  add_osm_feature(key = "boundary", value = "administrative") %>%
+#  add_osm_feature(key = "highway", value = "primary") %>%
+#  add_osm_feature(key = "highway", value = "secondary") %>%
+#  add_osm_feature(key = "highway", value = "tertiary") %>%
+#  add_osm_feature(key = "highway", value = "residential") %>%
   osmdata_sf()
@@
 ggplot_map <- ggplot() +
-  geom_sf(data = streets, color = "gray", size = 0.3, alpha = 0.6) +  # Add OSM street map layer
-  geom_point(data = shared_data, aes(x = longitude, y = latitude, color = magnitude, size = magnitude)) +
+  geom_sf(data = streets, color = "lightgray", size = 0.3, alpha = 0.6) +  # Add OSM street map layer
+  geom_point(data = shared_data, aes(x = longitude, y = latitude, color = case_num, size = case_num, 
+                                     text = paste("Total Cases: ", case_num, " | Area Name: ", area_name))) +
   coord_sf(
@@
   theme_minimal() +
-  labs(title = "Toronto Neighbourhood Data", x = "Longitude", y = "Latitude") +
+  labs(title = "Toronto Neighbourhood Data by Area", x = "Longitude", y = "Latitude", color = "Number of Cases", size = "Total Cases") +
   theme(
@@
     axis.text.x = element_text(angle = 45, hjust = 1)
-  )
+  ) +
+  scale_color_continuous(labels = scales::comma)
 
 # Convert ggplot object to interactive plotly object
-plotly_map <- ggplotly(ggplot_map) %>%
+plotly_map <- ggplotly(ggplot_map, tooltip = "text") %>%
   highlight(

### 2024-11-12 scripts/data_map_clean.R

@@ -10,52 +10,81 @@ raw_data <- read_csv(here("data", "Bicycle_Thefts_Open_Data.csv"))
 
 
 
-#### Clean Data ####
-# Read in the data
-raw_data <- read_csv(here("data", "Bicycle_Thefts_Open_Data.csv"))
+#### Define area categories ####
+north_york <- c(151, 153, 152, 149, 130, 131, 132, 155, 154, 173, 150, 118, 119, 120)
+scarborough <- c(143, 145, 146, 144, 142, 135, 156, 157, 136, 134, 133, 148, 147)
+downtown_toronto <- c(166, 169, 170, 168, 167, 165, 163, 164, 82, 83, 95, 79, 70, 71)
+etobicoke <- c(158, 159, 161, 160)
+york <- c(107, 109, 171)
+east_york <- c(100, 102)
 
-# Select only the specified columns and rename them
+
+
+#### Clean Data 1 ####
+# Select the specified columns, rename them, and filter out invalid values
 cleaned_data <- raw_data %>%
-  select(hood_num = HOOD_158, longitude = LONG_WGS84, latitude = LAT_WGS84) %>%
-  filter(hood_num != "NSA")
+  select(
+    longitude = LONG_WGS84,
+    latitude = LAT_WGS84,
+    stolen_place = PREMISES_TYPE,
+    cost = BIKE_COST,
+    status = STATUS,
+    hood_num = HOOD_158,
+    hood_name = NEIGHBOURHOOD_158
+  ) %>%
+  filter(hood_num != "NSA") %>%
+  group_by(hood_num) %>%
+  mutate(case_num = n()) %>%
+  ungroup()
 
-# Save the cleaned dataset
-write_csv(cleaned_data, here("data", "map_by_neighbourhoods_data.csv"))
+# Save data with only the required columns
+final_data <- cleaned_data %>%
+  select(longitude, latitude, stolen_place, cost, status, hood_num, hood_name, case_num)
 
-# Define neighborhood classification lists
-north_york <- c("151", "153", "152", "149", "130", "131", "132", "155", "154", "173", "150", "118", "119", "120")
-scarborough <- c("143", "145", "146", "144", "142", "135", "156", "157", "136", "134", "133", "148", "147")
-toronto_downtown_central <- c("166", "169", "170", "168", "167", "165", "163", "164", "82", "83", "95")
-etobicoke <- c("158", "159", "161", "160")
-york <- c("107", "109", "171")
[…]

### 2024-11-12 scripts/data_map_clean.R
data updated

@@ -64,10 +64,10 @@ cleaned_data_2 <- cleaned_data %>%
       hood_num %in% downtown_toronto ~ "Downtown Toronto",
       hood_num %in% etobicoke ~ "Etobicoke",
       hood_num %in% york ~ "York",
-      hood_num %in% east_york ~ "East York",
-      TRUE ~ "Others"
+      hood_num %in% east_york ~ "East York"
     )
   ) %>%
+  filter(area_name != "Others") %>%
   group_by(area_num, area_name) %>%
   summarize(
     longitude = mean(longitude, na.rm = TRUE),
@@ -76,15 +76,8 @@ cleaned_data_2 <- cleaned_data %>%
     .groups = 'drop'
   )
 
-cleaned_data_2 <- cleaned_data_2 %>%
-  mutate(
-    latitude = if_else(area_name == "Others", 43.8, latitude),
-    longitude = if_else(area_name == "Others", -79.4, longitude)
-  )
-
 # Save summarized data
 write_csv(cleaned_data_2, here("data", "map_by_area_data.csv"))
-
 
 
 

### 2024-11-12 paper/paper.Rmd
interactive maps added, maps section first draft

--- 2024-11-10 paper/paper.Rmd
@@
 
-```{r, include = FALSE, warning = FALSE, message = FALSE}
-knitr::opts_chunk$set(echo = FALSE, include=TRUE, eval=TRUE)
-
-required_packages <- c("lubridate", "sf", "tidyverse", "readr", "here", "osmdata", "ggplot2")
-for (p in required_packages) {
-  if (!require(p, character.only = TRUE)) {
-    install.packages(p, character.only = TRUE)
-  }
-}
-
-library(lubridate)
-library(tidyverse)
-library(ggplot2)
-library(osmdata)
-library(readr)
-library(here)
-library(sf)
-
-# you are welcome to use either the CSV file or the GeoJSON file
-# GeoJSON format maybe useful if you would like to combine
-# an external geospatial dataset
-bike_thefts_csv <- read_csv(here("data/clean_data.csv")) |>
-  mutate(
-    occurence_date = as_date(
-      OCC_DATE, format = "%a, %d %b %Y %H:%M:%S GMT"
-    ),
-    report_date = as_date(
-      REPORT_DATE, format = "%a, %d %b %Y %H:%M:%S GMT"
-    )
-  )
-bike_thefts_sf <- read_sf(here("data/Bicycle_Thefts_Open_Data.geojson")) |>
-  mutate(
-    occurence_date = as_date(
-      OCC_DATE, format = "%a, %d %b %Y %H:%M:%S GMT"
-    ),
-    report_date = as_date(
-      REPORT_DATE, format = "%a, %d %b %Y %H:%M:%S GMT"
-    )
-  )
-```
-Map
-```{r, include = TRUE, warning = FALSE, message = FALSE}
-# Load cleaned coordinates data
-coordinates_data <- read.csv(here("data/cleaned_coordinates_data.csv"))
-
-# Get bounding box for Toronto (approximate limits for Toronto)
-toronto_bbox <- c(-79.6303856025883, 43.5822069220627, -79.1180336515019, 43.8554571861712)
-
-# Fetch map data from OpenStreetMap (OSM)
-toronto_map <- opq(bbox = toronto_bbox) %>%
-  add_osm_feature(key = "highway", value = "primary") %>%
-  add_osm_feature(key = 'highway', value = 'secondary') %>%
-  add_osm_feature(key = 'highway', value = 'tertiary') %>%
-  add_osm_feature(key = 'highway', value = 'residential') %>%
-  osmdata_sf()
-
-# Convert map data to Simple Features (sf) objects
-streets <- toronto_map$osm_lines
-
-# Plot the map with bike theft locations data
-ggplot() +
-  geom_sf(data = streets, color = "gray", size = 0.3, alpha = 0.6) + # OSM street map layer
-  geom_point(
-    data = coordinates_data, aes(x = longitude, y = latitude),
-    size = 0.5, color = "red"
-  ) + # Bike theft points
-  labs(
-    title = "Map of Bicycle Theft Locations in Toronto",
-    x = "Longitude", y = "Latitude"
-  ) +
-  coord_sf(
-    xlim = c(-79.6303856025883, -79.1180336515019),
-    ylim = c(43.5822069220627, 43.8554571861712), expand = FALSE
-  ) +
-  theme_minimal() +
-  theme(
-    panel.background = element_blank(), # Remove panel background
-    panel.grid.major = element_blank(), # Remove major grid lines
-    panel.grid.minor = element_blank(), # Remove minor grid lines
-    axis.text.x = element_text(angle = 45, hjust = 1)
-  )
-```
 # introduction
@@
 
-```{r mothly_plot, include = TRUE, warning = FALSE, message = FALSE, fig.width=11, fig.height=5}
+```{r mothly_plot, echo=FALSE, warning = FALSE, message = FALSE, fig.width=11, fig.height=5}
 # Load necessary libraries
@@
 # Mapping the Danger Zones: High-Risk Locations Across Toronto
-Use a map visualization to highlight theft hotspots across Toronto, pointing out neighborhoods or transit hubs with the highest incidence rates.
 
-- map
+Now imagine you’re navigating the streets of Toronto, trying to understand where bicycle thefts are happening.
+The first chart is like an overhead view from a hot air balloon, showing clusters of incidents with bright orange circles scattered across the landscape.
+Each circle represents a collection of theft reports—smaller bubbles indicate fewer incidents, while larger ones stand like towering beacons, signaling areas of greater vulnerability.
+Downtown Toronto, unsurprisingly, is covered by a massive bubble, indicating that this densely populated urban center has been most affected by bike thefts.
+As we drift north and away from the downtown core, the bubbles shrink, suggesting fewer incidents—likely due to the suburban nature of these areas, where bikes are stored more securely.
+And here's the interactive part—you can click on these bubbles to zoom in and explore specific areas, uncovering the exact locations and getting a more detailed sense of bike stolen cases.
+It's like having a personal guide leading you through the hot spots and quieter neighborhoods.
+
+```{r, echo=FALSE, warning=FALSE, message=FALSE}
+#### Map with Markers ####
+
+# Load necessary libraries
+library(dplyr)         # Provides functions for data manipulation.
+library(leaflet)       # Enables interactive maps.
+library(purrr)         # Contains functional programming tools, used here to walk through data.
+library(readr)         # Provides functions to read rectangular data like CSV files.
+library(here)          # Helps manage file paths in a more robust way.
+
+# Load your dataset (adjust the file path accordingly)
+map_data <- read_csv(here("data", "map_by_neighbourhoods_data.csv"), show_col_types = FALSE)
+# Loads the CSV file from the specified path using the 'here()' function for consistent path management.
+# 'show_col_types = FALSE' suppresses messages about the data types of each column.
+
+# Modify the data frame, categorizing case_num column
+map_data <- map_data %>% 
+  mutate(
+    mag.level = cut(case_num, c(100, 500, 1000, 1500),
+                    labels = c('> 100 & <=500', '>500 & <=1000', '>1000 & <=1500'))
+    # Creates a 'mag.level' column that categorizes 'case_num' into three levels based on specified ranges.
+  ) %>%
+  split(.$mag.level)  # Splits the dataset into a list of data frames by 'mag.level'.
+
+# Initialize the leaflet map
+l <- leaflet() %>%
+  addProviderTiles(providers$Esri.OceanBasemap)
+# Initializes a Leaflet map object and adds a base tile layer from the Esri Ocean Basemap provider.
+
+# Add the markers to the map for each case_num level
+names(map_data) %>%
+  walk(function(df) {
+    l <<- l %>% 
+      addMarkers(
+        data = map_data[[df]], lng = ~longitude, lat = ~latitude,
+        label = ~paste0("Hood: ", hood_name, " | Stolen Place: ", stolen_place, " | Cost: ", cost, " | Status: ", status),
+        popup = ~paste0(
+          "Hood: ", hood_name, "<br>",
+          "Stolen Place: ", stolen_place, "<br>",
+          "Cost: ", cost, "<br>",
+          "Status: ", status, "<br>",
+          "Case in area: ", case_num
+        ),
+        group = df,
+        clusterOptions = markerClusterOptions()
+      )
+  })
+# Iterates over the names of the 'map_data' list (which are the different 'mag.level' categories).
+# For each category, it adds markers to the map:
+# - `data = map_data[[df]]`: Uses the split data for the current case_num level.
+# - `lng = ~longitude, lat = ~latitude`: Sets longitude and latitude for marker placement.
+# - `label`: Displays the 'case_num' value when markers are hovered over.
+# - `popup`: Displays additional information (hood_num, stolen_place, cost, status, and case_num) when a marker is clicked.
+# - `group = df`: Groups the markers by 'mag.level'.
+# - `clusterOptions = markerClusterOptions()`: Enables clustering of markers for better visualization.
+
+# Add layer controls and a minimap
+l <- l %>%
+  addLayersControl(
+    overlayGroups = names(map_data),
+    options = layersControlOptions(collapsed = FALSE)
+  ) %>%
+  addMiniMap(tiles = providers$Esri.OceanBasemap, width = 120, height = 80)
+# Adds layer controls to allow switching between different 'mag.level' categories on the map.
+# Adds a minimap showing a small overview of the area using the Esri Ocean Basemap.
+
+# Display the Map
+l
+```
+
+In the second chart, we dive deeper into the city with a ground-level view—a sea of red dots each marks an individual theft incident.
+The dots are packed tightly in certain neighborhoods, sprawling across downtown Toronto like a dense red blanket.
+It paints a vivid picture of the density of bike thefts—evidence that the bustling central part of the city faces a higher risk.
+Street after street is littered with these red markers, almost as if each streetlight bore witness to a theft.
+There’s a sharp concentration near transit hubs and popular neighborhoods, suggesting a correlation between foot traffic, bike use, and crime opportunity.
+The City has been making efforts to combat this issue; for example, Cycle Toronto launched the #EndBikeTheft campaign, advocating for secure parking and better registration systems, with city discussions exploring collaboration with platforms like 529 Garage to help reduce and recover stolen bikes (@citeEndBikeTheft).
+It’s almost as though you can hear the honks and feel the rush of people in these crowded streets.
+
+```{r, echo=FALSE, warning=FALSE, message=FALSE}
+# Load necessary libraries
+library(ggplot2)
+library(sf)
+library(osmdata)
+library(here)
+
+# Load cleaned coordinates data
+coordinates_data <- read.csv(here("data/cleaned_coordinates_data.csv"))
+
+# Get bounding box for Toronto (approximate limits for Toronto)
+toronto_bbox <- c(-79.6303856025883, 43.5822069220627, -79.1180336515019, 43.8554571861712)
+
+# Fetch map data from OpenStreetMap (OSM)
+toronto_map <- opq(bbox = toronto_bbox) %>%
+  add_osm_feature(key = "highway", value = "primary") %>%
+  add_osm_feature(key = 'highway', value = 'secondary') %>%
+  add_osm_feature(key = 'highway', value = 'tertiary') %>%
+  add_osm_feature(key = 'highway', value = 'residential') %>%
+  osmdata_sf()
+
+# Convert map data to Simple Features (sf) objects
+streets <- toronto_map$osm_lines
+
+# Plot the map with bike theft locations data
+bike_theft_plot <- ggplot() +
+  geom_sf(data = streets, color = "gray", size = 0.3, alpha = 0.6) + # OSM street map layer
+  geom_point(
+    data = coordinates_data, aes(x = longitude, y = latitude),
+    size = 0.5, color = "red"
+  ) + # Bike theft points
+  labs(
+    title = "Map of Stolen Bike Cases in Toronto",
+    x = "Longitude", y = "Latitude"
+  ) +
+  coord_sf(
+    xlim = c(-79.6303856025883, -79.1180336515019),
+    ylim = c(43.5822069220627, 43.8554571861712), expand = FALSE
+  ) +
+  theme_minimal() +
+  theme(
+    panel.background = element_blank(), # Remove panel background
+    panel.grid.major = element_blank(), # Remove major grid lines
+    panel.grid.minor = element_blank(), # Remove minor grid lines
+    axis.text.x = element_text(angle = 45, hjust = 1)
+  )
+
+bike_theft_plot
+```
+
+Finally, the third chart takes a step back to help us understand the data by neighborhood, but this time with broader strokes.
+It presents different regions in Toronto as bubbles of varying sizes and colors, indicating the number of thefts in each.
+The larger and darker the bubble, the more incidents that have occurred there.
+One particular neighborhood stands out—a massive blue circle in the downtown area—it visually reinforces what the other charts have hinted at: that specific neighborhoods, especially those near the core, are the epicenters of bicycle theft.
+Meanwhile, the areas with smaller circles seem almost untouched in comparison, a stark contrast that reveals a city of disparities—some areas buzz with activity and theft risk, while others enjoy relative calm.
+
+```{r, echo=FALSE, warning=FALSE, message=FALSE}
+#### Map with Areas ####
+
+# Load necessary libraries
+library(dplyr)
+library(readr)
+library(ggplot2)
+library(plotly)
+library(sf)
+library(crosstalk)
+library(here)
+library(osmdata)
+
+# Load your dataset (adjust the file path accordingly)
+map_data <- read_csv(here("data", "map_by_area_data.csv"), show_col_types = FALSE)
+
+# Get bounding box for Toronto (approximate limits for Toronto)
+toronto_bbox <- c(-79.6303856025883, 43.5822069220627, -79.1180336515019, 43.8554571861712)
+
+# Fetch map data from OpenStreetMap (OSM)
+toronto_map <- opq(bbox = toronto_bbox) %>%
+  add_osm_feature(key = "boundary", value = "administrative") %>%
+  osmdata_sf()
+
+# Convert map data to Simple Features (sf) objects
+streets <- toronto_map$osm_lines
+
+# Generate a similar plot using ggplot2 and plotly
+shared_data <- crosstalk::SharedData$new(map_data)
+
+# Create ggplot object with the dataset and Toronto map as a background
+ggplot_map <- ggplot() +
+  geom_sf(data = streets, color = "lightgray", size = 0.3, alpha = 0.6) +  # Add OSM street map layer
+  geom_point(data = shared_data, aes(x = longitude, y = latitude, color = case_num, size = case_num, 
+                                     text = paste("Total Cases: ", case_num, " | Area Name: ", area_name))) +
+  coord_sf(
+    xlim = c(-79.6303856025883, -79.1180336515019),
+    ylim = c(43.5822069220627, 43.8554571861712), expand = FALSE
+  ) +
+  theme_minimal() +
+  labs(title = "Toronto Stolen Bike Case Numbers by Area", x = "Longitude", y = "Latitude", color = "Number of Cases", size = "Total Cases") +
+  theme(
+    panel.background = element_blank(),
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    axis.text.x = element_text(angle = 45, hjust = 1)
+  ) +
+  scale_color_continuous(labels = scales::comma) +
+  scale_size_continuous(range = c(3, 12)) # Adjust range values to control the size of points
+
+# Convert ggplot object to interactive plotly object
+plotly_map <- ggplotly(ggplot_map, tooltip = "text") %>%
+  highlight(
+    on = "plotly_hover",
+    off = "plotly_doubleclick",
+    selected = attrs_selected(line = list(color = "black"))
+  )
+
+plotly_map
+```
 
@@
 find relevant news and articels to explain it and cite), 用更descriptive的形式去explain 你的visualization plot with proves.
+
+# Citation

### 2024-11-12 paper/paper.Rmd
paper revised

--- 2024-11-11 paper/paper.Rmd
@@
 # Mapping the Danger Zones: High-Risk Locations Across Toronto
-Use a map visualization to highlight theft hotspots across Toronto, pointing out neighborhoods or transit hubs with the highest incidence rates.
 
-- map
+# Mapping the Danger Zones: High-Risk Locations Across Toronto
 
-# Discussion 
-- Consolidation of all the info that we present, we first talk about...this is how all visualizations are connected together, in the future what can be done...
+Now imagine you’re navigating the streets of Toronto, trying to understand where bicycle thefts are happening.
+The first chart is like an overhead view from a hot air balloon, showing clusters of incidents with bright orange circles scattered across the landscape.
+Each circle represents a collection of theft reports—smaller bubbles indicate fewer incidents, while larger ones stand like towering beacons, signaling areas of greater vulnerability.
+Downtown Toronto, unsurprisingly, is covered by a massive bubble, indicating that this densely populated urban center has been most affected by bike thefts.
+As we drift north and away from the downtown core, the bubbles shrink, suggesting fewer incidents—likely due to the suburban nature of these areas, where bikes are stored more securely.
+And here's the interactive part—you can click on these bubbles to zoom in and explore specific areas, uncovering the exact locations and getting a more detailed sense of bike stolen cases.
+It's like having a personal guide leading you through the hot spots and quieter neighborhoods.
 
-# Conclusion
-- short reminder for the audience, tips to protect their bikes
+```{r, echo=FALSE, warning=FALSE, message=FALSE}
+#### Map with Markers ####
 
-General tips: 
- - This paper wants to tell the story about tips to protect bikes
+# Load necessary libraries
+library(dplyr)         # Provides functions for data manipulation.
+library(leaflet)       # Enables interactive maps.
+library(purrr)         # Contains functional programming tools, used here to walk through data.
+library(readr)         # Provides functions to read rectangular data like CSV files.
+library(here)          # Helps manage file paths in a more robust way.
 
- - after every visualizations talk a bit about the visualization itself, key points, make sure the story that we are talking about is proved by this visualization so each plot make sense (for example in 2016 there is a peak in May illustrated by the visualization, why?
-find relevant news and articels to explain it and cite), 用更descriptive的形式去explain 你的visualization plot with proves.
+# Load your dataset (adjust the file path accordingly)
+map_data <- read_csv(here("data", "map_by_neighbourhoods_data.csv"), show_col_types = FALSE)
+# Loads the CSV file from the specified path using the 'here()' function for consistent path management.
+# 'show_col_types = FALSE' suppresses messages about the data types of each column.
 
-Map
-```{r, include = TRUE, warning = FALSE, message = FALSE}
+# Modify the data frame, categorizing case_num column
+map_data <- map_data %>% 
+  mutate(
+    mag.level = cut(case_num, c(100, 500, 1000, 1500),
+                    labels = c('> 100 & <=500', '>500 & <=1000', '>1000 & <=1500'))
+    # Creates a 'mag.level' column that categorizes 'case_num' into three levels based on specified ranges.
+  ) %>%
+  split(.$mag.level)  # Splits the dataset into a list of data frames by 'mag.level'.
+
+# Initialize the leaflet map
+l <- leaflet() %>%
+  addProviderTiles(providers$Esri.OceanBasemap)
+# Initializes a Leaflet map object and adds a base tile layer from the Esri Ocean Basemap provider.
+
+# Add the markers to the map for each case_num level
+names(map_data) %>%
+  walk(function(df) {
+    l <<- l %>% 
+      addMarkers(
+        data = map_data[[df]], lng = ~longitude, lat = ~latitude,
+        label = ~paste0("Hood: ", hood_name, " | Stolen Place: ", stolen_place, " | Cost: ", cost, " | Status: ", status),
+        popup = ~paste0(
+          "Hood: ", hood_name, "<br>",
+          "Stolen Place: ", stolen_place, "<br>",
+          "Cost: ", cost, "<br>",
+          "Status: ", status, "<br>",
+          "Case in area: ", case_num
+        ),
+        group = df,
+        clusterOptions = markerClusterOptions()
+      )
+  })
+# Iterates over the names of the 'map_data' list (which are the different 'mag.level' categories).
+# For each category, it adds markers to the map:
+# - `data = map_data[[df]]`: Uses the split data for the current case_num level.
+# - `lng = ~longitude, lat = ~latitude`: Sets longitude and latitude for marker placement.
+# - `label`: Displays the 'case_num' value when markers are hovered over.
+# - `popup`: Displays additional information (hood_num, stolen_place, cost, status, and case_num) when a marker is clicked.
+# - `group = df`: Groups the markers by 'mag.level'.
+# - `clusterOptions = markerClusterOptions()`: Enables clustering of markers for better visualization.
+
+# Add layer controls and a minimap
+l <- l %>%
+  addLayersControl(
+    overlayGroups = names(map_data),
+    options = layersControlOptions(collapsed = FALSE)
+  ) %>%
+  addMiniMap(tiles = providers$Esri.OceanBasemap, width = 120, height = 80)
+# Adds layer controls to allow switching between different 'mag.level' categories on the map.
+# Adds a minimap showing a small overview of the area using the Esri Ocean Basemap.
+
+# Display the Map
+l
+```
+
+In the second chart, we dive deeper into the city with a ground-level view—a sea of red dots each marks an individual theft incident.
+The dots are packed tightly in certain neighborhoods, sprawling across downtown Toronto like a dense red blanket.
+It paints a vivid picture of the density of bike thefts—evidence that the bustling central part of the city faces a higher risk.
+Street after street is littered with these red markers, almost as if each streetlight bore witness to a theft.
+There’s a sharp concentration near transit hubs and popular neighborhoods, suggesting a correlation between foot traffic, bike use, and crime opportunity.
+The City has been making efforts to combat this issue; for example, Cycle Toronto launched the #EndBikeTheft campaign, advocating for secure parking and better registration systems, with city discussions exploring collaboration with platforms like 529 Garage to help reduce and recover stolen bikes (@citeEndBikeTheft).
+It’s almost as though you can hear the honks and feel the rush of people in these crowded streets.
+
+```{r, echo=FALSE, warning=FALSE, message=FALSE}
+# Load necessary libraries
+library(ggplot2)
+library(sf)
+library(osmdata)
+library(here)
+
 # Load cleaned coordinates data
@@
 # Plot the map with bike theft locations data
-ggplot() +
+bike_theft_plot <- ggplot() +
   geom_sf(data = streets, color = "gray", size = 0.3, alpha = 0.6) + # OSM street map layer
@@
   labs(
-    title = "Map of Bicycle Theft Locations in Toronto",
+    title = "Map of Stolen Bike Cases in Toronto",
     x = "Longitude", y = "Latitude"
@@
   )
+
+bike_theft_plot
 ```
+
+Finally, the third chart takes a step back to help us understand the data by neighborhood, but this time with broader strokes.
+It presents different regions in Toronto as bubbles of varying sizes and colors, indicating the number of thefts in each.
+The larger and darker the bubble, the more incidents that have occurred there.
+One particular neighborhood stands out—a massive blue circle in the downtown area—it visually reinforces what the other charts have hinted at: that specific neighborhoods, especially those near the core, are the epicenters of bicycle theft.
+Meanwhile, the areas with smaller circles seem almost untouched in comparison, a stark contrast that reveals a city of disparities—some areas buzz with activity and theft risk, while others enjoy relative calm.
+
+```{r, echo=FALSE, warning=FALSE, message=FALSE}
+#### Map with Areas ####
+
+# Load necessary libraries
+library(dplyr)
+library(readr)
+library(ggplot2)
+library(plotly)
+library(sf)
+library(crosstalk)
+library(here)
+library(osmdata)
+
+# Load your dataset (adjust the file path accordingly)
+map_data <- read_csv(here("data", "map_by_area_data.csv"), show_col_types = FALSE)
+
+# Get bounding box for Toronto (approximate limits for Toronto)
+toronto_bbox <- c(-79.6303856025883, 43.5822069220627, -79.1180336515019, 43.8554571861712)
+
+# Fetch map data from OpenStreetMap (OSM)
+toronto_map <- opq(bbox = toronto_bbox) %>%
+  add_osm_feature(key = "boundary", value = "administrative") %>%
+  osmdata_sf()
+
+# Convert map data to Simple Features (sf) objects
+streets <- toronto_map$osm_lines
+
+# Generate a similar plot using ggplot2 and plotly
+shared_data <- crosstalk::SharedData$new(map_data)
+
+# Create ggplot object with the dataset and Toronto map as a background
+ggplot_map <- ggplot() +
+  geom_sf(data = streets, color = "lightgray", size = 0.3, alpha = 0.6) +  # Add OSM street map layer
+  geom_point(data = shared_data, aes(x = longitude, y = latitude, color = case_num, size = case_num, 
+                                     text = paste("Total Cases: ", case_num, " | Area Name: ", area_name))) +
+  coord_sf(
+    xlim = c(-79.6303856025883, -79.1180336515019),
+    ylim = c(43.5822069220627, 43.8554571861712), expand = FALSE
+  ) +
+  theme_minimal() +
+  labs(title = "Toronto Stolen Bike Case Numbers by Area", x = "Longitude", y = "Latitude", color = "Number of Cases", size = "Total Cases") +
+  theme(
+    panel.background = element_blank(),
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    axis.text.x = element_text(angle = 45, hjust = 1)
+  ) +
+  scale_color_continuous(labels = scales::comma) +
+  scale_size_continuous(range = c(3, 12)) # Adjust range values to control the size of points
+
+# Convert ggplot object to interactive plotly object
+plotly_map <- ggplotly(ggplot_map, tooltip = "text") %>%
+  highlight(
+    on = "plotly_hover",
+    off = "plotly_doubleclick",
+    selected = attrs_selected(line = list(color = "black"))
+  )
+
+plotly_map
+```
+
+# Discussion 
+- Consolidation of all the info that we present, we first talk about...this is how all visualizations are connected together, in the future what can be done...
+
+# Conclusion
+- short reminder for the audience, tips to protect their bikes
+
+General tips: 
+ - This paper wants to tell the story about tips to protect bikes
+
+ - after every visualizations talk a bit about the visualization itself, key points, make sure the story that we are talking about is proved by this visualization so each plot make sense (for example in 2016 there is a peak in May illustrated by the visualization, why?
+find relevant news and articels to explain it and cite), 用更descriptive的形式去explain 你的visualization plot with proves.
+
+# Citation

### 2024-11-12 scripts/maps.R
charts exploration

@@ -1,0 +1,299 @@
+
+#### Setup #####
+# Libraries
+required_packages <- c("sf", "tidyverse", "here", "osmdata", "ggplot2")
+for (p in required_packages) {
+  if (!require(p, character.only = TRUE)) {
+    install.packages(p, character.only = TRUE)
+  }
+}
+
+library(tidyverse)
+library(ggplot2)
+library(osmdata)
+library(here)
+library(sf)
+
+
+
+#### Chart 5 #####
+# Load North York data
+north_york_data <- read_csv(here("data", "north_york_data.csv"))
+
+# Get bounding box for Toronto (approximate limits for Toronto)
+toronto_bbox <- c(-79.6303856025883, 43.5822069220627, -79.1180336515019, 43.8554571861712)
+
+# Fetch map data from OpenStreetMap (OSM)
+toronto_map <- opq(bbox = toronto_bbox) %>%
+  add_osm_feature(key = "highway", value = "primary") %>%
+  add_osm_feature(key = 'highway', value = 'secondary') %>%
+  add_osm_feature(key = 'highway', value = 'tertiary') %>%
+  add_osm_feature(key = 'highway', value = 'residential') %>%
+  osmdata_sf()
+
+# Convert map data to Simple Features (sf) objects
+streets <- toronto_map$osm_lines
+
+# Plot the map with North York bike theft locations data
+ggplot() +
+  geom_sf(data = streets, color = "gray", size = 0.3, alpha = 0.6) + # OSM street map layer
+  geom_point(
+    data = north_york_data, aes(x = longitude, y = latitude),
+    size = 0.5, color = "red"
+  ) + # Bike theft points
+  labs(
+    title = "Map of Bicycle Theft Locations in North York",
+    x = "Longitude", y = "Latitude"
+  ) +
+  coord_sf(
+    xlim = c(-79.6303856025883, -79.1180336515019),
+    ylim = c(43.5822069220627, 43.8554571861712), expand = FALSE
+  ) +
+  theme_minimal() +
+  theme(
+    panel.background = element_blank(), # Remove panel background
+    panel.grid.major = element_blank(), # Remove major grid lines
+    panel.grid.minor = element_blank(), # Remove minor grid lines
+    axis.text.x = element_text(angle = 45, hjust = 1)
+  )
+
+# Save the plot
+ggsave(here("other/charts/north_york_bicycle_theft_map.png"))
+
+
+
+#### Chart 6 #####
+# Load North York data
[…]

### 2024-11-12 paper/paper.Rmd
Add descriptions to each section and edit format

@@
 ---
-thanks: "Code and data are available at: [https://github.com/iJustinn/Toronto_Bicycle_Thefts/tree/main](https://github.com/iJustinn/Toronto_Bicycle_Thefts/tree/main)."
 output: html_document
 bibliography: references.bib
----
----
-output: html_document
+thanks: "Code and data are available at: [https://github.com/iJustinn/Toronto_Bicycle_Thefts/tree/main](https://github.com/iJustinn/Toronto_Bicycle_Thefts/tree/main)."
 ---
 
-<!-- Background image -->
 <style>
-body {
-  background-image: url('bikes1.jpg');
+/* Container for title, subtitle, description, author, and date with background image */
+.header-section {
+  background-image: url('bikes.jpg'); 
   background-size: cover;
@@
   background-attachment: fixed;
+  padding: 50px;
   color: white;
-  font-family: Arial, sans-serif;
 }
@@
 .title {
-  font-size: 60px;
-  font-weight: bold;
-  color: #FFC107; /* Yellow color */
-  margin-top: 100px;
-  text-align: left;
-  font-family: 'Georgia'
+  font-size: 70px;            /* Larger font size for the main title */
+  font-weight: bold;          /* Bold font weight for emphasis */
+  color: #FFC107;             /* Yellow color similar to the example */
+  text-align: left;           /* Align text to the left */
+  font-family: Georgia, serif; /* Use Georgia or a similar serif font */
+  margin: 0;
+  line-height: 1.1;           /* Tighter line height */
 }
@@
 .subtitle {
-  font-size: 35px;
-  font-weight: normal;
-  color: white;
-  text-align: left;
+  font-size: 40px;            /* Slightly larger font size for the subtitle */
+  font-weight: normal;        /* Normal font weight */
+  color: white;               /* White color for the subtitle */
+  text-align: left;           /* Align text to the left */
+  font-family: 'Times New Roman', Times, serif; /* A serif font for contrast */
   margin-top: 10px;
-  font-family: 'Open Sans', sans-serif;
+  line-height: 1.2;           /* Adjust line height for spacing */
 }
@@
 .description {
-  font-size: 18px;
+  display: block; /* Makes span act like a block element */
+  font-size: 20px;
   font-weight: normal;
-  color: white;
+  font-style: italic; /* Makes the text italic */
   line-height: 1.6;
@@
   margin-top: 20px;
-  font-family: 'Lora'
+  font-family: "Times New Roman", Times, serif; /* Change to desired font */
+  background-color: transparent !important;
+  border: none !important;
+  padding: 0 !important;
+  box-shadow: none !important;
 }
@@
 }
+
+.main-body {
+  font-size: 18px;            /* Slightly larger font for readability */
+  font-weight: 300;           /* Light font weight for a softer tone */
+  color: black;             
+  line-height: 1.8;           /* Increased line height for readability */
+  text-align: justify;        /* Justified alignment for a clean look */
+  max-width: 800px;           /* Limit width to keep text contained */
+  margin: 0 auto;             /* Center the introduction on the page */
+  padding: 20px;              /* Add padding around the text */
+  font-family: 'Georgia', serif; /* Use a classic serif font */
+}
+
+.section-heading {
+  max-width: 800px;              /* Limit the width */
+  margin: 30px auto 20px auto;   /* Center the heading on the page */
+  padding-bottom: 5px;           /* Space below for the underline */
+  border-bottom: 2px solid #FFC107; /* Optional yellow underline */
+}
+
+.section-title-line1 {
+  font-size: 35px;               /* Larger font size for the first line */
+  font-weight: bold;             /* Bold weight for emphasis */
+  color: #FFC107;                /* Dark yellow color */
+  text-align: left;              /* Align text to the left */
+  font-family: 'Georgia', serif; /* Serif font */
+  display: block;                /* Ensures each line appears separately */
+}
+
+.section-title-line2 {
+  font-size: 25px;               /* Slightly smaller font for the second line */
+  font-weight: normal;           /* Regular weight */
+  color: #603601;                /* Dark color for contrast */
+  text-align: left;              /* Align text to the left */
+  font-family: 'Georgia', serif; /* Serif font */
+  display: block;                /* Ensures each line appears separately */
+  margin-top: -5px;               /* Adds some spacing between lines */
+}
+
 </style>
 
+<!-- Header section with background image -->
+<div class="header-section">
   <div class="title">Ride at Your Own Risk: Insights into Toronto’s Bicycle Theft Hotspots</div>
-
   <div class="subtitle">Navigating Toronto’s streets with eyes wide open, this data-driven guide helps cyclists stay ahead of bicycle thieves.</div>
 
-<div class="description">
+  <!-- Using span instead of div for description -->
+  <span class="description">
     Each year, countless bikes disappear from Toronto’s streets, leaving cyclists frustrated and vulnerable.
@@
 With data spanning over a decade, we reveal theft hotspots and provide tips to help keep your bike safe.
+  </span>
+
+  <div class="author-date">Yingke He, Ziheng Zhong<br>November 12, 2024</div>
 </div>
 
-<div class="author-date">Yingke He, Ziheng Zhong<br>November 12, 2024</div>
+<!-- Main article content without background image -->
+<div class="main-body">
+  <p>Imagine locking up your bike on a bustling Toronto street, feeling reassured that a strong lock and some common sense will keep it safe.
+But what if certain seasons, specific bike types, or even certain neighborhoods increase your risk of theft far more than you realize?
+For many cyclists, bike theft has moved from a distant possibility to an everyday concern, with data revealing just how pervasive the risk can be in Toronto.</p>
+
+  <p>In this analysis, we dig into over a decade’s worth of data from the <a href="https://data.torontopolice.on.ca/datasets/TorontoPS::bicycle-thefts-open-data/about" target="_blank" style="color: #FFC107; text-decoration: underline;">Toronto Police Service</a> to answer key questions: When are bikes at the greatest risk?
+What makes a bike more likely to be targeted?
+And where are the theft hotspots cyclists should avoid?
+Each section of our article addresses a different angle of bike theft in Toronto, from seasonal and weekly theft patterns to variations by bicycle type and value, to pinpointing the city’s most high-risk locations.</p>
+
+  <p>Over the past decade, <strong style="color: #FFC107;">32,489</strong> bike thefts have been reported in Toronto, yet only <strong style="color: #FFC107;">422</strong> of these stolen bikes were successfully recovered.
+With these insights, we aim to empower cyclists with knowledge that can help them safeguard their bikes and inform Cycle Toronto and local authorities about the areas most in need of intervention.
+Read on as we trace theft trends over the years, reveal the high-risk locations, and provide practical advice to help protect your bike.</p>
+</div>
+
+</div>
 
@@
 
-Imagine locking up your bike on a bustling Toronto street, feeling reassured that a strong lock and some common sense will keep it safe.
-But what if certain seasons, specific bike types, or even certain neighborhoods increase your risk of theft far more than you realize?
-For many cyclists, bike theft has moved from a distant possibility to an everyday concern, with data revealing just how pervasive the risk can be in Toronto.
+<div class="section-heading">
+  <span class="section-title-line1">When Are Bikes at the Greatest Risk?</span><br>
+  <span class="section-title-line2">A Look at Seasonal and Weekly Patterns</span>
+</div>
 
-In this analysis, we dig into over a decade’s worth of data from the Toronto Police Service to answer key questions: When are bikes at the greatest risk?
-What makes a bike more likely to be targeted?
-And where are the theft hotspots cyclists should avoid?
-Each section of our article addresses a different angle of bike theft in Toronto, from seasonal and weekly theft patterns to variations by bicycle type and value, to pinpointing the city’s most high-risk locations.
+<center>
+```{r interactive_weekly_plot, echo=FALSE, message=FALSE, warning=FALSE, results='asis', fig.width=9.5, fig.height=4}
 
-With these insights, we aim to empower cyclists with knowledge that can help them safeguard their bikes and inform Cycle Toronto and local authorities about the areas most in need of intervention.
-Read on as we trace theft trends over the years, reveal the high-risk locations, and provide practical advice to help protect your bike.
-
-# When Are Bikes at the Greatest Risk? A Look at Seasonal and weekly Patterns
-
-```{r interactive_weekly_plot, echo=FALSE, message=FALSE, warning=FALSE, results='asis', fig.width=9.5, fig.height=4}
 library(plotly)
@@
 
-# Arrange data by day of the week (Monday to Sunday)
+# Arrange data by day of the week (Monday to Sunday) and convert OCC_DOW to a factor with specified levels
 data <- data %>%
-  arrange(factor(OCC_DOW, levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")))
+  mutate(OCC_DOW = factor(OCC_DOW, levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))) %>%
+  arrange(OCC_DOW)
 
@@
 
-# Add layout with the slider and set background colors
+# Add layout with the slider, title annotation in the top-left, and set background colors
 fig <- fig %>%
@@
     plot_bgcolor = "#faecd5",     # Set background color for the plotting area
-    paper_bgcolor = "#faecd5"     # Set background color for the entire plot
+    paper_bgcolor = "#faecd5",     # Set background color for the entire plot
+    annotations = list(
+      list(
+        x = 0.01, y = 1.05,  # Position in normalized coordinates (0 = left, 1 = top)
+        xref = "paper", yref = "paper",
+        text = "Weekly Bicycle Theft Patterns in Toronto",  # Title text
+        showarrow = FALSE,
+        font = list(size = 12, color = "#603601")  # Set title color to #603601
+      )
+    )
   )
@@
 ``` 
+</center>
 
-```{r mothly_plot, include = TRUE, warning = FALSE, message = FALSE, fig.width=11, fig.height=5}
+<div class="main-body">
+  <p> Weekly bicycle theft patterns in Toronto is illustrated in @interactive_weekly_plot, revealing that thefts are not evenly distributed throughout the week.
+The data shows a peak on Fridays, with over <strong style="color: #FFC107;">4,900</strong> reported thefts, followed by a decline on Saturday and Sunday.
+This trend may reflect how people use their bikes during the week versus the weekend.
+Fridays might represent a combination of commuter bike usage and weekend planning, where people may leave their bikes in high-traffic or less secure areas, making them more vulnerable to theft.</p>
+
+<p>This insight could be valuable for both cyclists and advocacy groups like <a href="https://www.cycleto.ca/" target="_blank" style="color: #FFC107; text-decoration: underline;">Cycle Toronto</a>.
+Understanding that Friday is a peak day for thefts, local authorities could consider increasing surveillance or public awareness efforts on this day, especially in known hotspot areas.
+Additionally, for cyclists, it suggests that extra caution on Fridays could reduce the risk of theft.
+The data here underscores the importance of timing in bike theft prevention, showing how risks fluctuate within the week, which may reflect broader social and behavioral patterns around work and leisure in Toronto.</p>\
+
+<center>
+```{r mothly_plot, include = TRUE, warning = FALSE, message = FALSE, fig.width=9.5, fig.height=5}
 # Load necessary libraries
@@
 ```
+</center>
+\
 
-# What Makes a Bike a Target? Analyzing Theft by Bicycle Type and Value
+<div class="main-body">
+  <p>The visualization of bike theft and recovery patterns in Toronto @monthly_plot ussing data from 2014 to 2024 reveals a distinct seasonality, with thefts peaking during the warmer months from May to August.
+This trend likely correlates with <a href="https://www.toronto.ca/wp-content/uploads/2021/04/8f76-2019-Cycling-Public-Option-Survey-City-of-Toronto-Cycling.pdf" target="_blank" style="color: #FFC107; text-decoration: underline;">increase</a> cycling activity during the summer, when more people choose biking as a primary mode of transportation or recreation.
+Events like <a href="https://www.bikemonth.ca/toronto" target="_blank" style="color: #FFC107; text-decoration: underline;">Bike Month</a> in June, which includes initiatives encouraging cycling, leading to higher exposure of bikes, making them easier targets for theft.</p>
+
+<p>In contrast, the left side of the plot illustrates the number of bikes found each month, which remains consistently low across the years.
+The low recovery rate highlights systemic issues in bike recovery efforts.
+Despite <a href="https://www.tps.ca/services/bicycle-registration/" target="_blank" style="color: #FFC107; text-decoration: underline;">city-wide bike registry programs</a> and <a href="https://www.tps.ca/crime-prevention/bicycle-safety-and-theft-prevention/" target="_blank" style="color: #FFC107; text-decoration: underline;">police campaigns</a> aimed at educating cyclists about secure parking and locking techniques, the ratio of bikes recovered to those stolen has remained low.
+In recent years, Toronto has initiated <a href="https://www.toronto.ca/services-payments/streets-parking-transportation/cycling-in-toronto/bicycle-parking/" style="color: #FFC107; text-decoration: underline;">programs</a> to improve bike parking infrastructure and introduced more secure lock stands in high-theft areas, but these measures appear insufficient given the scale of theft illustrated in this data.</p>
+
+<div class="section-heading">
+  <span class="section-title-line1">What Makes a Bike a Target?</span><br>
+  <span class="section-title-line2">Analyzing Theft by Bicycle Type and Value</span>
+</div>
+
 Discuss any available data on bike types, brands, or values, showing if certain bikes are more vulnerable to theft than others.
 
-# A Decade of Disappearing Bikes: Tracing Theft Trends Over Ten Years
+<div class="section-heading">
+  <span class="section-title-line1">A Decade of Disappearing Bikes:</span><br>
+  <span class="section-title-line2"> Tracing Theft Trends Over Ten Years</span>
+</div>
 
-```{r animated_bar_plot, echo=FALSE, message=FALSE, warning=FALSE, results='asis', fig.width=7, fig.height=4.5}
+<center>
+```{r animated_bar_plot, echo=FALSE, message=FALSE, warning=FALSE, results='asis', fig.width=4.5, fig.height=2.3}
 # Libraries
@@
 
-# Rename "THEFT" to "Stolen" in the Offence_Category column
+# Rename categories for clarity
 data <- data %>%
-  mutate(Offence_Category = ifelse(Offence_Category == "THEFT", "Stolen", Offence_Category))
+  mutate(Offence_Category = case_when(
+    Offence_Category == "THEFT" ~ "Bikes Stolen",
+    Offence_Category == "FOUND" ~ "Bikes Found",
+    TRUE ~ Offence_Category
+  ))
 
@@
 # Ensure Offence_Category is a factor for proper ordering
-animated_data$Offence_Category <- as.factor(animated_data$Offence_Category)
+animated_data$Offence_Category <- factor(animated_data$Offence_Category, levels = c("Bikes Found", "Other", "Bikes Stolen"))
 
 # Define custom colors for each category
-custom_colors <- c("Stolen" = "#603601", "FOUND" = "#4682B4", "Other" = "#eedaaf")
+custom_colors <- c("Bikes Stolen" = "#603601", "Bikes Found" = "#4682B4", "Other" = "#eedaaf")
 
-# Create the animated bar plot
-ggplot(animated_data, aes(x=Offence_Category, y=Number_of_Offences, fill=Offence_Category)) + 
-  geom_bar(stat='identity') +
+# Create the animated bar plot with the x-axis label at the bottom right
+ggplot(animated_data, aes(x = Offence_Category, y = Number_of_Offences, fill = Offence_Category)) + 
+  geom_bar(stat = 'identity') +
   theme_minimal() +
@@
 
-  # Set background colors for panel and plot
+  # Set background colors and adjust text positioning, placing the x-axis label at the bottom right
   theme(
     panel.background = element_rect(fill = "#faecd5", color = NA),
-    plot.background = element_rect(fill = "#faecd5", color = NA)
+    plot.background = element_rect(fill = "#faecd5", color = NA),
+    axis.text.x = element_text(size = 8),
+    axis.text.y = element_text(size = 8),
+    axis.title.x = element_text(size = 8, hjust = 1, vjust = -1),  # Position x-axis label at the bottom right
+    axis.title.y = element_text(size = 8),
+    legend.text = element_text(size = 6)
   ) +
@@
 ```
-<div style="color: grey; font-size: 12 px; margin-top: 3px;"> Displays the count of various bicycle-related offences reported to the Toronto Police Service, highlighting categories such as stolen, found, and other incidents.
-The smooth increase in bar heights emphasizes the scale of each offence type, offering insights into the distribution and relative frequency of these incidents from 2014 to 2024 </div> \
+</center>
 
-```{r animated_line_plot, echo=FALSE, message=FALSE, warning=FALSE, results='asis', fig.width=6, fig.height=3}
+<div style="color: grey; font-size: 12px; margin-top: 3px; max-width: 800px; margin: 0 auto;">
+  Displays the count of various bicycle-related offences reported to the Toronto Police Service, highlighting categories such as stolen, found, and other incidents.
+The smooth increase in bar heights emphasizes the scale of each offence type, offering insights into the distribution and relative frequency of these incidents from 2014 to 2024.
+</div> \
+
+<div class="main-body">
+  <p>The tallest bar, representing "Bikes Stolen," towers above the others with over <strong style="color: #FFC107;">32,000</strong> reported incidents, emphasizing how prevalent bike theft has become across the city of Toronto.
+<a href="https://www.ctvnews.ca/canada/should-toronto-tear-up-its-bike-lanes-to-improve-traffic-flow-critics-say-it-s-not-so-simple-1.7103768" style="color: #FFC107; text-decoration: underline;">CTV news</a> have highlighted hotspots, including downtown Toronto and areas near major transit hubs, where cyclists frequently leave bikes unattended.
+In response, The Toronto Police Service (TPS) has introduced <a href="https://www.tps.ca/media-centre/news-releases/fix-title-project-sentry/" style="color: #FFC107; text-decoration: underline;">Project Sentry</a>, an initiative led by officers in 14 Division aimed at recovering stolen bicycles and reuniting them with their rightful owners across the city.
+This program is part of TPS’s effort to address the high rates of bike theft and improve recovery outcomes for Toronto cyclists.
+</p>
+
+ <p>In contrast, the "Bikes Found" bar, with only <strong style="color: #FFC107;">422</strong> cases, reveals a deep gap in recovery efforts.
+The small size of this bar underscores how difficult it is to retrieve stolen bikes and reunite them with their owners, suggesting a systemic issue in tracking and identifying stolen bicycles.
+Although Toronto has introduced <a href="https://project529.com/garage" style="color: #FFC107; text-decoration: underline;">Project 529</a> to help track ownership, recovery rates remain low, partly due to limited resources and the challenge of identifying recovered bikes that may have been altered or resold.
+</p>
+
+ <p>The "Other" category, with around <strong style="color: #FFC107;">3,200</strong> cases, includes incidents such as attempted thefts, damage to bikes, mischief, and other related offenses.
+This category highlights a broader issue affecting bike security, indicating that many cyclists encounter safety challenges even when their bikes aren’t ultimately stolen.
+</p>
+
+<center>
+```{r animated_line_plot, echo=FALSE, message=FALSE, warning=FALSE, results='asis', fig.width=5, fig.height=3}
 # Load necessary libraries
@@
 
-# Create the animated plot
+# Create the animated plot with smaller text elements
 plot <- data %>%
@@
   theme(
-    axis.text.x = element_text(angle = 45, hjust = 1),
+    axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
+    axis.text.y = element_text(size = 8),
+    axis.title.x = element_text(size = 10),
+    axis.title.y = element_text(size = 10),
+    legend.title = element_text(size = 8),
+    legend.text = element_text(size = 6),
     panel.background = element_rect(fill = "#faecd5", color = NA),
@@
 ```
-<div style="color: grey; font-size: 12 px; margin-top: 3px;"> Visualizes the monthly count of bicycle thefts reported to the Toronto Police Service from 2014 to June 2024.
+</center>
+
+<div style="color: grey; font-size: 12px; margin-top: 3px; max-width: 800px; margin: 0 auto;">
+ Visualizes the monthly count of bicycle thefts reported to the Toronto Police Service from 2014 to June 2024.
 The animation reveals seasonal patterns and variations across different years, providing insights into peak months and potential trends over time.
-</div> \
+</div>
 
-# Mapping the Danger Zones: High-Risk Locations Across Toronto
+@animated_line_plot illustrates the monthly patterns of bicycle thefts in Toronto from 2014 to mid-2024, revealing a clear seasonal trend.
+Each year, bike thefts rise steadily in the spring, peak during the summer months of June and July, and then decline in the fall and winter when cycling activity decreases.
+This predictable pattern aligns with Toronto's warmer months when more residents choose biking as their primary mode of transportation or recreation, leading to increased exposure of bikes in public spaces.
+These high-theft months underline the need for heightened security measures and awareness among cyclists, particularly during summer.
 
-# Mapping the Danger Zones: High-Risk Locations Across Toronto
+The year 2020, however, deviates from this regular trend due to the impact of the COVID-19 pandemic.
+As public transit options were considered risky, many Torontonians turned to bicycles as a safer and more flexible transportation option, resulting in a rise in bike ownership and driving up theft rates (@citeshapiro2021).
+Additionally, the pandemic stretched police resources, potentially limiting routine patrols and recovery efforts.
+The 2020 increase highlights how external factors, such as a public health crisis, can exacerbate bike theft trends and points to the importance of adaptable theft prevention strategies in response to changing urban transportation needs.
 
-Now imagine you’re navigating the streets of Toronto, trying to understand where bicycle thefts are happening.
-The first chart is like an overhead view from a hot air balloon, showing clusters of incidents with bright orange circles scattered across the landscape.
+<div class="section-heading">
+  <span class="section-title-line1">Mapping the Danger Zones:</span><br>
+  <span class="section-title-line2"> High-Risk Locations Across Toronto</span>
+</div>
+
+<div class="main-body">
+  <p>Now imagine you’re navigating the streets of Toronto, trying to understand where bicycle thefts are happening.
+@interactive_map is like an overhead view from a hot air balloon, showing clusters of incidents with bright orange circles scattered across the landscape.
 Each circle represents a collection of theft reports—smaller bubbles indicate fewer incidents, while larger ones stand like towering beacons, signaling areas of greater vulnerability.
-Downtown Toronto, unsurprisingly, is covered by a massive bubble, indicating that this densely populated urban center has been most affected by bike thefts.
+<a href="https://en.wikipedia.org/wiki/Downtown_Toronto" target="_blank" style="color: #FFC107; text-decoration: underline;">Downtown Toronto</a>, unsurprisingly, is covered by a massive bubble, indicating that this densely populated urban center has been most affected by bike thefts.
 As we drift north and away from the downtown core, the bubbles shrink, suggesting fewer incidents—likely due to the suburban nature of these areas, where bikes are stored more securely.
-And here's the interactive part—you can click on these bubbles to zoom in and explore specific areas, uncovering the exact locations and getting a more detailed sense of bike stolen cases.
-It's like having a personal guide leading you through the hot spots and quieter neighborhoods.
+And here's the interactive part—you can <strong style="color: #FFC107;">click</strong> on these bubbles to zoom in and explore specific areas, uncovering the exact locations and getting a more detailed sense of bike stolen cases.
+It's like having a personal guide leading you through the hot spots and quieter neighborhoods.</p>
 
-```{r, echo=FALSE, warning=FALSE, message=FALSE}
+<center>
+```{r interactive_map, echo=FALSE, warning=FALSE, message=FALSE}
 #### Map with Markers ####
@@
 ```
+</center>
 
-In the second chart, we dive deeper into the city with a ground-level view—a sea of red dots each marks an individual theft incident.
+<div style="color: grey; font-size: 12px; margin-top: 3px; max-width: 800px; margin: 0 auto;">
+  [To be updated...]
+</div> \
+
+<div class="main-body">
+  <p>In @map_of_stolen_bike, we dive deeper into the city with a ground-level view—a sea of red dots each marks an individual theft incident.
 The dots are packed tightly in certain neighborhoods, sprawling across downtown Toronto like a dense red blanket.
@@
 There’s a sharp concentration near transit hubs and popular neighborhoods, suggesting a correlation between foot traffic, bike use, and crime opportunity.
-The City has been making efforts to combat this issue; for example, Cycle Toronto launched the #EndBikeTheft campaign, advocating for secure parking and better registration systems, with city discussions exploring collaboration with platforms like 529 Garage to help reduce and recover stolen bikes (@citeEndBikeTheft).
-It’s almost as though you can hear the honks and feel the rush of people in these crowded streets.
+The City has been making efforts to combat this issue; for example, Cycle Toronto launched the <a href="https://www.cycleto.ca/council-talking-about-ending-bike-theft-week" target="_blank" style="color: #FFC107; text-decoration: underline;">#EndBikeTheft campaign</a>, advocating for secure parking and better registration systems, with city discussions exploring collaboration with platforms like <a href="https://project529.com/garage" style="color: #FFC107; text-decoration: underline;">529 Garage</a> to help reduce and recover stolen bikes (@citeEndBikeTheft).
+It’s almost as though you can hear the honks and feel the rush of people in these crowded streets.</p>
 
-```{r, echo=FALSE, warning=FALSE, message=FALSE}
+<center>
+```{r map_of_stolen_bike, echo=FALSE, warning=FALSE, message=FALSE}
 # Load necessary libraries
@@
 ```
+</center>
 
-Finally, the third chart takes a step back to help us understand the data by neighborhood, but this time with broader strokes.
+<div style="color: grey; font-size: 12px; margin-top: 3px; max-width: 800px; margin: 0 auto;">
+  [To be updated...]
+</div> \
+
+<div class="main-body">
+  <p>@map_case_number takes a step back to help us understand the data by neighborhood, but this time with broader strokes.
 It presents different regions in Toronto as bubbles of varying sizes and colors, indicating the number of thefts in each.
@@
 One particular neighborhood stands out—a massive blue circle in the downtown area—it visually reinforces what the other charts have hinted at: that specific neighborhoods, especially those near the core, are the epicenters of bicycle theft.
-Meanwhile, the areas with smaller circles seem almost untouched in comparison, a stark contrast that reveals a city of disparities—some areas buzz with activity and theft risk, while others enjoy relative calm.
+Meanwhile, the areas with smaller circles seem almost untouched in comparison, a stark contrast that reveals a city of disparities—some areas buzz with activity and theft risk, while others enjoy relative calm.</p>
 
-```{r, echo=FALSE, warning=FALSE, message=FALSE}
+<center>
+```{r map_case_number, echo=FALSE, warning=FALSE, message=FALSE}
 #### Map with Areas ####
@@
 ```
+</center>
 
-# Discussion 
-- Consolidation of all the info that we present, we first talk about...this is how all visualizations are connected together, in the future what can be done...
+<div style="color: grey; font-size: 12px; margin-top: 3px; max-width: 800px; margin: 0 auto;">
+  [To be updated...]
+</div> \
 
-# Conclusion
-- short reminder for the audience, tips to protect their bikes
+<div class="section-heading">
+  <span class="section-title-line1">Putting it All Together</span><br>
+</div>
 
-General tips: 
- - This paper wants to tell the story about tips to protect bikes
+<div class="main-body">
+  <p>In this analysis, we began by examining when bikes are at the greatest risk of theft, revealing a strong seasonal trend with thefts peaking in the summer months from May to August and notable decrease on Fridays.
+These insights provided a foundation for understanding the timing of bike thefts.
+Next, we looked into bike recovery rates, which showed a significant gap between the number of bikes stolen and those successfully recovered, highlighting the challenges in returning stolen bikes to their owners.
+This aspect underscored systemic issues in recovery efforts and the need for improved tracking systems.</p>
 
- - after every visualizations talk a bit about the visualization itself, key points, make sure the story that we are talking about is proved by this visualization so each plot make sense (for example in 2016 there is a peak in May illustrated by the visualization, why?
-find relevant news and articels to explain it and cite), 用更descriptive的形式去explain 你的visualization plot with proves.
+<p>The analysis also dove into geographical patterns, identifying hotspots such as downtown Toronto and major transit hubs where bike thefts are most concentrated.
+Through mapping, we provided a visual representation of high-risk areas, guiding cyclists and policymakers on where extra security measures are most needed.</p>
 
-# Citation
+<p>Together, these visualizations connect to form a comprehensive view of Toronto’s bike theft landscape.
+They reveal the when, where, and why of bike theft, offering insights that can inform future actions.
+Moving forward, Toronto can strengthen its approach by expanding secure bike parking options, increasing partnerships with bike registration platforms like Project 529, and deploying targeted initiatives like Project Sentry in high-theft areas.
+Future studies could extend this analysis to examine bike theft patterns across Canada, providing a nationwide perspective on hotspots and seasonal trends.
+By combining these efforts, city authorities, advocacy groups, and cyclists themselves can work together to create a safer environment for biking across Toronto.</p>
+
+<div class="section-heading">
+  <span class="section-title-line1">Conclusion</span><br>
+</div>
+
+<div class="main-body">
+  <p>This article is a reminder: as cycling grows in popularity, so does the risk of theft.
+Whether you’re a daily commuter or a weekend rider, taking extra precautions—like using a sturdy lock, parking in well-lit areas, and registering your bike—can make a big difference.
+Protect your bike, and keep Toronto’s cycling community rolling safely all year round.</p>
+
+# Citations

### 2024-11-12 paper/paper.Rmd
title, subtitle, description formatted

@@
   line-height: 1.1;                  /* Tighter line height */
+  padding: 10px;                     /* Add padding around text */
+  border: 5px solid #FFC107;         /* Border around the title text */
+  border-radius: 8px;                /* Rounded corners for a softer look */
+  display: inline-block;             /* Keeps the border tight around text */
+  text-shadow: 3px 3px 8px rgba(0, 0, 0, 0.7); /* Text shadow for emphasis */
+  box-shadow: 0px 4px 10px rgba(0, 0, 0, 0.5); /* Optional shadow for depth */
 }
@@
   line-height: 1.2;           /* Adjust line height for spacing */
+  text-shadow: 3px 3px 8px rgba(0, 0, 0, 0.7); /* Text shadow for emphasis */
 }
@@
   box-shadow: none !important;
+  text-shadow: 3px 3px 8px rgba(0, 0, 0, 0.7); /* Text shadow for emphasis */
 }
@@
   font-style: italic;
+  text-shadow: 3px 3px 8px rgba(0, 0, 0, 0.7); /* Text shadow for emphasis */
 }

### 2024-11-12 paper/paper.Rmd
paper formmating

@@
 
-required_packages <- c("lubridate", "sf", "tidyverse", "readr", "here", "osmdata", "ggplot2")
+required_packages <- c("sf", "here", "dplyr", "readr", "purrr", "plotly", "ggplot2", "leaflet", "osmdata", 
+                       "ggridges", "cowplot", "lubridate", "tidyverse", "crosstalk", "bookdown", "hrbrthemes", "gganimate")
+
 for (p in required_packages) {
@@
 
+library(sf)
+library(here)
+library(dplyr)
+library(readr)
+library(purrr)
+library(plotly)
+library(ggplot2)
+library(leaflet)
+library(osmdata)
+library(cowplot)
+library(ggridges)
+library(bookdown)
 library(lubridate)
 library(tidyverse)
-library(ggplot2)
-library(osmdata)
-library(readr)
-library(here)
-library(sf)
+library(crosstalk)
+library(gganimate)
+library(hrbrthemes)
 
-# you are welcome to use either the CSV file or the GeoJSON file
-# GeoJSON format maybe useful if you would like to combine
-# an external geospatial dataset
-bike_thefts_csv <- read_csv(here("data/clean_data.csv")) |>
-  mutate(
-    occurence_date = as_date(
-      OCC_DATE, format = "%a, %d %b %Y %H:%M:%S GMT"
-    ),
-    report_date = as_date(
-      REPORT_DATE, format = "%a, %d %b %Y %H:%M:%S GMT"
-    )
-  )
-bike_thefts_sf <- read_sf(here("data/Bicycle_Thefts_Open_Data.geojson")) |>
-  mutate(
-    occurence_date = as_date(
-      OCC_DATE, format = "%a, %d %b %Y %H:%M:%S GMT"
-    ),
-    report_date = as_date(
-      REPORT_DATE, format = "%a, %d %b %Y %H:%M:%S GMT"
-    )
-  )
 ```
@@
 ```{r interactive_weekly_plot, echo=FALSE, message=FALSE, warning=FALSE, results='asis', fig.width=9.5, fig.height=4}
-
-library(plotly)
-library(readr)
-library(dplyr)
-library(here)
 
@@
 fig <- plot_ly(data, x = ~OCC_DOW, y = ~Number_of_Thefts, type = 'scatter', mode = 'lines+markers',
-               line = list(color = 'brown'), marker = list(color = 'blue', size = 8))
+               line = list(color = '#05595B'), marker = list(color = '#603601', size = 10))
 
@@
       textposition = "top center",
-      marker = list(color = "yellow", size = 10),
+      marker = list(color = "#FFC107", size = 15),
       showlegend = FALSE,
@@
 <div class="main-body">
-  <p> Weekly bicycle theft patterns in Toronto is illustrated in @interactive_weekly_plot, revealing that thefts are not evenly distributed throughout the week.
+  <p> Weekly bicycle theft patterns in Toronto is illustrated in \@ref(fig:interactive_weekly_plot), revealing that thefts are not evenly distributed throughout the week.
 The data shows a peak on Fridays, with over <strong style="color: #FFC107;">4,900</strong> reported thefts, followed by a decline on Saturday and Sunday.
@@
 ```{r mothly_plot, include = TRUE, warning = FALSE, message = FALSE, fig.width=9.5, fig.height=5}
-# Load necessary libraries
-library(tidyverse)
-library(ggridges)
-library(cowplot)
-library(here)
 
@@
 
+```{r}
+
+```
+
 Discuss any available data on bike types, brands, or values, showing if certain bikes are more vulnerable to theft than others.
@@
 ```{r animated_bar_plot, echo=FALSE, message=FALSE, warning=FALSE, results='asis', fig.width=4.5, fig.height=2.3}
-# Libraries
-library(ggplot2)
-library(gganimate)
-library(readr)
-library(here)
-library(dplyr)
 
@@
 ```{r animated_line_plot, echo=FALSE, message=FALSE, warning=FALSE, results='asis', fig.width=5, fig.height=3}
-# Load necessary libraries
-library(ggplot2)
-library(gganimate)
-library(dplyr)
-library(hrbrthemes)
-library(readr)
-library(here)
 
@@
 The year 2020, however, deviates from this regular trend due to the impact of the COVID-19 pandemic.
-As public transit options were considered risky, many Torontonians turned to bicycles as a safer and more flexible transportation option, resulting in a rise in bike ownership and driving up theft rates (@citeshapiro2021).
+As public transit options were considered risky, many Torontonians turned to bicycles as a safer and more flexible transportation option, resulting in a rise in bike ownership and driving up theft rates (@citeShapiro2021).
 Additionally, the pandemic stretched police resources, potentially limiting routine patrols and recovery efforts.
@@
 
-# Load necessary libraries
-library(dplyr)         # Provides functions for data manipulation.
-library(leaflet)       # Enables interactive maps.
-library(purrr)         # Contains functional programming tools, used here to walk through data.
-library(readr)         # Provides functions to read rectangular data like CSV files.
-library(here)          # Helps manage file paths in a more robust way.
-
-# Load your dataset (adjust the file path accordingly)
+# Load your dataset
 map_data <- read_csv(here("data", "map_by_neighbourhoods_data.csv"), show_col_types = FALSE)
-# Loads the CSV file from the specified path using the 'here()' function for consistent path management.
-# 'show_col_types = FALSE' suppresses messages about the data types of each column.
 
@@
                     labels = c('> 100 & <=500', '>500 & <=1000', '>1000 & <=1500'))
-    # Creates a 'mag.level' column that categorizes 'case_num' into three levels based on specified ranges.
   ) %>%
-  split(.$mag.level)  # Splits the dataset into a list of data frames by 'mag.level'.
+  split(.$mag.level)
 
@@
   addProviderTiles(providers$Esri.OceanBasemap)
-# Initializes a Leaflet map object and adds a base tile layer from the Esri Ocean Basemap provider.
 
@@
   })
-# Iterates over the names of the 'map_data' list (which are the different 'mag.level' categories).
-# For each category, it adds markers to the map:
-# - `data = map_data[[df]]`: Uses the split data for the current case_num level.
-# - `lng = ~longitude, lat = ~latitude`: Sets longitude and latitude for marker placement.
-# - `label`: Displays the 'case_num' value when markers are hovered over.
-# - `popup`: Displays additional information (hood_num, stolen_place, cost, status, and case_num) when a marker is clicked.
-# - `group = df`: Groups the markers by 'mag.level'.
-# - `clusterOptions = markerClusterOptions()`: Enables clustering of markers for better visualization.
 
@@
   addMiniMap(tiles = providers$Esri.OceanBasemap, width = 120, height = 80)
-# Adds layer controls to allow switching between different 'mag.level' categories on the map.
-# Adds a minimap showing a small overview of the area using the Esri Ocean Basemap.
 
@@
 l
+
 ```
@@
 ```{r map_of_stolen_bike, echo=FALSE, warning=FALSE, message=FALSE}
-# Load necessary libraries
-library(ggplot2)
-library(sf)
-library(osmdata)
-library(here)
 
@@
     data = coordinates_data, aes(x = longitude, y = latitude),
-    size = 0.5, color = "red"
+    size = 0.5, color = "#FFC107"
   ) + # Bike theft points
@@
 bike_theft_plot
+
 ```
@@
 
-# Load necessary libraries
-library(dplyr)
-library(readr)
-library(ggplot2)
-library(plotly)
-library(sf)
-library(crosstalk)
-library(here)
-library(osmdata)
-
 # Load your dataset (adjust the file path accordingly)
@@
 shared_data <- crosstalk::SharedData$new(map_data)
+
+# Define more detailed breaks for color scale based on `case_num`
+max_case_num <- max(map_data$case_num, na.rm = TRUE)
+color_breaks <- seq(0, max_case_num, by = max_case_num / 4)
+
+# Create a rounding function to simplify the labels
+rounded_labels <- function(x) scales::comma(round(x, -6))
 
@@
   ) +
-  scale_color_continuous(labels = scales::comma) +
-  scale_size_continuous(range = c(3, 12)) # Adjust range values to control the size of points
+  scale_color_gradientn(colors = c("#603601", "#FFC107"), breaks = color_breaks, labels = rounded_labels) +
+  scale_size_continuous(range = c(3, 12))
 

### 2024-11-13 scripts/data_clean.R
bike type and value data added

@@ -1,35 +1,30 @@
-
-# Purpose: This code sequence cleans and processes bicycle theft data by renaming columns, converting data types, handling missing values, and adding calculated fields. The cleaned dataset is then saved for further analysis, enabling insights into theft patterns, risk factors, and reporting delays to better inform the cyclist community and relevant stakeholders.
-# Author: Yingke He, Ziheng Zhong
-# Date: Nov 11 2024
-# Contact: ziheng.zhong@mail.utoronto.ca
-# License: MIT
-
 #### Load necessary libraries ####
 library(dplyr)
 library(lubridate)
 library(readr)
-library(here)  # Added this to ensure 'here' is loaded
+library(here)
 
-#### Load data ####
+
+
+#### Clean Data ####
+# Load Data
 bicycle_thefts <- read_csv(here("data", "Bicycle_Thefts_Open_Data.csv"))
 
-# Clean data
-
-#### Handle missing values ####
+# Handle missing values
 # Example: Remove rows with missing dates
 bicycle_thefts <- bicycle_thefts %>%
   filter(!is.na(Occurrence_Date) & !is.na(Reported_Date))
 
-#### Remove columns with any missing values ####
+# Remove columns with any missing values
 bicycle_thefts <- bicycle_thefts %>%
   select(where(~ !any(is.na(.))))
 
-#### Save cleaned data ####
+# Save Data
 write_csv(bicycle_thefts, here("data", "clean_data.csv"))
 
-# Bicycle theft yearly count
 
+
+#### Bicycle theft yearly count ####
 # Load the dataset
 bicycle_thefts <- read_csv(here("data", "Bicycle_Thefts_Open_Data.csv"))
 
@@ -42,8 +37,9 @@ yearly_counts <- bicycle_thefts %>%
 # Save the results to a new CSV file
 write_csv(yearly_counts, here("data", "Bicycle_Theft_Yearly_Counts_2014_2024.csv"))
 
-### Bicycle theft monthly count
 
+
+#### Bicycle theft monthly count ####
 # Load the dataset
 bicycle_thefts <- read_csv(here("data", "Bicycle_Thefts_Open_Data.csv"))
 
@@ -65,13 +61,9 @@ monthly_counts <- monthly_counts %>%
 # Save the results to a new CSV file
[…]

### 2024-11-13 paper/paper.Rmd
citations formatted, bike type and value charts added

@@
 
-  <p>In this analysis, we dig into over a decade’s worth of data from the <a href="https://data.torontopolice.on.ca/datasets/TorontoPS::bicycle-thefts-open-data/about" target="_blank" style="color: #FFC107; text-decoration: underline;">Toronto Police Service</a> to answer key questions: When are bikes at the greatest risk?
+  <p>In this analysis, we dig into over a decade’s worth of data from the <a href="https://data.torontopolice.on.ca/datasets/TorontoPS::bicycle-thefts-open-data/about" target="_blank" style="color: #FFC107; text-decoration: underline;">Toronto Police Service</a> (@citePolice) to answer key questions: When are bikes at the greatest risk?
 What makes a bike more likely to be targeted?
@@
 
-required_packages <- c("sf", "here", "dplyr", "readr", "purrr", "plotly", "ggplot2", "leaflet", "osmdata", 
+required_packages <- c("sf", "here", "dplyr", "readr", "purrr", "scales", "plotly", "ggplot2", "leaflet", "osmdata", 
                        "ggridges", "cowplot", "lubridate", "tidyverse", "crosstalk", "bookdown", "hrbrthemes", "gganimate")
@@
 library(purrr)
+library(scales)
 library(plotly)
@@
 
-<p>This insight could be valuable for both cyclists and advocacy groups like <a href="https://www.cycleto.ca/" target="_blank" style="color: #FFC107; text-decoration: underline;">Cycle Toronto</a>.
+<p>This insight could be valuable for both cyclists and advocacy groups like <a href="https://www.cycleto.ca/" target="_blank" style="color: #FFC107; text-decoration: underline;">Cycle Toronto</a> (@citeEndBikeTheft).
 Understanding that Friday is a peak day for thefts, local authorities could consider increasing surveillance or public awareness efforts on this day, especially in known hotspot areas.
@@
   <p>The visualization of bike theft and recovery patterns in Toronto @monthly_plot ussing data from 2014 to 2024 reveals a distinct seasonality, with thefts peaking during the warmer months from May to August.
-This trend likely correlates with <a href="https://www.toronto.ca/wp-content/uploads/2021/04/8f76-2019-Cycling-Public-Option-Survey-City-of-Toronto-Cycling.pdf" target="_blank" style="color: #FFC107; text-decoration: underline;">increase</a> cycling activity during the summer, when more people choose biking as a primary mode of transportation or recreation.
-Events like <a href="https://www.bikemonth.ca/toronto" target="_blank" style="color: #FFC107; text-decoration: underline;">Bike Month</a> in June, which includes initiatives encouraging cycling, leading to higher exposure of bikes, making them easier targets for theft.</p>
+This trend likely correlates with <a href="https://www.toronto.ca/wp-content/uploads/2021/04/8f76-2019-Cycling-Public-Option-Survey-City-of-Toronto-Cycling.pdf" target="_blank" style="color: #FFC107; text-decoration: underline;">increase</a> (@citeSurvey) cycling activity during the summer, when more people choose biking as a primary mode of transportation or recreation.
+Events like <a href="https://www.bikemonth.ca/toronto" target="_blank" style="color: #FFC107; text-decoration: underline;">Bike Month</a> (@citeBikeMonth) in June, which includes initiatives encouraging cycling, leading to higher exposure of bikes, making them easier targets for theft.</p>
 
@@
 The low recovery rate highlights systemic issues in bike recovery efforts.
-Despite <a href="https://www.tps.ca/services/bicycle-registration/" target="_blank" style="color: #FFC107; text-decoration: underline;">city-wide bike registry programs</a> and <a href="https://www.tps.ca/crime-prevention/bicycle-safety-and-theft-prevention/" target="_blank" style="color: #FFC107; text-decoration: underline;">police campaigns</a> aimed at educating cyclists about secure parking and locking techniques, the ratio of bikes recovered to those stolen has remained low.
-In recent years, Toronto has initiated <a href="https://www.toronto.ca/services-payments/streets-parking-transportation/cycling-in-toronto/bicycle-parking/" style="color: #FFC107; text-decoration: underline;">programs</a> to improve bike parking infrastructure and introduced more secure lock stands in high-theft areas, but these measures appear insufficient given the scale of theft illustrated in this data.</p>
+Despite <a href="https://www.tps.ca/services/bicycle-registration/" target="_blank" style="color: #FFC107; text-decoration: underline;">city-wide bike registry programs</a> (@citeTPSRegistration) and <a href="https://www.tps.ca/crime-prevention/bicycle-safety-and-theft-prevention/" target="_blank" style="color: #FFC107; text-decoration: underline;">police campaigns</a> (@citeTPSBicycleSafety) aimed at educating cyclists about secure parking and locking techniques, the ratio of bikes recovered to those stolen has remained low.
+In recent years, Toronto has initiated <a href="https://www.toronto.ca/services-payments/streets-parking-transportation/cycling-in-toronto/bicycle-parking/" style="color: #FFC107; text-decoration: underline;">programs</a> (@citeBicycleParking) to improve bike parking infrastructure and introduced more secure lock stands in high-theft areas, but these measures appear insufficient given the scale of theft illustrated in this data.</p>
 
@@
 
-```{r}
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+
+# Load the cleaned dataset
+bike_type_counts <- read_csv(here("data", "bike_type_counts.csv"))
+
+# Mapping bike type codes to descriptive names
+bike_type_names <- c(
+  "Others" = "Other Types",
+  "MT" = "Mountain",
+  "RG" = "Gravel",
+  "OT" = "Other",
+  "RC" = "Recreational & Commuting",
+  "EL" = "Electric"
+)
+
+# Calculate percentages for each bike type
+bike_type_counts <- bike_type_counts %>%
+  mutate(total = sum(bike_num)) %>%
+  group_by(bike_type) %>%
+  mutate(percentage = (bike_num / total) * 100)
+
+# Summarize types with less than 5% as "Others"
+bike_type_counts <- bike_type_counts %>%
+  mutate(bike_type = ifelse(percentage < 5, "Others", bike_type)) %>%
+  group_by(bike_type) %>%
+  summarise(bike_num = sum(bike_num), percentage = sum(percentage)) %>%
+  ungroup()
+
+# Reorder bike types by percentage in descending order
+bike_type_counts <- bike_type_counts %>%
+  mutate(bike_type = fct_reorder(bike_type, -percentage))
+
+# Create a horizontal stacked bar chart
+ggplot(bike_type_counts, aes(x = factor(1), y = percentage, fill = bike_type)) +
+  geom_bar(stat = "identity", position = "fill") +
+  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
+            position = position_fill(vjust = 0.5), size = 3) +
+  scale_y_continuous(labels = percent_format()) +
+  labs(
+    title = "Distribution of Bike Types",
+    x = "Bike Types",
+    y = "Percentage",
+    fill = "Bike Types"
+  ) +
+scale_fill_manual(labels = bike_type_names, values = c("#FF7043", "#FF8F00", "#FFA726", "#FFB300", "#FFC107", "#FFCA28")) +  coord_flip() +
+  theme_minimal() +
+  theme(axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        legend.position = "right")
+
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+
+# Load data
+bike_cost_counts <- read_csv(here("data", "bike_cost_counts.csv"))
+
+# Create a pie chart of bike cost tiers
+ggplot(bike_cost_counts, aes(x = "", y = bike_num, fill = cost_tier)) +
+  geom_bar(width = 1, stat = "identity") +
+  coord_polar("y") +
+  labs(
+    title = "Proportion of Bike Cost Tiers",
+    fill = "Cost Tier"
+  ) +
+  scale_fill_manual(values = c("#FFCA28", "#FFC107", "#FFB300", "#FF8F00")) +  # Customize colors
+  theme_minimal() +
+  theme(
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank(),
+    axis.text = element_blank(),
+    panel.grid = element_blank(),
+    plot.title = element_text(hjust = 0.5)
+  ) +
+  geom_text(aes(label = paste0(round(bike_num / sum(bike_num) * 100, 1), "%")),
+            position = position_stack(vjust = 0.5))
 
@@
   <p>The tallest bar, representing "Bikes Stolen," towers above the others with over <strong style="color: #FFC107;">32,000</strong> reported incidents, emphasizing how prevalent bike theft has become across the city of Toronto.
-<a href="https://www.ctvnews.ca/canada/should-toronto-tear-up-its-bike-lanes-to-improve-traffic-flow-critics-say-it-s-not-so-simple-1.7103768" style="color: #FFC107; text-decoration: underline;">CTV news</a> have highlighted hotspots, including downtown Toronto and areas near major transit hubs, where cyclists frequently leave bikes unattended.
-In response, The Toronto Police Service (TPS) has introduced <a href="https://www.tps.ca/media-centre/news-releases/fix-title-project-sentry/" style="color: #FFC107; text-decoration: underline;">Project Sentry</a>, an initiative led by officers in 14 Division aimed at recovering stolen bicycles and reuniting them with their rightful owners across the city.
+<a href="https://www.ctvnews.ca/canada/should-toronto-tear-up-its-bike-lanes-to-improve-traffic-flow-critics-say-it-s-not-so-simple-1.7103768" style="color: #FFC107; text-decoration: underline;">CTV news</a> (@citeCTV) have highlighted hotspots, including downtown Toronto and areas near major transit hubs, where cyclists frequently leave bikes unattended.
+In response, The Toronto Police Service (TPS) has introduced <a href="https://www.tps.ca/media-centre/news-releases/fix-title-project-sentry/" style="color: #FFC107; text-decoration: underline;">Project Sentry</a> (@citeTPSProjectSentry), an initiative led by officers in 14 Division aimed at recovering stolen bicycles and reuniting them with their rightful owners across the city.
 This program is part of TPS’s effort to address the high rates of bike theft and improve recovery outcomes for Toronto cyclists.
@@
 The small size of this bar underscores how difficult it is to retrieve stolen bikes and reunite them with their owners, suggesting a systemic issue in tracking and identifying stolen bicycles.
-Although Toronto has introduced <a href="https://project529.com/garage" style="color: #FFC107; text-decoration: underline;">Project 529</a> to help track ownership, recovery rates remain low, partly due to limited resources and the challenge of identifying recovered bikes that may have been altered or resold.
+Although Toronto has introduced <a href="https://project529.com/garage" style="color: #FFC107; text-decoration: underline;">Project 529</a> (@cite529) to help track ownership, recovery rates remain low, partly due to limited resources and the challenge of identifying recovered bikes that may have been altered or resold.
 </p>
@@
 There’s a sharp concentration near transit hubs and popular neighborhoods, suggesting a correlation between foot traffic, bike use, and crime opportunity.
-The City has been making efforts to combat this issue; for example, Cycle Toronto launched the <a href="https://www.cycleto.ca/council-talking-about-ending-bike-theft-week" target="_blank" style="color: #FFC107; text-decoration: underline;">#EndBikeTheft campaign</a>, advocating for secure parking and better registration systems, with city discussions exploring collaboration with platforms like <a href="https://project529.com/garage" style="color: #FFC107; text-decoration: underline;">529 Garage</a> to help reduce and recover stolen bikes (@citeEndBikeTheft).
+The City has been making efforts to combat this issue; for example, Cycle Toronto launched the <a href="https://www.cycleto.ca/council-talking-about-ending-bike-theft-week" target="_blank" style="color: #FFC107; text-decoration: underline;">#EndBikeTheft campaign</a> (@citeEndBikeTheft), advocating for secure parking and better registration systems, with city discussions exploring collaboration with platforms like <a href="https://project529.com/garage" style="color: #FFC107; text-decoration: underline;">529 Garage</a> (@cite529) to help reduce and recover stolen bikes.
 It’s almost as though you can hear the honks and feel the rush of people in these crowded streets.</p>
@@
 
-# Citations
+<div class="section-heading">
+  <span class="section-title-line1">Citations</span><br>
+</div>

### 2024-11-13 paper/paper.Rmd
Auto stash before merge of "kiki" and "origin/kiki"

@@
 <div class="main-body">
-  <p>In this analysis, we began by examining when bikes are at the greatest risk of theft, revealing a strong seasonal trend with thefts peaking in the summer months from May to August and notable decrease on Fridays.
+  <p>In this analysis, we began by examining when bikes are at the greatest risk of theft, revealing a strong seasonal trend with thefts peaking in the summer months from May to August and notable increase on Fridays.
 These insights provided a foundation for understanding the timing of bike thefts.

### 2024-11-13 paper/paper.Rmd

@@
 output: html_document
-bibliography: references.bib
 thanks: "Code and data are available at: [https://github.com/iJustinn/Toronto_Bicycle_Thefts/tree/main](https://github.com/iJustinn/Toronto_Bicycle_Thefts/tree/main)."
@@
 .title {
-  font-size: 70px;                   /* Larger font size for the main title */
+  font-size: 40px;                   /* Larger font size for the main title */
   font-weight: bold;                 /* Bold font weight for emphasis */
@@
 .subtitle {
-  font-size: 40px;            /* Slightly larger font size for the subtitle */
+  font-size: 28px;            /* Slightly larger font size for the subtitle */
   font-weight: normal;        /* Normal font weight */
@@
   display: block; /* Makes span act like a block element */
-  font-size: 20px;
+  font-size: 18px;
   font-weight: normal;
@@
 .author-date {
-  font-size: 18px;
+  font-size: 16px;
   font-weight: normal;
@@
 .main-body {
-  font-size: 18px;            /* Slightly larger font for readability */
-  font-weight: 300;           /* Light font weight for a softer tone */
+  max-width: 800px;              /* Set max width for main body */
+  width: 100%;                    /* Ensures full width within max-width */
+  font-size: 12px;                /* Font size for readability */
+  font-weight: 300;               /* Lighter font weight for softer tone */
   color: black;             
-  line-height: 1.8;           /* Increased line height for readability */
+  line-height: 1.5;               /* Increase line height for readability */
   text-align: justify;            /* Justified alignment for a clean look */
-  max-width: 800px;           /* Limit width to keep text contained */
-  margin: 0 auto;             /* Center the introduction on the page */
+  margin: 0 auto;                 /* Center content on the page */
   padding: 20px;                  /* Add padding around the text */
@@
 
+.main-body p {
+  width: 100%;                    /* Full width within .main-body */
+  max-width: none;                /* Remove max-width constraint */
+  margin: 0 0 1em 0;              /* Consistent margin below each paragraph */
+  padding: 0;                     /* Remove padding */
+}
+
 .section-heading {
   max-width: 800px;              /* Limit the width */
-  margin: 30px auto 20px auto;   /* Center the heading on the page */
+  margin: 20px auto 20px auto;   /* Center the heading on the page */
   padding-bottom: 5px;           /* Space below for the underline */
@@
 .section-title-line1 {
-  font-size: 35px;               /* Larger font size for the first line */
+  font-size: 25px;               /* Larger font size for the first line */
   font-weight: bold;             /* Bold weight for emphasis */
@@
 .section-title-line2 {
-  font-size: 25px;               /* Slightly smaller font for the second line */
+  font-size: 20px;               /* Slightly smaller font for the second line */
   font-weight: normal;           /* Regular weight */
@@
   margin-top: -5px;               /* Adds some spacing between lines */
+}
+
+/* Citation section styling */
+.citation-section {
+  max-width: 800px;
+  margin: 30px auto;              /* Center the section */
+  padding: 20px;                  /* Add padding around citations */
+  background-color: #f9f9f9;      /* Light background for contrast */
+  border-left: 5px solid #FFC107; /* Yellow border to match title color */
+  box-shadow: 0px 4px 10px rgba(0, 0, 0, 0.1); /* Subtle shadow for depth */
+  font-family: 'Georgia', serif;  /* Match main font */
+  color: #333;                    /* Dark text color */
+}
+
+.citation-section h3 {
+  font-size: 20px;                /* Set citation title font size to 20px */
+  line-height: 1.5;
+  color: #603601;                 /* Darker color for contrast */
+  font-weight: bold;
+  margin-bottom: 10px;
+}
+
+.citation-section ul {
+  list-style-type: none;          /* Remove default bullets */
+  padding: 0;                     /* Remove default padding */
+}
+
+.citation-section li {
+  font-size: 12px;                /* Set individual citations to 12px */
+  margin-bottom: 10px;            /* Space between each citation */
+  line-height: 1.5;               /* Increase line height for readability */
+}
+
+.citation-section li a {
+  color: #1a73e8;                 /* Link color for readability */
+  text-decoration: none;
+}
+
+.citation-section li a:hover {
+  text-decoration: underline;      /* Underline on hover */
 }
@@
 
-</div>
-
 ```{r, include = FALSE, warning = FALSE, message = FALSE}
@@
 library(hrbrthemes)
-
+library(htmltools)
 ```
@@
 <center>
-```{r interactive_weekly_plot, echo=FALSE, message=FALSE, warning=FALSE, results='asis', fig.width=9.5, fig.height=4}
+```{r interactive_weekly_plot, echo=FALSE, message=FALSE, warning=FALSE, results='asis', fig.width=8, fig.height=3.5}
 
@@
         showarrow = FALSE,
-        font = list(size = 12, color = "#603601")  # Set title color to #603601
+        font = list(size = 11, color = "#603601")  # Set title color to #603601
       )
@@
 </center>
+<div style="color: grey; font-size: 12px; margin-top: 3px; max-width: 800px; margin: 0 auto;">
+  Note: Dragging the slider reveals daily bike theft patterns in Toronto, highlighting higher-risk days, with data covering 2014 to mid-2024.
+</div> \
 
 <div class="main-body">
-  <p> Weekly bicycle theft patterns in Toronto is illustrated in \@ref(fig:interactive_weekly_plot), revealing that thefts are not evenly distributed throughout the week.
+  <p> The Weekly Bicycle Theft Patterns in Toronto plot revealed that thefts are not evenly distributed throughout the week.
 The data shows a peak on Fridays, with over <strong style="color: #FFC107;">4,900</strong> reported thefts, followed by a decline on Saturday and Sunday.
@@
 The data here underscores the importance of timing in bike theft prevention, showing how risks fluctuate within the week, which may reflect broader social and behavioral patterns around work and leisure in Toronto.</p>\
+</div>
 
 <center>
-```{r mothly_plot, include = TRUE, warning = FALSE, message = FALSE, fig.width=9.5, fig.height=5}
+```{r mothly_plot, include = TRUE,fig.cap = "Bike theft and recovery patterns in Toronto from 2014 to 2024", warning = FALSE, message = FALSE, fig.width=8, fig.height=4.3}
 
@@
     panel.border = element_blank(),
-    plot.title = element_text(size = 14, color = "#05595B", hjust = -0.1, vjust = 1.5),  # Smaller title
+    plot.title = element_text(size = 13, color = "#05595B", hjust = -0.1, vjust = 1.5),  # Smaller title
     panel.background = element_rect(fill = "#faecd5", color = NA),  # Light blue background for plot area
@@
   ggtitle("Bikes Found") +  # Add title for Bikes Found
-  geom_text(data = yearly_totals, aes(x = 12.5, y = OCC_YEAR, label = Found_Total), 
+  geom_text(data = yearly_totals, aes(x = 12, y = OCC_YEAR, label = Found_Total), 
             color = "#05595B", hjust = 1, size = 3, inherit.aes = FALSE)
@@
     plot.background = element_rect(fill = "#faecd5", color = NA),   # Light blue background for overall plot
-    plot.title = element_text(size = 14, color = "#603601", hjust = -0.1, vjust = 1.5)  # Smaller title
+    plot.title = element_text(size = 13, color = "#603601", hjust = -0.1, vjust = 1.5)  # Smaller title
   ) +
@@
   ggtitle("Bikes Stolen") +  # Add title for Bikes Stolen
-  geom_text(data = yearly_totals, aes(x = 12.5, y = OCC_YEAR, label = Stolen_Total), 
+  geom_text(data = yearly_totals, aes(x = 12, y = OCC_YEAR, label = Stolen_Total), 
             color = "#603601", hjust = 1, size = 3, inherit.aes = FALSE)
@@
 <div class="main-body">
-  <p>The visualization of bike theft and recovery patterns in Toronto @monthly_plot ussing data from 2014 to 2024 reveals a distinct seasonality, with thefts peaking during the warmer months from May to August.
+  <p>The visualization of bike theft and recovery patterns in Toronto using data from 2014 to mid 2024 above reveals a distinct seasonality, with thefts peaking during the warmer months from May to August.
 This trend likely correlates with <a href="https://www.toronto.ca/wp-content/uploads/2021/04/8f76-2019-Cycling-Public-Option-Survey-City-of-Toronto-Cycling.pdf" target="_blank" style="color: #FFC107; text-decoration: underline;">increase</a> (@citeSurvey) cycling activity during the summer, when more people choose biking as a primary mode of transportation or recreation.
@@
 In recent years, Toronto has initiated <a href="https://www.toronto.ca/services-payments/streets-parking-transportation/cycling-in-toronto/bicycle-parking/" style="color: #FFC107; text-decoration: underline;">programs</a> (@citeBicycleParking) to improve bike parking infrastructure and introduced more secure lock stands in high-theft areas, but these measures appear insufficient given the scale of theft illustrated in this data.</p>
+</div>
 
@@
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
+<center>
+```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis', fig.width=7, fig.height=4}
 
@@
   ) +
-scale_fill_manual(labels = bike_type_names, values = c("#FF7043", "#FF8F00", "#FFA726", "#FFB300", "#FFC107", "#FFCA28")) +  coord_flip() +
+  scale_fill_manual(labels = bike_type_names, values = c("#FF7043", "#FF8F00", "#FFA726", "#FFB300", "#FFC107", "#FFCA28")) +
+  coord_flip() +
   theme_minimal() +
@@
 ```
+</center>
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
+<div class="main-body">
+  <p>The first plot illustrates the distribution of stolen bike types in Toronto, highlighting which kinds are more frequently targeted.
+Mountain bikes and recreational & commuting bikes make up the largest portions, at <strong style="color: #FFC107;">31%</strong> and <strong style="color: #FFC107;">27.4%</strong> respectively, reflecting their popularity among Toronto cyclists for both daily commuting and recreational use.
+Their common use likely makes them more visible and accessible, increasing the risk of theft.
+Electric bikes, by contrast, are less frequently stolen, accounting for only <strong style="color: #FFC107;">7.8%</strong>, which may reflect the added security measures often used by owners of higher-value bikes.</p>
+
+<center>
+```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis', fig.width=7, fig.height=4}
 
@@
 ```
+</center>
 
-Discuss any available data on bike types, brands, or values, showing if certain bikes are more vulnerable to theft than others.
+<p>The second plot examines bike theft by cost tier, showing that bikes in the lower price ranges (under \$500 and \$500-\$999) are the most commonly stolen, at <strong style="color: #FFC107;">34.9%</strong> and <strong style="color: #FFC107;">31.7%</strong> respectively.
+These lower-cost bikes are often used for daily commuting in Toronto, left in public spaces where they are more vulnerable.
+Interestingly, higher-value bikes (\$1000-\$1999 and above \$2000) also face theft risk, comprising <strong style="color: #FFC107;">20.9%</strong> and <strong style="color: #FFC107;">12.4%</strong> of thefts.
+This suggests that while thieves frequently target accessible, lower-value bikes, higher-cost bikes are still vulnerable, especially in busy urban areas where security can vary.</p>
+
+<p>These data highlight that all Toronto cyclists, regardless of their bike's value, should implement strong security measures.
+For lower-cost bikes commonly used for commuting, investing in a high-quality U-lock or chain lock is essential, as these bikes are frequently targeted due to their accessibility.
+Parking in high-traffic areas with security cameras, like those near busy shops or designated bike racks, can help prevent opportunistic theft.
+Even for a lower-value bike, taking these extra precautions can make a significant difference in reducing theft risk.</p>
+
+<p>Higher-value bikes, while less commonly stolen, still attract attention and may require even more advanced protection.
+Cyclists with more expensive bikes should consider using two different types of locks, such as a U-lock paired with a cable lock, and avoid leaving their bikes outside overnight.
+Indoor storage options, when available, provide the highest level of security (@citeTPSBicycleSafety).
+Additionally, registering bikes with Toronto’s bike registry or Project 529 can improve the chances of recovery if theft occurs (@citeTPSRegistration; @cite529).
+By marking bikes with unique identifiers and varying parking locations regularly, cyclists can make their bikes less predictable targets and better protect them from theft in Toronto.</p>
+</div>
 
@@
 <center>
-```{r animated_bar_plot, echo=FALSE, message=FALSE, warning=FALSE, results='asis', fig.width=4.5, fig.height=2.3}
+```{r animated_bar_plot, echo=FALSE, message=FALSE, warning=FALSE, results='asis', fig.width=4, fig.height=2}
 
@@
     plot.background = element_rect(fill = "#faecd5", color = NA),
-    axis.text.x = element_text(size = 8),
-    axis.text.y = element_text(size = 8),
-    axis.title.x = element_text(size = 8, hjust = 1, vjust = -1),  # Position x-axis label at the bottom right
-    axis.title.y = element_text(size = 8),
-    legend.text = element_text(size = 6)
+    axis.text.x = element_text(size = 6),
+    axis.text.y = element_text(size = 6),
+    axis.title.x = element_text(size = 6, hjust = 1, vjust = -1),  # Position x-axis label at the bottom right
+    axis.title.y = element_text(size = 6),
+    legend.text = element_text(size = 4)
   ) +
@@
 </p>
+</div>
 
 <center>
-```{r animated_line_plot, echo=FALSE, message=FALSE, warning=FALSE, results='asis', fig.width=5, fig.height=3}
+```{r animated_line_plot, echo=FALSE, message=FALSE, warning=FALSE, results='asis', fig.width=4.2, fig.height=2.6}
 
@@
   theme(
-    axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
+    axis.text.x = element_text(angle = 45, hjust = 1, size = 7),
     axis.text.y = element_text(size = 8),
@@
 
-@animated_line_plot illustrates the monthly patterns of bicycle thefts in Toronto from 2014 to mid-2024, revealing a clear seasonal trend.
+<div class="main-body">
+  <p>The animated line plot illustrates the monthly patterns of bicycle thefts in Toronto from 2014 to mid-2024, revealing a clear seasonal trend.
 Each year, bike thefts rise steadily in the spring, peak during the summer months of June and July, and then decline in the fall and winter when cycling activity decreases.
 This predictable pattern aligns with Toronto's warmer months when more residents choose biking as their primary mode of transportation or recreation, leading to increased exposure of bikes in public spaces.
-These high-theft months underline the need for heightened security measures and awareness among cyclists, particularly during summer.
+These high-theft months underline the need for heightened security measures and awareness among cyclists, particularly during summer.</p>
 
-The year 2020, however, deviates from this regular trend due to the impact of the COVID-19 pandemic.
+<p>The year 2020, however, deviates from this regular trend due to the impact of the COVID-19 pandemic.
 As public transit options were considered risky, many Torontonians turned to bicycles as a safer and more flexible transportation option, resulting in a rise in bike ownership and driving up theft rates (@citeShapiro2021).
 Additionally, the pandemic stretched police resources, potentially limiting routine patrols and recovery efforts.
-The 2020 increase highlights how external factors, such as a public health crisis, can exacerbate bike theft trends and points to the importance of adaptable theft prevention strategies in response to changing urban transportation needs.
+The 2020 increase highlights how external factors, such as a public health crisis, can exacerbate bike theft trends and points to the importance of adaptable theft prevention strategies in response to changing urban transportation needs.</p>
+</div>
 
@@
   <p>Now imagine you’re navigating the streets of Toronto, trying to understand where bicycle thefts are happening.
-@interactive_map is like an overhead view from a hot air balloon, showing clusters of incidents with bright orange circles scattered across the landscape.
+The interactive map below is like an overhead view from a hot air balloon, showing clusters of incidents with bright orange circles scattered across the landscape.
 Each circle represents a collection of theft reports—smaller bubbles indicate fewer incidents, while larger ones stand like towering beacons, signaling areas of greater vulnerability.
@@
 It's like having a personal guide leading you through the hot spots and quieter neighborhoods.</p>
+</div>
 
 <center>
-```{r interactive_map, echo=FALSE, warning=FALSE, message=FALSE}
+```{r interactive_map, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=7, fig.height=4.5}
 #### Map with Markers ####
@@
 <div style="color: grey; font-size: 12px; margin-top: 3px; max-width: 800px; margin: 0 auto;">
-  [To be updated...]
+  Note: This interactive map reveals clusters of bicycle thefts across Toronto, clicking on each circle allows users to zoom in for detailed information on specific theft locations.
 </div> \
@@
 <div class="main-body">
-  <p>In @map_of_stolen_bike, we dive deeper into the city with a ground-level view—a sea of red dots each marks an individual theft incident.
+  <p>We then dive deeper into the city with a ground-level view—a sea of red dots each marks an individual theft incident(see "Map of Stolen Bike Cases in Toronto" below).
 The dots are packed tightly in certain neighborhoods, sprawling across downtown Toronto like a dense red blanket.
@@
 It’s almost as though you can hear the honks and feel the rush of people in these crowded streets.</p>
+</div>
 
 <center>
-```{r map_of_stolen_bike, echo=FALSE, warning=FALSE, message=FALSE}
+```{r map_of_stolen_bike, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=8, fig.height=4}
 
@@
     data = coordinates_data, aes(x = longitude, y = latitude),
-    size = 0.5, color = "#FFC107"
+    size = 0.3, color = "#FFC107"
   ) + # Bike theft points
@@
 
-<div style="color: grey; font-size: 12px; margin-top: 3px; max-width: 800px; margin: 0 auto;">
-  [To be updated...]
-</div> \
+<div style="color: grey; font-size: 12px; margin-top: 3px; max-width: 800px; margin: 0 auto; text-align: center; display: flex; justify-content: center;">
+  This map reveals a high concentration of bike theft incidents in downtown Toronto.
+</div>
 
 <div class="main-body">
-  <p>@map_case_number takes a step back to help us understand the data by neighborhood, but this time with broader strokes.
+  <p>The map below takes a step back to help us understand the data by neighborhood, but this time with a broader overview.
 It presents different regions in Toronto as bubbles of varying sizes and colors, indicating the number of thefts in each.
@@
 Meanwhile, the areas with smaller circles seem almost untouched in comparison, a stark contrast that reveals a city of disparities—some areas buzz with activity and theft risk, while others enjoy relative calm.</p>
+</div>
 
 <center>
-```{r map_case_number, echo=FALSE, warning=FALSE, message=FALSE}
+```{r map_case_number, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=7, fig.height=4}
 #### Map with Areas ####
@@
 <div style="color: grey; font-size: 12px; margin-top: 3px; max-width: 800px; margin: 0 auto;">
-  [To be updated...]
+  Note: The size of each point is proportional to the number of cases reported in each area, highlighting hotspots like downtown and other major regions.
+By clicking on each point, number of totals cases will be shown for different areas, including Downtown, Etobicoke, York, East York, North York, and Scarborough.
 </div> \
@@
 <div class="main-body">
-  <p>In this analysis, we began by examining when bikes are at the greatest risk of theft, revealing a strong seasonal trend with thefts peaking in the summer months from May to August and notable increase on Fridays.
+  <p>In this article, we began by examining when bikes are at the greatest risk of theft, revealing a strong seasonal trend with thefts peaking in the summer months from <strong style="color: #FFC107;">May</strong> to <strong style="color: #FFC107;">August</strong> and notable increase on <strong style="color: #FFC107;">Fridays</strong>.
 These insights provided a foundation for understanding the timing of bike thefts.
@@
 
-<p>The analysis also dove into geographical patterns, identifying hotspots such as downtown Toronto and major transit hubs where bike thefts are most concentrated.
+<p>We also explored geographical patterns, identifying hotspots such as downtown Toronto and major transit hubs where bike thefts are most concentrated.
 Through mapping, we provided a visual representation of high-risk areas, guiding cyclists and policymakers on where extra security measures are most needed.</p>
@@
 Future studies could extend this analysis to examine bike theft patterns across Canada, providing a nationwide perspective on hotspots and seasonal trends.
-By combining these efforts, city authorities, advocacy groups, and cyclists themselves can work together to create a safer environment for biking across Toronto.</p>
+By combining these efforts, city authorities, advocacy groups, and cyclists themselves can work together to create a <strong style="color: #FFC107;">safer</strong> environment for biking across Toronto.</p>
+</div>
 
@@
 <div class="main-body">
-  <p>This article is a reminder: as cycling grows in popularity, so does the risk of theft.
+  <p>**This article is a reminder**: as cycling grows in popularity, so does the risk of <strong style="color: #FFC107;">theft</strong>.
 Whether you’re a daily commuter or a weekend rider, taking extra precautions—like using a sturdy lock, parking in well-lit areas, and registering your bike—can make a big difference.
-Protect your bike, and keep Toronto’s cycling community rolling safely all year round.</p>
+<strong style="color: #FFC107;">Protect</strong> your bike, and keep Toronto’s cycling community rolling safely all year round.</p>
+</div>
 
 <div class="section-heading">
-  <span class="section-title-line1">Citations</span><br>
+  <span class="section-title-line1"></span><br>
 </div>
+
+<div class='citation-section'>
+  <h3>References</h3>
+  <ul>
+    <li>Bike Month. (2024). <i>Bike Month Toronto.</i> <a href='https://www.bikemonth.ca/toronto'>https://www.bikemonth.ca/toronto</a></li>
+    <li>City of Toronto.
+(2019).
+<i>2019 cycling public opinion survey.</i> <a href='https://www.toronto.ca/wp-content/uploads/2021/04/8f76-2019-Cycling-Public-Option-Survey-City-of-Toronto-Cycling.pdf'>https://www.toronto.ca/wp-content/uploads/2021/04/8f76-2019-Cycling-Public-Option-Survey-City-of-Toronto-Cycling.pdf</a></li>
+    <li>City of Toronto.
+(2024).
+<i>Bicycle parking.</i> <a href='https://www.toronto.ca/services-payments/streets-parking-transportation/cycling-in-toronto/bicycle-parking/'>https://www.toronto.ca/services-payments/streets-parking-transportation/cycling-in-toronto/bicycle-parking/</a></li>
+    <li>CTV News.
+(2024).
+Should Toronto tear up its bike lanes to improve traffic flow?
+Critics say it’s not so simple.
+<i>CTV News.</i> <a href='https://www.ctvnews.ca/canada/should-toronto-tear-up-its-bike-lanes-to-improve-traffic-flow-critics-say-it-s-not-so-simple-1.7103768'>https://www.ctvnews.ca/canada/should-toronto-tear-up-its-bike-lanes-to-improve-traffic-flow-critics-say-it-s-not-so-simple-1.7103768</a></li>
+    <li>Cycle Toronto.
+(2021).
+Council talking about ending bike theft week.
+<i>Cycle Toronto.</i> <a href='https://www.cycleto.ca/council-talking-about-ending-bike-theft-week'>https://www.cycleto.ca/council-talking-about-ending-bike-theft-week</a></li>
+    <li>Project 529. (2024). <i>529 garage: Bike registration to reduce theft and help recovery.</i> <a href='https://project529.com/garage'>https://project529.com/garage</a></li>
+    <li>Shapiro, A.
+(2021).
+Bike thieves are on a roll during the pandemic.
+Here’s how to protect your ride.
+<i>NPR.</i> <a href='https://www.npr.org/2021/04/02/980008727/bike-thieves-are-on-a-roll-during-the-pandemic-heres-how-to-protect-your-ride'>https://www.npr.org/2021/04/02/980008727/bike-thieves-are-on-a-roll-during-the-pandemic-heres-how-to-protect-your-ride</a></li>
+    <li>Toronto Police Service. (2024a). <i>Bicycle registration.</i> <a href='https://www.tps.ca/services/bicycle-registration/'>https://www.tps.ca/services/bicycle-registration/</a></li>
+    <li>Toronto Police Service.
+(2024b).
+<i>Bicycle safety & theft prevention.</i> <a href='https://www.tps.ca/crime-prevention/bicycle-safety-and-theft-prevention/'>https://www.tps.ca/crime-prevention/bicycle-safety-and-theft-prevention/</a></li>
+    <li>Toronto Police Service.
+(2024c).
+<i>Bicycle thefts open data.</i> <a href='https://data.torontopolice.on.ca/datasets/TorontoPS::bicycle-thefts-open-data/about'>https://data.torontopolice.on.ca/datasets/TorontoPS::bicycle-thefts-open-data/about</a></li>
+    <li>Toronto Police Service.
+(2024d).
+Project Sentry: Keeping Toronto safe.
+<i>Toronto Police Service.</i> <a href='https://www.tps.ca/media-centre/news-releases/fix-title-project-sentry/'>https://www.tps.ca/media-centre/news-releases/fix-title-project-sentry/</a></li>
+  </ul>
+</div>

### 2024-11-14 paper/paper.Rmd

@@
 
-  <p>In this analysis, we dig into over a decade’s worth of data from the <a href="https://data.torontopolice.on.ca/datasets/TorontoPS::bicycle-thefts-open-data/about" target="_blank" style="color: #FFC107; text-decoration: underline;">Toronto Police Service</a> (@citePolice) to answer key questions: When are bikes at the greatest risk?
+  <p>In this analysis, we dig into over a decade’s worth of data from the <a href="https://data.torontopolice.on.ca/datasets/TorontoPS::bicycle-thefts-open-data/about" target="_blank" style="color: #FFC107; text-decoration: underline;">Toronto Police Service</a> (Toronto Police Service, 2024c) to answer key questions: When are bikes at the greatest risk?
 What makes a bike more likely to be targeted?
@@
 
-<p>This insight could be valuable for both cyclists and advocacy groups like <a href="https://www.cycleto.ca/" target="_blank" style="color: #FFC107; text-decoration: underline;">Cycle Toronto</a> (@citeEndBikeTheft).
+<p>This insight could be valuable for both cyclists and advocacy groups like <a href="https://www.cycleto.ca/" target="_blank" style="color: #FFC107; text-decoration: underline;">Cycle Toronto</a> (Cycle Toronto, 2021).
 Understanding that Friday is a peak day for thefts, local authorities could consider increasing surveillance or public awareness efforts on this day, especially in known hotspot areas.
@@
   <p>The visualization of bike theft and recovery patterns in Toronto using data from 2014 to mid 2024 above reveals a distinct seasonality, with thefts peaking during the warmer months from May to August.
-This trend likely correlates with <a href="https://www.toronto.ca/wp-content/uploads/2021/04/8f76-2019-Cycling-Public-Option-Survey-City-of-Toronto-Cycling.pdf" target="_blank" style="color: #FFC107; text-decoration: underline;">increase</a> (@citeSurvey) cycling activity during the summer, when more people choose biking as a primary mode of transportation or recreation.
-Events like <a href="https://www.bikemonth.ca/toronto" target="_blank" style="color: #FFC107; text-decoration: underline;">Bike Month</a> (@citeBikeMonth) in June, which includes initiatives encouraging cycling, leading to higher exposure of bikes, making them easier targets for theft.</p>
+This trend likely correlates with <a href="https://www.toronto.ca/wp-content/uploads/2021/04/8f76-2019-Cycling-Public-Option-Survey-City-of-Toronto-Cycling.pdf" target="_blank" style="color: #FFC107; text-decoration: underline;">increase</a> (City of Toronto, 2019) cycling activity during the summer, when more people choose biking as a primary mode of transportation or recreation.
+Events like <a href="https://www.bikemonth.ca/toronto" target="_blank" style="color: #FFC107; text-decoration: underline;">Bike Month</a> (Bike Month, 2024) in June, which includes initiatives encouraging cycling, leading to higher exposure of bikes, making them easier targets for theft.</p>
 
@@
 The low recovery rate highlights systemic issues in bike recovery efforts.
-Despite <a href="https://www.tps.ca/services/bicycle-registration/" target="_blank" style="color: #FFC107; text-decoration: underline;">city-wide bike registry programs</a> (@citeTPSRegistration) and <a href="https://www.tps.ca/crime-prevention/bicycle-safety-and-theft-prevention/" target="_blank" style="color: #FFC107; text-decoration: underline;">police campaigns</a> (@citeTPSBicycleSafety) aimed at educating cyclists about secure parking and locking techniques, the ratio of bikes recovered to those stolen has remained low.
-In recent years, Toronto has initiated <a href="https://www.toronto.ca/services-payments/streets-parking-transportation/cycling-in-toronto/bicycle-parking/" style="color: #FFC107; text-decoration: underline;">programs</a> (@citeBicycleParking) to improve bike parking infrastructure and introduced more secure lock stands in high-theft areas, but these measures appear insufficient given the scale of theft illustrated in this data.</p>
+Despite <a href="https://www.tps.ca/services/bicycle-registration/" target="_blank" style="color: #FFC107; text-decoration: underline;">city-wide bike registry programs</a> (Toronto Police Service, 2024a) and <a href="https://www.tps.ca/crime-prevention/bicycle-safety-and-theft-prevention/" target="_blank" style="color: #FFC107; text-decoration: underline;">police campaigns</a> (Toronto Police Service, 2024b) aimed at educating cyclists about secure parking and locking techniques, the ratio of bikes recovered to those stolen has remained low.
+In recent years, Toronto has initiated <a href="https://www.toronto.ca/services-payments/streets-parking-transportation/cycling-in-toronto/bicycle-parking/" style="color: #FFC107; text-decoration: underline;">programs</a> (City of Toronto, 2024) to improve bike parking infrastructure and introduced more secure lock stands in high-theft areas, but these measures appear insufficient given the scale of theft illustrated in this data.</p>
 </div>
@@
 Cyclists with more expensive bikes should consider using two different types of locks, such as a U-lock paired with a cable lock, and avoid leaving their bikes outside overnight.
-Indoor storage options, when available, provide the highest level of security (@citeTPSBicycleSafety).
-Additionally, registering bikes with Toronto’s bike registry or Project 529 can improve the chances of recovery if theft occurs (@citeTPSRegistration; @cite529).
+Indoor storage options, when available, provide the highest level of security (Toronto Police Service, 2024b).
+Additionally, registering bikes with Toronto’s bike registry or Project 529 can improve the chances of recovery if theft occurs (Toronto Police Service, 2024b; Project 529, 2024).
 By marking bikes with unique identifiers and varying parking locations regularly, cyclists can make their bikes less predictable targets and better protect them from theft in Toronto.</p>
@@
   <p>The tallest bar, representing "Bikes Stolen," towers above the others with over <strong style="color: #FFC107;">32,000</strong> reported incidents, emphasizing how prevalent bike theft has become across the city of Toronto.
-<a href="https://www.ctvnews.ca/canada/should-toronto-tear-up-its-bike-lanes-to-improve-traffic-flow-critics-say-it-s-not-so-simple-1.7103768" style="color: #FFC107; text-decoration: underline;">CTV news</a> (@citeCTV) have highlighted hotspots, including downtown Toronto and areas near major transit hubs, where cyclists frequently leave bikes unattended.
-In response, The Toronto Police Service (TPS) has introduced <a href="https://www.tps.ca/media-centre/news-releases/fix-title-project-sentry/" style="color: #FFC107; text-decoration: underline;">Project Sentry</a> (@citeTPSProjectSentry), an initiative led by officers in 14 Division aimed at recovering stolen bicycles and reuniting them with their rightful owners across the city.
+<a href="https://www.ctvnews.ca/canada/should-toronto-tear-up-its-bike-lanes-to-improve-traffic-flow-critics-say-it-s-not-so-simple-1.7103768" style="color: #FFC107; text-decoration: underline;">CTV news</a> (CTV News, 2024) have highlighted hotspots, including downtown Toronto and areas near major transit hubs, where cyclists frequently leave bikes unattended.
+In response, The Toronto Police Service (TPS) has introduced <a href="https://www.tps.ca/media-centre/news-releases/fix-title-project-sentry/" style="color: #FFC107; text-decoration: underline;">Project Sentry</a> (Toronto Police Service, 2024d), an initiative led by officers in 14 Division aimed at recovering stolen bicycles and reuniting them with their rightful owners across the city.
 This program is part of TPS’s effort to address the high rates of bike theft and improve recovery outcomes for Toronto cyclists.
@@
 The small size of this bar underscores how difficult it is to retrieve stolen bikes and reunite them with their owners, suggesting a systemic issue in tracking and identifying stolen bicycles.
-Although Toronto has introduced <a href="https://project529.com/garage" style="color: #FFC107; text-decoration: underline;">Project 529</a> (@cite529) to help track ownership, recovery rates remain low, partly due to limited resources and the challenge of identifying recovered bikes that may have been altered or resold.
+Although Toronto has introduced <a href="https://project529.com/garage" style="color: #FFC107; text-decoration: underline;">Project 529</a> (Project 529, 2024) to help track ownership, recovery rates remain low, partly due to limited resources and the challenge of identifying recovered bikes that may have been altered or resold.
 </p>
@@
 <p>The year 2020, however, deviates from this regular trend due to the impact of the COVID-19 pandemic.
-As public transit options were considered risky, many Torontonians turned to bicycles as a safer and more flexible transportation option, resulting in a rise in bike ownership and driving up theft rates (@citeShapiro2021).
+As public transit options were considered risky, many Torontonians turned to bicycles as a safer and more flexible transportation option, resulting in a rise in bike ownership and driving up theft rates (Shapiro, 2021).
 Additionally, the pandemic stretched police resources, potentially limiting routine patrols and recovery efforts.
@@
   <p>Now imagine you’re navigating the streets of Toronto, trying to understand where bicycle thefts are happening.
-The interactive map below is like an overhead view from a hot air balloon, showing clusters of incidents with bright orange circles scattered across the landscape.
-Each circle represents a collection of theft reports—smaller bubbles indicate fewer incidents, while larger ones stand like towering beacons, signaling areas of greater vulnerability.
+The interactive map below shows an overhead view with clusters of incidents marked by bright orange circles spread across the area of Toronto.
+Each circle represents a group of theft reports—smaller circles show fewer incidents, while larger ones stand out, marking areas with higher vulnerability.
 <a href="https://en.wikipedia.org/wiki/Downtown_Toronto" target="_blank" style="color: #FFC107; text-decoration: underline;">Downtown Toronto</a>, unsurprisingly, is covered by a massive bubble, indicating that this densely populated urban center has been most affected by bike thefts.
@@
 <div class="main-body">
-  <p>We then dive deeper into the city with a ground-level view—a sea of red dots each marks an individual theft incident(see "Map of Stolen Bike Cases in Toronto" below).
-The dots are packed tightly in certain neighborhoods, sprawling across downtown Toronto like a dense red blanket.
-It paints a vivid picture of the density of bike thefts—evidence that the bustling central part of the city faces a higher risk.
-Street after street is littered with these red markers, almost as if each streetlight bore witness to a theft.
+  <p>We then dive deeper into the city with a ground-level view — a sea of <strong style="color: #FFC107;">yellow</strong> dots each marks an individual theft incident(see "Map of Stolen Bike Cases in Toronto" below).
+The dots are packed tightly in certain neighborhoods, spreading across downtown Toronto like a thick yellow blanket.
+It paints a picture of the density of bike thefts—evidence that the busy central part of the city faces a higher risk.
 There’s a sharp concentration near transit hubs and popular neighborhoods, suggesting a correlation between foot traffic, bike use, and crime opportunity.
-The City has been making efforts to combat this issue; for example, Cycle Toronto launched the <a href="https://www.cycleto.ca/council-talking-about-ending-bike-theft-week" target="_blank" style="color: #FFC107; text-decoration: underline;">#EndBikeTheft campaign</a> (@citeEndBikeTheft), advocating for secure parking and better registration systems, with city discussions exploring collaboration with platforms like <a href="https://project529.com/garage" style="color: #FFC107; text-decoration: underline;">529 Garage</a> (@cite529) to help reduce and recover stolen bikes.
-It’s almost as though you can hear the honks and feel the rush of people in these crowded streets.</p>
+Nevertheless, toronto has been making efforts to combat this issue; for example, Cycle Toronto launched the <a href="https://www.cycleto.ca/council-talking-about-ending-bike-theft-week" target="_blank" style="color: #FFC107; text-decoration: underline;">#EndBikeTheft campaign</a> (Cycle Toronto, 2021), advocating for secure parking and better registration systems, with city discussions exploring collaboration with platforms like <a href="https://project529.com/garage" style="color: #FFC107; text-decoration: underline;">529 Garage</a> (Project 529, 2024) to help reduce and recover stolen bikes.</p>
 </div>
@@
 It presents different regions in Toronto as bubbles of varying sizes and colors, indicating the number of thefts in each.
-The larger and darker the bubble, the more incidents that have occurred there.
-One particular neighborhood stands out—a massive blue circle in the downtown area—it visually reinforces what the other charts have hinted at: that specific neighborhoods, especially those near the core, are the epicenters of bicycle theft.
-Meanwhile, the areas with smaller circles seem almost untouched in comparison, a stark contrast that reveals a city of disparities—some areas buzz with activity and theft risk, while others enjoy relative calm.</p>
+The larger the bubble, the more incidents that have occurred there.
+One particular neighborhood stands out—a massive <strong style="color: #FFC107;">yellow</strong> circle in the downtown area—it visually reinforces what the other charts have hinted at: that specific neighborhoods, especially those near the core, are the epicenters of bicycle theft.
+In contrast, the areas with smaller circles seem barely affected, this highlights a clear divide in the city — some neighborhoods experience frequent theft activity, while others remain calm and safer.</p>
 </div>
@@
 Whether you’re a daily commuter or a weekend rider, taking extra precautions—like using a sturdy lock, parking in well-lit areas, and registering your bike—can make a big difference.
-<strong style="color: #FFC107;">Protect</strong> your bike, and keep Toronto’s cycling community rolling safely all year round.</p>
+<strong style="color: #FFC107;">Protect</strong> your bike, and keep Toronto’s cycling community rolling safely all year round!</p>
 </div>

### 2024-11-19 paper/paper.Rmd
rewitten in story format

@@
 
-  <div class="author-date">Yingke He, Ziheng Zhong<br>November 12, 2024</div>
+  <div class="author-date">Yingke He, Ziheng Zhong<br>November 18, 2024</div>
 </div>
@@
 Read on as we trace theft trends over the years, reveal the high-risk locations, and provide practical advice to help protect your bike.</p>
+</div>
+
+<div class="main-body">
+  <p>Hi there!
+I’m a bicycle—just your regular two-wheeled friend.
+I’m here to take you places, let you feel the wind in your hair, and help you enjoy the streets of Toronto.
+Life might seem easy for me, but it’s not all smooth rides.
+In this city, there’s one big worry I face all the time: bike theft.
+And believe me, I’ve seen plenty of it.</p>
+
+  <p>Picture this: you lock me up on a busy Toronto street, thinking a strong lock and a little care will keep me safe.
+But the truth is, some seasons, certain types of bikes, and even specific areas make bikes like me much more likely to be stolen.
+Over the years, bike theft has gone from something that “might happen” to something we constantly have to worry about.
+But don’t worry—I’ve joined forces with some data experts to figure out what’s really happening.</p>
+
+  <p>We’ve looked at over ten years of data from the <a href="https://data.torontopolice.on.ca/datasets/TorontoPS::bicycle-thefts-open-data/about" target="_blank" style="color: #FFC107; text-decoration: underline;">Toronto Police Service</a> (Toronto Police Service, 2024c) to answer some big questions: When are bikes like me at the most risk?
+What makes us targets?
+And which parts of Toronto should we avoid?
+Over this time, <strong style="color: #FFC107;">32,489</strong> bikes have been reported stolen in Toronto, but only <strong style="color: #FFC107;">422</strong> were ever recovered.
+With these insights, we hope to give cyclists like you the knowledge to protect us better, while helping groups like Cycle Toronto and local officials focus on areas that need the most attention.
+Together, we’ll uncover theft trends, identify high-risk locations, and share practical tips to keep your bike safe and secure.</p>
 </div>
@@
 <div class="main-body">
-  <p> The Weekly Bicycle Theft Patterns in Toronto plot revealed that thefts are not evenly distributed throughout the week.
-The data shows a peak on Fridays, with over <strong style="color: #FFC107;">4,900</strong> reported thefts, followed by a decline on Saturday and Sunday.
-This trend may reflect how people use their bikes during the week versus the weekend.
-Fridays might represent a combination of commuter bike usage and weekend planning, where people may leave their bikes in high-traffic or less secure areas, making them more vulnerable to theft.</p>
+<p>It was Friday again, my least favorite day of the week.
+Don’t get me wrong, I love being ridden to the park or to the office, feeling the wind rushing past my handlebars.
+But Fridays?
+Fridays are dangerous.
+I’ve seen too many of my fellow bikes disappear on this day—snatched from racks, left lonely in crowded parking lots.
+Over <strong style="color: #FFC107;">4,900</strong> of us have gone missing on Fridays in Toronto.
+It’s not paranoia; it’s data.</p>
 
-<p>This insight could be valuable for both cyclists and advocacy groups like <a href="https://www.cycleto.ca/" target="_blank" style="color: #FFC107; text-decoration: underline;">Cycle Toronto</a> (Cycle Toronto, 2021).
-Understanding that Friday is a peak day for thefts, local authorities could consider increasing surveillance or public awareness efforts on this day, especially in known hotspot areas.
-Additionally, for cyclists, it suggests that extra caution on Fridays could reduce the risk of theft.
-The data here underscores the importance of timing in bike theft prevention, showing how risks fluctuate within the week, which may reflect broader social and behavioral patterns around work and leisure in Toronto.</p>\
+<p>You see, Fridays are chaotic.
+People rush to wrap up their week, juggling work and plans for the weekend.
+Some leave us in high-traffic zones, near pubs or downtown hotspots, forgetting how vulnerable we are.
+By Saturday and Sunday, the risk eases up a bit.
+Fewer commutes, fewer hurried stops.
+But Fridays?
+Fridays are a minefield.</p>
+
+<p>If only they knew what the data shows.
+Advocacy groups like <a href="https://www.cycleto.ca/" target="_blank" style="color: #FFC107; text-decoration: underline;">Cycle Toronto</a> (Cycle Toronto, 2021) have been raising awareness about these patterns.
+Perhaps one day, local authorities will patrol more on Fridays or run public awareness campaigns around hotspots.
+And for cyclists, knowing that Friday is the peak day for thefts might encourage them to lock us more securely or park in safer areas.
+I just hope these efforts take hold before more of us end up as another Friday statistic.</p\
 </div>
@@
 <div class="main-body">
-  <p>The visualization of bike theft and recovery patterns in Toronto using data from 2014 to mid 2024 above reveals a distinct seasonality, with thefts peaking during the warmer months from May to August.
-This trend likely correlates with <a href="https://www.toronto.ca/wp-content/uploads/2021/04/8f76-2019-Cycling-Public-Option-Survey-City-of-Toronto-Cycling.pdf" target="_blank" style="color: #FFC107; text-decoration: underline;">increase</a> (City of Toronto, 2019) cycling activity during the summer, when more people choose biking as a primary mode of transportation or recreation.
-Events like <a href="https://www.bikemonth.ca/toronto" target="_blank" style="color: #FFC107; text-decoration: underline;">Bike Month</a> (Bike Month, 2024) in June, which includes initiatives encouraging cycling, leading to higher exposure of bikes, making them easier targets for theft.</p>
+  <p>Summer is supposed to be my favorite time of year.
+The warm weather, the long days, and the bustling streets filled with fellow bikes and riders.
+But as much as I love the attention, it also makes me nervous.
+Between May and August, thefts peak—this is when bikes like me are at the greatest risk.
+It’s not surprising, really.
+More people are out riding, whether it’s for fun or as their main way to get around, as the <a href="https://www.toronto.ca/wp-content/uploads/2021/04/8f76-2019-Cycling-Public-Option-Survey-City-of-Toronto-Cycling.pdf" target="_blank" style="color: #FFC107; text-decoration: underline;">City of Toronto</a> (City of Toronto, 2019) has pointed out.
+Events like <a href="https://www.bikemonth.ca/toronto" target="_blank" style="color: #FFC107; text-decoration: underline;">Bike Month</a> (Bike Month, 2024) in June bring even more of us out into the open, where thieves have more opportunities to strike.
+We become easy targets, exposed and vulnerable, even when we’re locked up securely.</p>
 
-<p>In contrast, the left side of the plot illustrates the number of bikes found each month, which remains consistently low across the years.
-The low recovery rate highlights systemic issues in bike recovery efforts.
-Despite <a href="https://www.tps.ca/services/bicycle-registration/" target="_blank" style="color: #FFC107; text-decoration: underline;">city-wide bike registry programs</a> (Toronto Police Service, 2024a) and <a href="https://www.tps.ca/crime-prevention/bicycle-safety-and-theft-prevention/" target="_blank" style="color: #FFC107; text-decoration: underline;">police campaigns</a> (Toronto Police Service, 2024b) aimed at educating cyclists about secure parking and locking techniques, the ratio of bikes recovered to those stolen has remained low.
-In recent years, Toronto has initiated <a href="https://www.toronto.ca/services-payments/streets-parking-transportation/cycling-in-toronto/bicycle-parking/" style="color: #FFC107; text-decoration: underline;">programs</a> (City of Toronto, 2024) to improve bike parking infrastructure and introduced more secure lock stands in high-theft areas, but these measures appear insufficient given the scale of theft illustrated in this data.</p>
+  <p>And then there’s the sad reality of being found.
+While thousands of us go missing every year, the number of bikes recovered stays painfully low, no matter the season.
+Despite efforts like the <a href="https://www.tps.ca/services/bicycle-registration/" target="_blank" style="color: #FFC107; text-decoration: underline;">city-wide bike registry programs</a> (Toronto Police Service, 2024a) and <a href="https://www.tps.ca/crime-prevention/bicycle-safety-and-theft-prevention/" target="_blank" style="color: #FFC107; text-decoration: underline;">police campaigns</a> (Toronto Police Service, 2024b) to teach better locking techniques, the chances of being reunited with my rider are slim.
+Even with new <a href="https://www.toronto.ca/services-payments/streets-parking-transportation/cycling-in-toronto/bicycle-parking/" style="color: #FFC107; text-decoration: underline;">bike parking programs</a> (City of Toronto, 2024) and secure lock stands, the efforts still feel small compared to how many of us disappear each year.
+I can’t help but wonder—what more can be done to keep me and my friends safe?</p>
 </div>
@@
 <div class="main-body">
-  <p>The first plot illustrates the distribution of stolen bike types in Toronto, highlighting which kinds are more frequently targeted.
-Mountain bikes and recreational & commuting bikes make up the largest portions, at <strong style="color: #FFC107;">31%</strong> and <strong style="color: #FFC107;">27.4%</strong> respectively, reflecting their popularity among Toronto cyclists for both daily commuting and recreational use.
-Their common use likely makes them more visible and accessible, increasing the risk of theft.
-Electric bikes, by contrast, are less frequently stolen, accounting for only <strong style="color: #FFC107;">7.8%</strong>, which may reflect the added security measures often used by owners of higher-value bikes.</p>
+  <p>Let me tell you about the bikes that thieves seem to like the most.
+It’s no surprise that mountain bikes like me and our commuting cousins top the list.
+We’re everywhere—on trails, on streets, parked outside offices, and near parks.
+Together, we make up the biggest targets, with mountain bikes accounting for <strong style="color: #FFC107;">31%</strong> and recreational & commuting bikes adding another <strong style="color: #FFC107;">27.4%</strong>.
+Our popularity means we’re easy to spot and easier to steal.
+</p> <p>Electric bikes, though, seem to have it a bit easier.
+They only make up <strong style="color: #FFC107;">7.8%</strong> of stolen bikes.
+Maybe it’s because their owners tend to invest more in security—fancier locks, GPS trackers, or even parking us in safer spots.
+I guess it pays to be high-tech, but for the rest of us, being useful and everywhere means we’re always at risk.</p>
 
@@
 
-<p>The second plot examines bike theft by cost tier, showing that bikes in the lower price ranges (under \$500 and \$500-\$999) are the most commonly stolen, at <strong style="color: #FFC107;">34.9%</strong> and <strong style="color: #FFC107;">31.7%</strong> respectively.
-These lower-cost bikes are often used for daily commuting in Toronto, left in public spaces where they are more vulnerable.
-Interestingly, higher-value bikes (\$1000-\$1999 and above \$2000) also face theft risk, comprising <strong style="color: #FFC107;">20.9%</strong> and <strong style="color: #FFC107;">12.4%</strong> of thefts.
-This suggests that while thieves frequently target accessible, lower-value bikes, higher-cost bikes are still vulnerable, especially in busy urban areas where security can vary.</p>
+  <p>Let’s talk about how much I’m worth—or, as thieves might see it, how much they think I’m worth.
+The second plot shows that bikes in the lower price ranges, like those under \$500 or between \$500-\$999, are stolen the most, making up <strong style="color: #FFC107;">34.9%</strong> and <strong style="color: #FFC107;">31.7%</strong> of thefts.
+It makes sense—we’re often used for daily commuting, left outside offices, stores, or train stations, and become easy pickings.
+But don’t think being fancy makes me immune.
+Bikes worth \$1000-\$1999 and even those over \$2000 aren’t safe either, accounting for <strong style="color: #FFC107;">20.9%</strong> and <strong style="color: #FFC107;">12.4%</strong> of thefts.
+In the city, no bike is truly off-limits.</p>
 
-<p>These data highlight that all Toronto cyclists, regardless of their bike's value, should implement strong security measures.
-For lower-cost bikes commonly used for commuting, investing in a high-quality U-lock or chain lock is essential, as these bikes are frequently targeted due to their accessibility.
-Parking in high-traffic areas with security cameras, like those near busy shops or designated bike racks, can help prevent opportunistic theft.
-Even for a lower-value bike, taking these extra precautions can make a significant difference in reducing theft risk.</p>
+  <p>What does this mean for me and my friends?
+It’s simple: we all need protection, no matter our price tag.
+For lower-cost bikes like me, a strong U-lock or chain lock is a must.
+Parking in busy spots with security cameras or near bike racks helps too—anything to make thieves think twice.
+Even if I’m not worth a lot of money, taking these steps can make a big difference in keeping me safe.</p>
 
-<p>Higher-value bikes, while less commonly stolen, still attract attention and may require even more advanced protection.
-Cyclists with more expensive bikes should consider using two different types of locks, such as a U-lock paired with a cable lock, and avoid leaving their bikes outside overnight.
-Indoor storage options, when available, provide the highest level of security (Toronto Police Service, 2024b).
-Additionally, registering bikes with Toronto’s bike registry or Project 529 can improve the chances of recovery if theft occurs (Toronto Police Service, 2024b; Project 529, 2024).
-By marking bikes with unique identifiers and varying parking locations regularly, cyclists can make their bikes less predictable targets and better protect them from theft in Toronto.</p>
+  <p>Higher-value bikes, though, need even more care.
+If I were a high-end model, I’d hope for two locks—maybe a U-lock and a cable lock—and I’d beg you not to leave me outside overnight.
+Indoor storage is the gold standard.
+Oh, and registering me with Toronto’s bike registry or <a href="https://project529.com" target="_blank" style="color: #FFC107; text-decoration: underline;">Project 529</a> (Toronto Police Service, 2024b; Project 529, 2024) would improve my chances of being found if something went wrong.
+Marking me with a unique ID or changing up where you park me can also keep thieves guessing.
+With the right precautions, we can stay out of trouble and keep riding the streets of Toronto together.</p>
 </div>
@@
 <div class="main-body">
-  <p>The tallest bar, representing "Bikes Stolen," towers above the others with over <strong style="color: #FFC107;">32,000</strong> reported incidents, emphasizing how prevalent bike theft has become across the city of Toronto.
-<a href="https://www.ctvnews.ca/canada/should-toronto-tear-up-its-bike-lanes-to-improve-traffic-flow-critics-say-it-s-not-so-simple-1.7103768" style="color: #FFC107; text-decoration: underline;">CTV news</a> (CTV News, 2024) have highlighted hotspots, including downtown Toronto and areas near major transit hubs, where cyclists frequently leave bikes unattended.
-In response, The Toronto Police Service (TPS) has introduced <a href="https://www.tps.ca/media-centre/news-releases/fix-title-project-sentry/" style="color: #FFC107; text-decoration: underline;">Project Sentry</a> (Toronto Police Service, 2024d), an initiative led by officers in 14 Division aimed at recovering stolen bicycles and reuniting them with their rightful owners across the city.
-This program is part of TPS’s effort to address the high rates of bike theft and improve recovery outcomes for Toronto cyclists.
-</p>
+  <p>Now move on to the next plot, it’s hard to miss the tallest bar on the chart.
+It represents bikes like me—stolen over <strong style="color: #FFC107;">32,000</strong> times across Toronto.
+That’s a staggering number and a clear sign of just how common bike theft has become.
+Hotspots like downtown Toronto and areas near major transit hubs are especially risky, as pointed out by <a href="https://www.ctvnews.ca/canada/should-toronto-tear-up-its-bike-lanes-to-improve-traffic-flow-critics-say-it-s-not-so-simple-1.7103768" style="color: #FFC107; text-decoration: underline;">CTV News</a> (CTV News, 2024).
+Cyclists often leave us unattended there, making it easier for thieves to strike.
+Thankfully, programs like <a href="https://www.tps.ca/media-centre/news-releases/fix-title-project-sentry/" style="color: #FFC107; text-decoration: underline;">Project Sentry</a> (Toronto Police Service, 2024d) are trying to change that.
+Officers in 14 Division are working hard to recover bikes like me and reunite us with our owners.
+It’s a step in the right direction, but there’s still a long way to go.</p>
 
- <p>In contrast, the "Bikes Found" bar, with only <strong style="color: #FFC107;">422</strong> cases, reveals a deep gap in recovery efforts.
-The small size of this bar underscores how difficult it is to retrieve stolen bikes and reunite them with their owners, suggesting a systemic issue in tracking and identifying stolen bicycles.
-Although Toronto has introduced <a href="https://project529.com/garage" style="color: #FFC107; text-decoration: underline;">Project 529</a> (Project 529, 2024) to help track ownership, recovery rates remain low, partly due to limited resources and the challenge of identifying recovered bikes that may have been altered or resold.
-</p>
+  <p>Then there’s the “Bikes Found” bar, standing sadly at just <strong style="color: #FFC107;">422</strong>.
+It’s tiny compared to the number of stolen bikes, showing how difficult it is for me and my friends to find our way back home.
+Even with tools like <a href="https://project529.com/garage" style="color: #FFC107; text-decoration: underline;">Project 529</a> (Project 529, 2024), which helps track bike ownership, recovery is a real challenge.
+Sometimes, thieves change how we look or sell us off, making it hard for authorities to identify us.
+With limited resources, finding us often feels like searching for a needle in a haystack.</p>
 
- <p>The "Other" category, with around <strong style="color: #FFC107;">3,200</strong> cases, includes incidents such as attempted thefts, damage to bikes, mischief, and other related offenses.
-This category highlights a broader issue affecting bike security, indicating that many cyclists encounter safety challenges even when their bikes aren’t ultimately stolen.
-</p>
+  <p>And let’s not forget the “Other” category, with about <strong style="color: #FFC107;">3,200</strong> cases.
+This includes all sorts of problems—attempted thefts, damage, mischief, and more.
+Even if we’re not stolen outright, it’s a reminder that staying safe in Toronto is tough.
+Whether it’s scratches, broken parts, or near-misses, we face plenty of challenges out here on the streets.</p>
 </div>
@@
 <div class="main-body">
-  <p>The animated line plot illustrates the monthly patterns of bicycle thefts in Toronto from 2014 to mid-2024, revealing a clear seasonal trend.
-Each year, bike thefts rise steadily in the spring, peak during the summer months of June and July, and then decline in the fall and winter when cycling activity decreases.
-This predictable pattern aligns with Toronto's warmer months when more residents choose biking as their primary mode of transportation or recreation, leading to increased exposure of bikes in public spaces.
-These high-theft months underline the need for heightened security measures and awareness among cyclists, particularly during summer.</p>
+  <p>Every year, like clockwork, we bikes notice the change in seasons.
+The animated line plot shows it perfectly—how thefts rise with the spring sunshine, peak in the summer months of June and July, and then ease up as the colder weather sets in.
+It’s no surprise; during the warmer months, we’re everywhere.
+Torontonians take us out for daily commutes, weekend rides, and everything in between.
+But this also means we’re more exposed, left in public spaces where thieves can easily find us.
+Summer, for us, is both a season of joy and of danger, a time when heightened security measures are absolutely necessary.</p>
 
-<p>The year 2020, however, deviates from this regular trend due to the impact of the COVID-19 pandemic.
-As public transit options were considered risky, many Torontonians turned to bicycles as a safer and more flexible transportation option, resulting in a rise in bike ownership and driving up theft rates (Shapiro, 2021).
-Additionally, the pandemic stretched police resources, potentially limiting routine patrols and recovery efforts.
-The 2020 increase highlights how external factors, such as a public health crisis, can exacerbate bike theft trends and points to the importance of adaptable theft prevention strategies in response to changing urban transportation needs.</p>
+  <p>Then came 2020—a year none of us will ever forget.
+The usual seasonal rhythm was disrupted by the COVID-19 pandemic.
+With public transit suddenly seen as risky, more people turned to us for safer, flexible transportation.
+Bike ownership soared, and with it, unfortunately, thefts did too (Shapiro, 2021).
+At the same time, police resources were stretched thin, and patrols or recovery efforts likely took a backseat.
+It was a tough time to be a bike in Toronto.
+This spike in thefts during 2020 reminds us that external factors, like a public health crisis, can make an already challenging situation worse.
+It shows how important it is to adapt theft prevention strategies to changing urban needs so we can keep rolling safely, no matter what the future holds.</p>
 </div>
@@
 <div class="main-body">
-  <p>Now imagine you’re navigating the streets of Toronto, trying to understand where bicycle thefts are happening.
-The interactive map below shows an overhead view with clusters of incidents marked by bright orange circles spread across the area of Toronto.
-Each circle represents a group of theft reports—smaller circles show fewer incidents, while larger ones stand out, marking areas with higher vulnerability.
-<a href="https://en.wikipedia.org/wiki/Downtown_Toronto" target="_blank" style="color: #FFC107; text-decoration: underline;">Downtown Toronto</a>, unsurprisingly, is covered by a massive bubble, indicating that this densely populated urban center has been most affected by bike thefts.
-As we drift north and away from the downtown core, the bubbles shrink, suggesting fewer incidents—likely due to the suburban nature of these areas, where bikes are stored more securely.
-And here's the interactive part—you can <strong style="color: #FFC107;">click</strong> on these bubbles to zoom in and explore specific areas, uncovering the exact locations and getting a more detailed sense of bike stolen cases.
-It's like having a personal guide leading you through the hot spots and quieter neighborhoods.</p>
+  <p>Now, imagine being me, trying to figure out where I’m safest on the streets of Toronto.
+The interactive map below feels like a glimpse into my world—bright orange circles marking the spots where bikes like me are most at risk.
+Each circle tells a story: the smaller ones mean fewer incidents, while the large, glaring ones scream danger.
+And then there’s <a href="https://en.wikipedia.org/wiki/Downtown_Toronto" target="_blank" style="color: #FFC107; text-decoration: underline;">Downtown Toronto</a>, the heart of the city, covered by a massive bubble.
+It’s no surprise—this bustling area, filled with commuters and visitors, is the epicenter of bike thefts.
+As you look further north and into suburban areas, the bubbles shrink, suggesting quieter streets where bikes are often stored more securely.</p>
+
+  <p>What makes this map even better?
+You can <strong style="color: #FFC107;">click</strong> on the bubbles to zoom in.
+It’s like having a detective’s guide to uncover the details—exact locations, hot spots, and even the safer neighborhoods.
+For me and my fellow bikes, this kind of insight is priceless.
+Knowing where the risks are helps us stay out of trouble and keep rolling safely through Toronto’s streets.</p>
 </div>
@@
 <div class="main-body">
-  <p>We then dive deeper into the city with a ground-level view — a sea of <strong style="color: #FFC107;">yellow</strong> dots each marks an individual theft incident(see "Map of Stolen Bike Cases in Toronto" below).
-The dots are packed tightly in certain neighborhoods, spreading across downtown Toronto like a thick yellow blanket.
-It paints a picture of the density of bike thefts—evidence that the busy central part of the city faces a higher risk.
-There’s a sharp concentration near transit hubs and popular neighborhoods, suggesting a correlation between foot traffic, bike use, and crime opportunity.
-Nevertheless, toronto has been making efforts to combat this issue; for example, Cycle Toronto launched the <a href="https://www.cycleto.ca/council-talking-about-ending-bike-theft-week" target="_blank" style="color: #FFC107; text-decoration: underline;">#EndBikeTheft campaign</a> (Cycle Toronto, 2021), advocating for secure parking and better registration systems, with city discussions exploring collaboration with platforms like <a href="https://project529.com/garage" style="color: #FFC107; text-decoration: underline;">529 Garage</a> (Project 529, 2024) to help reduce and recover stolen bikes.</p>
+  <p>Take a broader look at the view of the city—it’s like flying on the sky for a little bit.
+A sea of <strong style="color: #FFC107;">yellow</strong> dots stretches across the map, each one marking where a bike like me was stolen (see "Map of Stolen Bike Cases in Toronto" below).
+In downtown Toronto, these dots are packed so tightly it looks like a thick yellow blanket covering the streets.
+It’s a clear reminder that the busy central parts of the city are the riskiest for us.
+Transit hubs and popular neighborhoods show the highest concentration, likely because they have the most people, bikes, and unfortunately, opportunities for theft.</p>
+
+  <p>But not all hope is lost.
+Advocacy groups like Cycle Toronto have stepped up with initiatives like the <a href="https://www.cycleto.ca/council-talking-about-ending-bike-theft-week" target="_blank" style="color: #FFC107; text-decoration: underline;">#EndBikeTheft campaign</a> (Cycle Toronto, 2021), pushing for safer parking and better registration systems.
+There’s even talk of teaming up with platforms like <a href="https://project529.com/garage" style="color: #FFC107; text-decoration: underline;">529 Garage</a> (Project 529, 2024) to track us better and help us get back home if we’re ever taken.
+It’s a start, and with more efforts like these, maybe one day those yellow dots won’t cover the map quite so densely.</p>
 </div>
@@
 <div class="main-body">
-  <p>The map below takes a step back to help us understand the data by neighborhood, but this time with a broader overview.
-It presents different regions in Toronto as bubbles of varying sizes and colors, indicating the number of thefts in each.
-The larger the bubble, the more incidents that have occurred there.
-One particular neighborhood stands out—a massive <strong style="color: #FFC107;">yellow</strong> circle in the downtown area—it visually reinforces what the other charts have hinted at: that specific neighborhoods, especially those near the core, are the epicenters of bicycle theft.
-In contrast, the areas with smaller circles seem barely affected, this highlights a clear divide in the city — some neighborhoods experience frequent theft activity, while others remain calm and safer.</p>
+  <p>The map below gave us another step back, which is a chance for us to see how each areas compare when it comes to bike theft.
+It’s a colorful scene, with bubbles of different sizes and shades showing how many of us have been stolen in each area.
+The larger the bubble, the more incidents it represents.
+And right in the heart of the city is a massive <strong style="color: #FFC107;">yellow</strong> circle, covering downtown Toronto.
+It’s like a giant warning sign, confirming what we already know: the core of the city is the most dangerous place for bikes like me.</p>
+
+  <p>Further out, the bubbles shrink, and the map starts to feel calmer.
+These smaller circles mark neighborhoods where thefts are less common, offering a glimpse of what safety might look like.
+It’s a sharp divide—some areas are hotspots, buzzing with theft activity, while others stay quiet and safer.
+For bikes like me, maps like this are a lifeline, helping us and our riders navigate Toronto’s streets with a better sense of where to stay extra cautious.</p>
 </div>
@@
 <div class="main-body">
-  <p>In this article, we began by examining when bikes are at the greatest risk of theft, revealing a strong seasonal trend with thefts peaking in the summer months from <strong style="color: #FFC107;">May</strong> to <strong style="color: #FFC107;">August</strong> and notable increase on <strong style="color: #FFC107;">Fridays</strong>.
-These insights provided a foundation for understanding the timing of bike thefts.
-Next, we looked into bike recovery rates, which showed a significant gap between the number of bikes stolen and those successfully recovered, highlighting the challenges in returning stolen bikes to their owners.
-This aspect underscored systemic issues in recovery efforts and the need for improved tracking systems.</p>
+  <p>As this article comes to a close, let me reflect on what we’ve uncovered about life as a bike in Toronto.
+First, we looked at when I’m most at risk.
+It’s clear that thefts spike in the summer months from <strong style="color: #FFC107;">May</strong> to <strong style="color: #FFC107;">August</strong>, with a noticeable jump on <strong style="color: #FFC107;">Fridays</strong>.
+These patterns gave us an idea of the timing of bike thefts and helped us understand when extra caution is needed.
+Next, we dove into recovery rates—or rather, the lack of them.
+The huge gap between the number of stolen bikes and those recovered highlights just how hard it is for bikes like me to make it back to our owners.
+It’s a reminder of the need for better tracking and recovery systems.</p>
 
-<p>We also explored geographical patterns, identifying hotspots such as downtown Toronto and major transit hubs where bike thefts are most concentrated.
-Through mapping, we provided a visual representation of high-risk areas, guiding cyclists and policymakers on where extra security measures are most needed.</p>
+  <p>We then explored where bike thefts happen, pinpointing hotspots like downtown Toronto and busy transit hubs where the risk is highest.
+The maps painted a clear picture of these danger zones, giving both cyclists and city planners a guide to where extra security measures are most urgently needed.</p>
 
-<p>Together, these visualizations connect to form a comprehensive view of Toronto’s bike theft landscape.
-They reveal the when, where, and why of bike theft, offering insights that can inform future actions.
-Moving forward, Toronto can strengthen its approach by expanding secure bike parking options, increasing partnerships with bike registration platforms like Project 529, and deploying targeted initiatives like Project Sentry in high-theft areas.
-Future studies could extend this analysis to examine bike theft patterns across Canada, providing a nationwide perspective on hotspots and seasonal trends.
-By combining these efforts, city authorities, advocacy groups, and cyclists themselves can work together to create a <strong style="color: #FFC107;">safer</strong> environment for biking across Toronto.</p>
+  <p>Altogether, these visualizations offer a complete story of Toronto’s bike theft problem.
+They show the when, where, and why of theft, giving insights that can inspire action.
+Moving forward, Toronto can do more to protect bikes like me by creating more secure parking, working closely with registration platforms like Project 529, and expanding targeted programs like Project Sentry in high-risk areas.
+Maybe future studies will take this analysis nationwide, shedding light on bike theft patterns across Canada.
+With all these efforts combined, cyclists, city officials, and advocacy groups can work together to make Toronto a <strong style="color: #FFC107;">safer</strong> place for bikes like me to ride, rest, and thrive.</p>
 </div>
@@
 <div class="main-body">
-  <p>**This article is a reminder**: as cycling grows in popularity, so does the risk of <strong style="color: #FFC107;">theft</strong>.
-Whether you’re a daily commuter or a weekend rider, taking extra precautions—like using a sturdy lock, parking in well-lit areas, and registering your bike—can make a big difference.
-<strong style="color: #FFC107;">Protect</strong> your bike, and keep Toronto’s cycling community rolling safely all year round!</p>
+  <p><strong>This article is a reminder</strong>: as more people turn to biking in Toronto, the risk of <strong style="color: #FFC107;">theft</strong> continues to grow.
+For bikes like me, the world is full of possibilities—but also risks.
+Whether you’re a daily commuter or a weekend adventurer, taking extra steps to protect me can go a long way.
+A sturdy lock isn’t just a piece of metal; it’s a lifeline.
+Parking in well-lit, high-traffic areas makes thieves think twice.
+And registering me with platforms like Project 529 ensures I have a better chance of finding my way back home if the worst happens.</p>
+
+  <p>But beyond individual actions, we need a community effort.
+Cyclists, advocacy groups, and city planners must come together to create a <strong style="color: #FFC107;">safer</strong> Toronto.
+More secure bike parking, stronger recovery programs, and greater public awareness are the tools we need to keep rolling with confidence.
+For bikes like me, it’s not just about avoiding theft; it’s about helping Toronto’s cycling community thrive—through every season, every neighborhood, and every ride.</p>
+
+  <p>So as you unlock me and hop on for your next journey, remember this: every precaution you take protects not just me, but the joy of cycling itself.
+Together, let’s keep Toronto’s streets vibrant, its riders safe, and its bikes where they belong—under the sun, on the move, and by your side.</p>
 </div>

### 2024-11-19 paper/paper.Rmd
made minor changes to the intro section

@@
 Read on as we trace theft trends over the years, reveal the high-risk locations, and provide practical advice to help protect your bike.</p>
+
+  <p>But rather than just telling you the facts, let’s try something different—how about hearing it straight from the perspective of a <strong>bike?</strong></p>
 </div>
@@
 And for cyclists, knowing that Friday is the peak day for thefts might encourage them to lock us more securely or park in safer areas.
-I just hope these efforts take hold before more of us end up as another Friday statistic.</p\
+I just hope these efforts take hold before more of us end up as another Friday statistic.</p>
 </div>
@@
   <p>So as you unlock me and hop on for your next journey, remember this: every precaution you take protects not just me, but the joy of cycling itself.
-Together, let’s keep Toronto’s streets vibrant, its riders safe, and its bikes where they belong—under the sun, on the move, and by your side.</p>
+Together, let’s keep Toronto’s streets vibrant, its riders safe, and its bikes where they belong—under the sun, on the move, and by your side!</p>
 </div>

### 2024-11-19 paper/paper.Rmd
map and content revised, limitation added

@@
 With these insights, we aim to empower cyclists with knowledge that can help them safeguard their bikes and inform Cycle Toronto and local authorities about the areas most in need of intervention.
-Read on as we trace theft trends over the years, reveal the high-risk locations, and provide practical advice to help protect your bike.</p>
-
-  <p>But rather than just telling you the facts, let’s try something different—how about hearing it straight from the perspective of a <strong>bike?</strong></p>
-</div>
-
-<div class="main-body">
+Read on as we trace theft trends over the years, reveal the high-risk locations, and provide practical advice to help protect your bike.
+But rather than just telling you the facts, let’s try something different—how about hearing it straight from the perspective of a <strong>bike:</strong></p>
+
   <p>Hi there!
@@
 But don’t worry—I’ve joined forces with some data experts to figure out what’s really happening.</p>
-
-  <p>We’ve looked at over ten years of data from the <a href="https://data.torontopolice.on.ca/datasets/TorontoPS::bicycle-thefts-open-data/about" target="_blank" style="color: #FFC107; text-decoration: underline;">Toronto Police Service</a> (Toronto Police Service, 2024c) to answer some big questions: When are bikes like me at the most risk?
-What makes us targets?
-And which parts of Toronto should we avoid?
-Over this time, <strong style="color: #FFC107;">32,489</strong> bikes have been reported stolen in Toronto, but only <strong style="color: #FFC107;">422</strong> were ever recovered.
-With these insights, we hope to give cyclists like you the knowledge to protect us better, while helping groups like Cycle Toronto and local officials focus on areas that need the most attention.
-Together, we’ll uncover theft trends, identify high-risk locations, and share practical tips to keep your bike safe and secure.</p>
 </div>
@@
 
+<div class="main-body">
+  <p>Take a broader look at the view of the city—it’s like flying in the sky for a little bit.
+A sea of <strong style="color: #FFC107;">yellow</strong> dots stretches across the map, each one marking where a bike like me was stolen (see "Map of Stolen Bike Cases in Toronto" below).
+Areas with denser clusters of dots indicate theft hotspots where many incidents have been reported, while lighter or sparser areas suggest fewer thefts.
+In downtown Toronto, these dots are packed so tightly it looks like a thick yellow blanket covering the streets.
+It’s a clear reminder that the busy central parts of the city are the riskiest for us.
+Transit hubs and popular neighborhoods show the highest concentration, likely because they have the most people, bikes, and unfortunately, opportunities for theft.</p>
+
+  <p>But not all hope is lost.
+Advocacy groups like Cycle Toronto have stepped up with initiatives like the <a href="https://www.cycleto.ca/council-talking-about-ending-bike-theft-week" target="_blank" style="color: #FFC107; text-decoration: underline;">#EndBikeTheft campaign</a> (Cycle Toronto, 2021), pushing for safer parking and better registration systems.
+There’s even talk of teaming up with platforms like <a href="https://project529.com/garage" style="color: #FFC107; text-decoration: underline;">529 Garage</a> (Project 529, 2024) to track us better and help us get back home if we’re ever taken.
+It’s a start, and with more efforts like these, maybe one day those yellow dots won’t cover the map quite so densely.</p>
+</div>
+
 <center>
@@
     data = coordinates_data, aes(x = longitude, y = latitude),
-    size = 0.3, color = "#FFC107"
+    size = 0.45, color = "#FFC107", alpha = 0.15
   ) + # Bike theft points
@@
   theme(
-    panel.background = element_blank(), # Remove panel background
-    panel.grid.major = element_blank(), # Remove major grid lines
-    panel.grid.minor = element_blank(), # Remove minor grid lines
+    panel.background = element_blank(),
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
     axis.text.x = element_text(angle = 45, hjust = 1)
@@
 <div class="main-body">
-  <p>The map below gave us another step back, which is a chance for us to see how each areas compare when it comes to bike theft.
-It’s a colorful scene, with bubbles of different sizes and shades showing how many of us have been stolen in each area.
-The larger the bubble, the more incidents it represents.
-And right in the heart of the city is a massive <strong style="color: #FFC107;">yellow</strong> circle, covering downtown Toronto.
-It’s like a giant warning sign, confirming what we already know: the core of the city is the most dangerous place for bikes like me.</p>
-
-  <p>Further out, the bubbles shrink, and the map starts to feel calmer.
-These smaller circles mark neighborhoods where thefts are less common, offering a glimpse of what safety might look like.
-It’s a sharp divide—some areas are hotspots, buzzing with theft activity, while others stay quiet and safer.
-For bikes like me, maps like this are a lifeline, helping us and our riders navigate Toronto’s streets with a better sense of where to stay extra cautious.</p>
+  <p>The map below takes a broader look, comparing bike theft incidents across different areas in Toronto.
+Each circle represents the number of theft cases in a region, with larger and brighter circles indicating higher numbers.
+At the center of the city, a massive <strong style="color: #FFC107;">yellow</strong> circle dominates the map, marking downtown Toronto as the hotspot for bike thefts.
+It’s clear that the dense urban core, with its high bike usage and heavy foot traffic, is where bikes like me are most at risk.</p>
+
+  <p>As we move away from the city center, the circles shrink and darken, representing areas with fewer reported thefts.
+These quieter neighborhoods show the clear contrast between high-risk zones and safer regions, highlighting how geography plays a role in bike security.
+Maps like this aren’t just data—they’re lifelines for bikes like me and our riders, offering a guide to navigating Toronto’s streets with caution and awareness of where the greatest risks lie.</p>
 </div>
@@
 They show the when, where, and why of theft, giving insights that can inspire action.
-Moving forward, Toronto can do more to protect bikes like me by creating more secure parking, working closely with registration platforms like Project 529, and expanding targeted programs like Project Sentry in high-risk areas.
+However, there’s still room to improve how we handle this data to make the insights even clearer and more actionable.
+For example, instead of ignoring incomplete entries, filling in missing details in ways that preserve key trends could offer a more complete picture.
+Additionally, breaking down regions into smaller, more specific areas could highlight particular streets or blocks where thefts are most frequent.
+This would allow for more focused responses and targeted solutions, ultimately making the findings more reliable and impactful.</p>
+
+  <p>Moving forward, Toronto can do more to protect bikes like me by creating more secure parking, working closely with registration platforms like Project 529, and expanding targeted programs like Project Sentry in high-theft areas.
 Maybe future studies will take this analysis nationwide, shedding light on bike theft patterns across Canada.
